### 2016-03-15 paperdraft.tex
first commit for thesis draft

\documentclass[iop,apj,twocolappendix]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

\newcommand{\Reff}{R$_{\rm eff}$}
\newcommand{\Msun}{M$_{\odot}$}

%\renewcommand{\deg}{\ensuremath{^{\circ}}\xspace} %defines a degree symbol

\shorttitle{CCGs in the RESOLVE Survey}
\shortauthors{Snyder et al.}

\begin{document}

\title{The Formation and Evolution of Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Mark N. Norris\altaffilmark{3}}
\author{Callie Hood\altaffilmark{1}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Christine Ray\altaffilmark{1,4}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{the RESOLVE Team}
\affil{$^1$University of North Carolina at Chapel Hill}
\affil{$^2$National Optical Astronomical Observatory}
\affil{$^3$University of Central Lancashire}
\affil{$^4$Rutgers, The State University of New Jersey}
\begin{abstract}
We analyze the complete set of compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments. CCGs include both compact ellipticals (cEs) and compact cores surrounded by an envelope of gas and stars, which may represent earlier or later evolutionary stages of cEs. We select CCGs to have core-only radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. CCGs naturally occur in a range of environments from isolated to cluster. With GALEX NUV data, we derive star formation histories and find that a significant number of CCGs have recently formed stars. We compare velocity dispersions of CCGs derived from Gemini IFU data to velocity dispersions of other RESOLVE galaxies derived from SOAR spectroscopy. We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively. Initial results show several CCGs following the dissipative formation track.
\end{abstract}

\keywords{galaxies: formation; galaxies: evolution}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}

\noindent The term compact stellar system (CSS) composes a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es). Different types of CSSs include ultra compact dwarf galaxies (UCDs; \cite{Phillipps2001}), compact elliptical galaxies (cEs; \cite{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).  There are many unanswered questions about these types of galaxies, typically involving how they form and evolve. One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are in an intermediate and short-lived evolutionary phase, or simply hard to find due to their size. Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.

\subsection{Introduction to UCDs}
UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \cite{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\cite{Drinkwater2000}, \cite{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\cite{Bekki2001}, \cite{Bekki2003}, \cite{Jennings2015}, \cite{Zhang2015}). Meanwhile, \cite{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546. \cite{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy.

 \subsection{Introduction to cEs}
cEs, the intermediate-sized CSSs of the three previously mentioned have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \cite{Norris2014}). They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (Choi, Guhathakurta \& Johnson 2002, Graham 2002), or as a part of the low mass extension to the elliptical galaxy population. The evidence for tidal stripping includes finding tidal streams near cEs (Smith Castelli 2008, Chilingarian 2009) and one cE, studied in Kormendy 1997 that is believed to host a central massive black hole. (Threshed spiral scenario: Davidge, Beck \& McGregor 2008). On the other hand, Kormendy \& Bender 2012 argue that cEs can be the extension of normal elliptical galaxies, based on

\subsection{Introduction to dEs and dE,Ns}
dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \cite{Norris2014}). Similarly to cEs, dEs and dE,Ns are though to be tidally stripped remnants (Crnojevic 2014 - dEs in M31 show signs of tidal stripping) or the low mass extension to elliptical galaxies (Steve Crawfords work on high-z LCBDs). They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched. There is some evidence that dE,Ns are the progenitors of UCDs (\cite{Pfeffer2013}, \cite{Zhang2015}, \cite{Liu2015}).

\subsection{Environments of UCDs}
UCDs have been primarily found in clusters, such as Coma (\cite{Price2009}, \cite{Madrid2010}), Fornax (\cite{Hilker1999}, \cite{Drinkwater2000}), Virgo (\cite{Hasegan2005}, \cite{Jones2006}), Centaurus (\cite{Mieske2009}), and Hydra I (\cite{Wehner2007}, \cite{Misgeld2008}). Fewer UCDs have been found in groups: \cite{Evstigneeva2007} find one definite and two candidate UCDs in the Dorado group as well as two candidates in the NGC1400 group. Addititonally, \cite{Hau2009} find a UCD near the Sombrero galaxy.

\subsection{Environments of cEs}
cEs suffer the same issue: they are mainly found in clusters (\cite{Chilingarian2007}, \cite{SmithCastelli2012}, \cite{Price2009}) and groups (Chilingarian \& Bergond 2010, \cite{Huxor2011}), but recently more have been found in an isolated environment. \cite{Huxor2013}, \cite{Paudel2014}. There is also recent work by Chilingarian 2015 that finds more isolated

\subsection{Environments of dEs}
dEs have also primarily been found in groups -- Crnojevic et al. 2014 - dEs in M31, Penny 2014) and clusters (\cite{SmithCastelli2012}, Koo 1994, Guzman 1996, Michielson 2008, Steve Crawford's papers).

\subsection{How environments impact formation scenarios}
Thus, there's been no ubiquitous sample of CSSs that allow us to analyze the formation as a function of all environments. These studies mostly focus on selecting targets in the group/cluster environments, since this route is more convenient. Only recently have CSSs been found in the field environment (\cite{Huxor2013}, \cite{Chilingarian2015}), which highlights the need for a statistical census of CSSs that spans the group to cluster to field environments.

\noindent Our goal is to create a complete and volume-limited sample of compact galaxies across all environments so that we may study their evolutionary sequences. For this, we derive our sample from the RESOLVE survey, as described in (\autoref{resolve}). We also use the objects in the Archive of Intermediate Mass Stellar Systems (AIMSS) for comparisons to our sample (\autoref{aimss}). We describe our sample selection process in \autoref{samples} and lastly, describe our spectroscopic data collection and analysis in \autoref{methods}.

\noindent * History of compact galaxy discoveries \\
* AIMSS survey progress \\
* Include why using the RESOLVE survey for this project and its advantages \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Samples}
\label{samples}

\subsection{The RESOLVE survey}
\label{resolve}

\noindent We use the RESOLVE survey (Kannpann \& Wei 2008, Kannappan et al., in prep) as the parent sample for our census of CCGs. RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages. RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \cite{York2000}), and is designed to span two individual semesters: A for the spring sky and B for the fall, which overlaps much of Stripe-82. RESOLVE-A spans $\sim38,400$ Mpc$^3$ and occupies the region 131.25\textdegree $<$ RA $<$ 236.25\textdegree, 0\textdegree $<$ Dec $<$ 5\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$, while RESOLVE-B spans $\sim13,7000 $ Mpc$^3$ and occupies the region 330\textdegree $<$ RA $<$ 45\textdegree, -1.25\textdegree $<$ Dec $<$ 1.255\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.

RESOLVE's exceptional completeness is due to our use of multiple redshift surveys to recover galaxies that were missed in SDSS due to fiber collisions and several issues with their photometry pipeline. These issues include the oversubtraction of sky around galaxies that causes their flux to be underestimated and thereby not meet the magnitude cut for spectroscopic follow-up; the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, making no one piece meet the magnitude cut; and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut. We have used SDSS along with additional redshifts from archival sources (the Updated Zwicky Catalog \cite{Falco1999}, HyperLeda \cite{Paturel2003}, 6dF \cite{Jones2009}, 2dF \cite{Colless2001}, GAMA \cite{Driver2011}, and ALFALFA \cite{Haynes2011}) to counteract these issues and build up the survey's membership.

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \cite{Eckert2015B}). In Figure 1, we plot the stellar masses against the deconvolved \Reff (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs. We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.

An important caveat to RESOLVE's completeness is that the survey is most likely to be missing the objects this study is focused on, cEs. This is because these objects can often be mistaken for stars in redshift surveys using tools such as SExtractor's \texttt{class\_star} parameter. There are current ongoing efforts to use photo-z estimates to recover these objects.

\subsection{The AIMSS catalog}
\label{aimss}

\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog (\cite{Norris2014}, \cite{Forbes2014}, \cite{Janz2015}) as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found in groups and clusters and includes both literature and newly discovered objects. Their process to find new CSSs is as follows. First, a search is conducted in the Hyperleda redshift catalog (\cite{Paturel2003}) for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$. Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies. Next, SExtractor (\cite{Bertin1996}) is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature. Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted. AIMSS also includes literature data for (nucleated) dwarf ellipticals, dwarf spheroidals, dwarf S0s, young massive clusters, and massive elliptical galaxies. AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.

\subsection{CCG sample selection}

\subsubsection{Deconvolution of RESOLVE galaxies}
\label{deconv}

\noindent In order to get accurate \Reff measurements for our We use Galfit (\cite{Peng2002}) to deconvolve the seeing PSF, and to perform one and two component fits on images of the galaxies in RESOLVE. Deconvolution is important as the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for our science. High imaging resolution for the galaxies in RESOLVE is necessary to resolve compact cores down to cE-like radii. Thus, for RESOLVE-A, we use publicly-available KiDS $r$ band data, which offers $< \sim0.7''$ seeing resolution corresponding to $< \sim300$pc at RESOLVE distances. For RESOLVE-B, we use publicly-available $Y$ band data from the UKIDSS Large Area Survey, which offers $\sim 0.8-1.0''$ seeing resolution, or $\sim350-450$ pc at RESOLVE distances. (Note: CFHT for the fall is much better at $\sim0.5-0.6''$ seeing!)

*here expand on the sersic vs king profiles when complete

With the one and two component fits from Galfit in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit (typically is $>0.2$ lower for the 2 comp but will re-assess with higher-res imaging). With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc. The core will be the smaller of the two components fit by Galfit.

\subsubsection{Selection of CCGs}
\label{ccgsel}

\noindent We use the AIMSS sample to select a maximum radius for our CCGs: 800 pc. This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs. RESOLVE's lower stellar mass limit (quote, and include in RESOLVE section above) restricts us from reaching down to UCD masses.

Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B). Figure 1 shows their distribution in stellar mass and \Reff compared to other RESOLVE galaxies and the AIMSS CSSs.

%* Imaging data from UKIDSS or CFHT for RESOLVE - B and potentially Subaru or KiDS for RESOLVE - A \\ 
%* Galfit parameters: sersic vs king profiles \\
%* Deciding if a two component fit is better than a one component fit

\section{Data and Methods}
\label{methods}

\subsection{Photometry: colors, stellar masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey also overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo. \cite{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.

\subsection{Environmental Metrics}
\label{env}
\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments. \cite{Moffett2015}

\subsection{Kinematics}
\label{kin}

\noindent As noted in the Introduction, the velocity dispersion of a galaxy is an extremely helpful tool when testing formation scenarios. We describe the data reduction and analysis to derive $\sigma$ for our CCG sample in this section.

\subsubsection{SOAR spectroscopy}
\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile. We employ the Goodman Spectrograph, designed and built by UNC, along with our custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup. From this absorption-line setup, we are able to derive velocity dispersions. We use the supremely-efficient 2100 l/mm VPH grating and cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335. To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.

The

\subsubsection{Gemini-South spectroscopy}

\noindent A subset of the smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR. For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of 3"$\times$5" and the spectral range 4200-5600\AA. The B1200 grating offers 0.9\AA resolution when binned spectrally by 2. We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\,  after binning by 2 in the spectral direction and summing the fibers out to \Reff.

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \textsc{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individal fiber spectra out to \Reff to create a 1D spectrum for each galaxy. More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix A.

We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from Cappellari \& Emsellem (2004). This code fits many model spectra (cite Maraston) to the observed input spectrum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Colors and Star formation rates}
\noindent 
* FIGURE: FSMGR vs Mbary/stars for RESOLVE, CCGs, and AIMSS \\
* FIGURE: SFR vs. Mbary/stars for RESOLVE, CCGs, and AIMSS \\

\noindent Figure \#A shows the u-r colors of our CCG sample plotted against M$_{\rm bary}$, compared to the RESOLVE sample as a whole. An unsual finding is that XX CCGs live on the blue sequence, a previsouly rare color for CSSs. REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".

Figure \#B shows FSMGR vs. M$_{\rm bary}$ for the same objects. As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr). This again goes against the common thought that CSSs are "red and dead".

Here discuss more the envelope vs non-enveloped CCGs and how their popultions may differ.

\subsection{Environments}
\noindent 
 *FIGURE: nearest neighbor and group halo mass\\
* FIGURE: group n vs group halo mass  \\
* Tie in Huxor's cE, idea of ejection from groups, how environment would effect CCGs

\subsection{Gas Content}
\noindent * look into g/s ratios \\
* reference Dave and Katie's work here

\subsection{Metallicities}
\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios

\subsection{Kinematics}
\noindent * why kinematics are important for formation scenario discernment\\
* FIGURE: ppxf fits for spectroscopic data to derive velocity dispersions \\
* FIGURE: velocity dispersion vs. stellar mass

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CCG formation and evolution} %kind of like a discussion section

\subsection{Gadget-2 simulations of cE formation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
  Acknowledgments. 
}

\bibliographystyle{apj}
\bibliography{library.bib}

\section{Appendix}

\end{document}

### 2016-04-07 paperdraft.tex
more updates to paper

@@
 \noindent The term compact stellar system (CSS) composes a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es).
-Different types of CSSs include ultra compact dwarf galaxies (UCDs; \cite{Phillipps2001}), compact elliptical galaxies (cEs; \cite{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).
+Different types of CSSs include ultra compact dwarf galaxies (UCDs; \citet{Phillipps2001}), compact elliptical galaxies (cEs; \citet{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).
 There are many unanswered questions about these types of galaxies, typically involving how they form and evolve.
@@
 \subsection{Introduction to UCDs}
-UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \cite{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\cite{Drinkwater2000}, \cite{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\cite{Bekki2001}, \cite{Bekki2003}, \cite{Jennings2015}, \cite{Zhang2015}).
-Meanwhile, \cite{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546.
-\cite{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy.
+UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \citet{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\citet{Drinkwater2000}, \citet{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\citet{Bekki2001}, \citet{Bekki2003}, \citet{Jennings2015}, \citet{Zhang2015}).
+Meanwhile, \citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546.
+\citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy.
 
  \subsection{Introduction to cEs}
-cEs, the intermediate-sized CSSs of the three previously mentioned have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \cite{Norris2014}).
+cEs, the intermediate-sized CSSs of the three previously mentioned have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}).
 They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (Choi, Guhathakurta \& Johnson 2002, Graham 2002), or as a part of the low mass extension to the elliptical galaxy population.
@@
 \subsection{Introduction to dEs and dE,Ns}
-dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \cite{Norris2014}).
+dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \citet{Norris2014}).
 Similarly to cEs, dEs and dE,Ns are though to be tidally stripped remnants (Crnojevic 2014 - dEs in M31 show signs of tidal stripping) or the low mass extension to elliptical galaxies (Steve Crawfords work on high-z LCBDs).
 They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched.
-There is some evidence that dE,Ns are the progenitors of UCDs (\cite{Pfeffer2013}, \cite{Zhang2015}, \cite{Liu2015}).
+There is some evidence that dE,Ns are the progenitors of UCDs (\citet{Pfeffer2013}, \citet{Zhang2015}, \citet{Liu2015}).
 
 \subsection{Environments of UCDs}
-UCDs have been primarily found in clusters, such as Coma (\cite{Price2009}, \cite{Madrid2010}), Fornax (\cite{Hilker1999}, \cite{Drinkwater2000}), Virgo (\cite{Hasegan2005}, \cite{Jones2006}), Centaurus (\cite{Mieske2009}), and Hydra I (\cite{Wehner2007}, \cite{Misgeld2008}).
-Fewer UCDs have been found in groups: \cite{Evstigneeva2007} find one definite and two candidate UCDs in the Dorado group as well as two candidates in the NGC1400 group.
-Addititonally, \cite{Hau2009} find a UCD near the Sombrero galaxy.
+UCDs have been primarily found in clusters, such as Coma (\citet{Price2009}, \citet{Madrid2010}), Fornax (\citet{Hilker1999}, \citet{Drinkwater2000}), Virgo (\citet{Hasegan2005}, \citet{Jones2006}), Centaurus (\citet{Mieske2009}), and Hydra I (\citet{Wehner2007}, \citet{Misgeld2008}).
+Fewer UCDs have been found in groups: \citet{Evstigneeva2007} find one definite and two candidate UCDs in the Dorado group as well as two candidates in the NGC1400 group.
+Addititonally, \citet{Hau2009} find a UCD near the Sombrero galaxy.
 
 \subsection{Environments of cEs}
-cEs suffer the same issue: they are mainly found in clusters (\cite{Chilingarian2007}, \cite{SmithCastelli2012}, \cite{Price2009}) and groups (Chilingarian \& Bergond 2010, \cite{Huxor2011}), but recently more have been found in an isolated environment.
-\cite{Huxor2013}, \cite{Paudel2014}.
+cEs suffer the same issue: they are mainly found in clusters (\citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}) and groups (Chilingarian \& Bergond 2010, \citet{Huxor2011}), but recently more have been found in an isolated environment.
+\citet{Huxor2013}, \citet{Paudel2014}.
 There is also recent work by Chilingarian 2015 that finds more isolated
@@
 dEs have also primarily been found in groups -- Crnojevic et al.
-2014 - dEs in M31, Penny 2014) and clusters (\cite{SmithCastelli2012}, Koo 1994, Guzman 1996, Michielson 2008, Steve Crawford's papers).
+2014 - dEs in M31, Penny 2014) and clusters (\citep{SmithCastelli2012}, Koo 1994, Guzman 1996, Michielson 2008, Steve Crawford's papers).
 
@@
 These studies mostly focus on selecting targets in the group/cluster environments, since this route is more convenient.
-Only recently have CSSs been found in the field environment (\cite{Huxor2013}, \cite{Chilingarian2015}), which highlights the need for a statistical census of CSSs that spans the group to cluster to field environments.
+Only recently have CSSs been found in the field environment (\citet{Huxor2013}, \citet{Chilingarian2015}), which highlights the need for a statistical census of CSSs that spans the group to cluster to field environments.
 
@@
 We describe our sample selection process in \autoref{samples} and lastly, describe our spectroscopic data collection and analysis in \autoref{methods}.
-
-\noindent * History of compact galaxy discoveries \\
-* AIMSS survey progress \\
-* Include why using the RESOLVE survey for this project and its advantages \\
 
@@
 RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages.
-RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \cite{York2000}), and is designed to span two individual semesters: A for the spring sky and B for the fall, which overlaps much of Stripe-82.
+RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \citet{York2000}), and is designed to span two individual semesters: A for the spring sky and B for the fall, which overlaps much of Stripe-82.
 RESOLVE-A spans $\sim38,400$ Mpc$^3$ and occupies the region 131.25\textdegree $<$ RA $<$ 236.25\textdegree, 0\textdegree $<$ Dec $<$ 5\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$, while RESOLVE-B spans $\sim13,7000 $ Mpc$^3$ and occupies the region 330\textdegree $<$ RA $<$ 45\textdegree, -1.25\textdegree $<$ Dec $<$ 1.255\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.
@@
 These issues include the oversubtraction of sky around galaxies that causes their flux to be underestimated and thereby not meet the magnitude cut for spectroscopic follow-up; the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, making no one piece meet the magnitude cut; and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut.
-We have used SDSS along with additional redshifts from archival sources (the Updated Zwicky Catalog \cite{Falco1999}, HyperLeda \cite{Paturel2003}, 6dF \cite{Jones2009}, 2dF \cite{Colless2001}, GAMA \cite{Driver2011}, and ALFALFA \cite{Haynes2011}) to counteract these issues and build up the survey's membership.
+We have used SDSS along with additional redshifts from archival sources (the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}) to counteract these issues and build up the survey's membership.
 
 With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively.
-We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \cite{Eckert2015B}).
+We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}).
 In Figure 1, we plot the stellar masses against the deconvolved \Reff (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
@@
 An important caveat to RESOLVE's completeness is that the survey is most likely to be missing the objects this study is focused on, cEs.
-This is because these objects can often be mistaken for stars in redshift surveys using tools such as SExtractor's \texttt{class\_star} parameter.
+This is because these objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}, which uses the flux and ellipticity of an object to determine the probability of it being a star or a galaxy.
 There are current ongoing efforts to use photo-z estimates to recover these objects.
@@
 
-\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog (\cite{Norris2014}, \cite{Forbes2014}, \cite{Janz2015}) as a reference sample for our CCGs.
+\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog (\citet{Norris2014}, \citet{Forbes2014}, \citet{Janz2015}) as a reference sample for our CCGs.
 AIMSS is a catalog of spectroscopically confirmed CSSs found in groups and clusters and includes both literature and newly discovered objects.
 Their process to find new CSSs is as follows.
-First, a search is conducted in the Hyperleda redshift catalog (\cite{Paturel2003}) for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$.
+First, a search is conducted in the Hyperleda redshift catalog \citep{Paturel2003} for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$.
 Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies.
-Next, SExtractor (\cite{Bertin1996}) is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature.
+Next, Source Extractor is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature.
 Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted.
@@
 
-\noindent In order to get accurate \Reff measurements for our We use Galfit (\cite{Peng2002}) to deconvolve the seeing PSF, and to perform one and two component fits on images of the galaxies in RESOLVE.
+\noindent In order to get accurate \Reff measurements for all galaxies in the RESOLVE sample, we use Galfit \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and perform one and two component fits on high-resolution imaging.
 Deconvolution is important as the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for our science.
 High imaging resolution for the galaxies in RESOLVE is necessary to resolve compact cores down to cE-like radii.
-Thus, for RESOLVE-A, we use publicly-available KiDS $r$ band data, which offers $< \sim0.7''$ seeing resolution corresponding to $< \sim300$pc at RESOLVE distances.
-For RESOLVE-B, we use publicly-available $Y$ band data from the UKIDSS Large Area Survey, which offers $\sim 0.8-1.0''$ seeing resolution, or $\sim350-450$ pc at RESOLVE distances.
-(Note: CFHT for the fall is much better at $\sim0.5-0.6''$ seeing!)
+Thus, for both RESOLVE-A and RESOLVE-B, we use publicly-available UKIDSS Large Area Survey \citep{Lawrence2007} $Y$-band data, which offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances.
 
-*here expand on the sersic vs king profiles when complete
+The first step in this process is to create PSFs for each image. My process is as follows:
 
-With the one and two component fits from Galfit in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit (typically is $>0.2$ lower for the 2 comp but will re-assess with higher-res imaging).
+\begin{enumerate}
+
+\item We begin by running Source Extractor on the image to identify every object and get estimates for each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.
+
+\item With this information, we select stars to use for building our PSF.
+The limiting parameters are (1) that the flux must be between $5,000-100,000$ counts to ensure no extremely faint or saturated stars are included, (2) that the ellipticity be lt 0.2 to ensure we are selecting round objects, (3) that the effective radius of the star be greater than 1 pixel to avoid selecting hot pixels, and (4) that \texttt{class\_star} is greater than 0.6 to ensure the objects we're picking are most likely stars.
+We also make sure the stars are not near the image edges, since there can sometimes be image artifacts there.
+Lastly, we make sure to not include the galaxy we are going to fit, since the cE-like galaxies can appear to be stars.
+
+\item We next make $101\times101$ pixel cutouts of each object detected, with the flux peak at pixel $x=51,y=51$.
+
+\item Background subtraction is then performed by taking the median of the entire cutout and then subtracting each pixel by this median value.
+
+\item We also use the background median to reject any of the cutouts that have a background median greater than $2\sigma$ from the mean of all the background median values.
+This ensures we are not including any cutouts that have stars with large or bright neighboring objects.
+We are now left with background-subtracted cutouts of stars with no neighbors that could effect our stacking.
+
+\item Before we can combine all the cutouts, we must normalize the flux of each central star to the same amplitude.
+To do this, we run each cutout through Source Extractor once more to obtain the fluxes of each central star, and use these to weight the cutouts accordingly.
+We calculate the weight for each cutout as follows: (1) we find the central star with the highest flux of all the cutouts and then (2) divide every flux by this maximum flux.
+We then divide each cutout by its corresponding weight, which makes each central star have the same amplitude.
+
+\item We then take the median of all the weighted cutouts to create a semi-complete PSF.
+
+\item Lastly, we normalize the semi-complete PSF from Step 7 by dividing each pixel in the frame by the total flux in the image.
+We find the total image flux by taking the mean of each pixel and multiplying that by the number of pixels in the image (so, $101\times101$).
+This ensures that the final PSF image is normalized, i.e., the sum of the flux in each pixel of the cutout would equal one.
+
+\end{enumerate}
+
+\noindent Once the PSF is complete, we fit a crude 2D Gaussian to it to determine a rough estimate seeing FWHM.
+The average seeing FWHM is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.
+
+The next steps involve the creation of items necessary for Galfit to run properly.
+This includes an image mask, a constraint file, and starting guesses for the parameters being fit.
+The image mask is made by running each image through Source Extractor and using its output list of sources and their sizes to create a binary image of the objects to mask.
+The
+
+With the one and two component fits from Galfit in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit.
 With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc.
@@
 Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B).
-Figure 1 shows their distribution in stellar mass and \Reff compared to other RESOLVE galaxies and the AIMSS CSSs.
-
-%* Imaging data from UKIDSS or CFHT for RESOLVE - B and potentially Subaru or KiDS for RESOLVE - A \\ 
-%* Galfit parameters: sersic vs king profiles \\
-%* Deciding if a two component fit is better than a one component fit
+Figure 1 shows their distribution in stellar mass and \Reff\ compared to other RESOLVE galaxies and the AIMSS CSSs.
 
@@
 \label{phot}
-\noindent The RESOLVE survey also overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo.
-\cite{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.
+\noindent The RESOLVE survey overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo.
+\citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.
 
@@
 \noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
-\cite{Moffett2015}
+\citet{Moffett2015}
 
@@
 \noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile.
-We employ the Goodman Spectrograph, designed and built by UNC, along with our custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup.
+We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup.
 From this absorption-line setup, we are able to derive velocity dispersions.
@@
 For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of 3"$\times$5" and the spectral range 4200-5600\AA.
-The B1200 grating offers 0.9\AA resolution when binned spectrally by 2.
+The B1200 grating offers 0.9\AA\ resolution when binned spectrally by 2.
 We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\,  after binning by 2 in the spectral direction and summing the fibers out to \Reff.
@@
 Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed.
-We next use the GMOS package gemCRspec, a wrapper for \textsc{LA\_COSMIC}, to clean cosmic rays from each science exposure.
+We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure.
 We then correct the science frames for quantum efficiency differences between CCDs.
 Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed.
-We then stack the individal fiber spectra out to \Reff to create a 1D spectrum for each galaxy.
+We then stack the individal fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
 More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix A.
 
-We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from Cappellari \& Emsellem (2004).
+\subsubsection{Velocity Dispersion Extraction}
+
+\noindent We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
 This code fits many model spectra (cite Maraston) to the observed input spectrum.
@@
 As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr).
-This again goes against the common thought that CSSs are "red and dead".
+This again goes against the common thought that CSSs are ``red and dead".
 
@@
 
-\subsection{Gadget-2 simulations of cE formation}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-12 paperdraft.tex
updates to paper

@@
 We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}).
-In Figure 1, we plot the stellar masses against the deconvolved \Reff (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
+In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
 We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.
@@
 
-\noindent In order to get accurate \Reff measurements for all galaxies in the RESOLVE sample, we use Galfit \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and perform one and two component fits on high-resolution imaging.
-Deconvolution is important as the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for our science.
-High imaging resolution for the galaxies in RESOLVE is necessary to resolve compact cores down to cE-like radii.
-Thus, for both RESOLVE-A and RESOLVE-B, we use publicly-available UKIDSS Large Area Survey \citep{Lawrence2007} $Y$-band data, which offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances.
+\noindent We begin our analysis by deriving seeing-corrected \Reff\ measurements for all galaxies in the RESOLVE sample.
+For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits on each galaxy.
+Deconvolution is especially important since the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for the study of these objects.
 
-The first step in this process is to create PSFs for each image. My process is as follows:
+\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file.
+We obtain/construct these items as follows:
 
+\begin{description}
+
+\item[The initial input file]{The initial input file tells \textsc{Galfit} where to find the image, PSF, mask, and constraint, and also holds the initial guesses for our fit parameters.
+These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details).
+For the one component fits, we set up our input file to have a section for measuring the value of the sky background, and another section for fitting a S\'ersic profile to galaxy.
+The two component fits with have three sections -- the sky and S\'ersic as in the one component fits, plus a second S\'ersic fit.
+}
+
+\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}.
+This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies.
+The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst.
+We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}.
+While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful for constructing a PSF.
+There are  only XX galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis.
+Visual inspection of these galaxies indicate that they would most likely not be classified as CCGs anyways.
+
+\item[The PSF image]{We build our PSF image via the following steps.
 \begin{enumerate}
 
-\item We begin by running Source Extractor on the image to identify every object and get estimates for each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.
+\item We begin by running Source Extractor on the image to identify every object in the frame, including stars, galaxies, and even sometimes hot pixels.
+Source Extractor outputs a .txt file that has estimates of each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.
 
@@
 
-\noindent Once the PSF is complete, we fit a crude 2D Gaussian to it to determine a rough estimate seeing FWHM.
-The average seeing FWHM is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.
+\noindent Our last step is to fit a 2D Gaussian to the PSF to determine a rough estimate seeing full width half max (FWHM), as a sanity check.
+We find that the average FWHM for all PSFs is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.
+\textsc{Galfit} uses this PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken.}
 
-The next steps involve the creation of items necessary for Galfit to run properly.
-This includes an image mask, a constraint file, and starting guesses for the parameters being fit.
-The image mask is made by running each image through Source Extractor and using its output list of sources and their sizes to create a binary image of the objects to mask.
-The
+\item[The mask image]{The first step is to create a mask image that has the same dimensions as our input image with each pixel value as zero.
+We again use Source Extractor to compile a list of all the objects in the input image, and then use this list to replace the pixel values in our mask with one.
+We replace the areas of the mask that have detected sources with ones, thus creating a binary image.
+\textsc{Galfit} uses the mask image to }
 
-With the one and two component fits from Galfit in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit.
+\item[The constant file]{The constraint file hosts the limits we are willing to accept for our fits.
+We fit on the following galaxy parameters: x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
+The constraints in place for these variables are listed in \autoref{constrtable}.}
+
+\end{description}
+
+\begin{table}[htdp]
+\begin{center}
+\begin{tabular}{cc} \hline
+parameter & constaint  \\ \hline
+x \& y position & $\pm5$ pixels from input value \\
+integrated magnitude & 0 -- 40 \\ 
+\Reff\ & 0.2 -- 750 pixels \\ 
+S\'ersic n & 0.1 -- 8 \\ 
+axial ratio & 0 -- 1 \\
+position angle & -360 -- 360 \\ \hline
+
+\end{tabular}
+\end{center}
+\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
+\label{constrtable}
+\end{table}%
+
+With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit.
 With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc.
-The core will be the smaller of the two components fit by Galfit.
+The core will be the smaller of the two components fit by \textsc{Galfit}.
 
@@
 
-\subsection{Gas Content}
-\noindent * look into g/s ratios \\
-* reference Dave and Katie's work here
-
-\subsection{Metallicities}
-\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios
-
 \subsection{Kinematics}
@@
 
+\section{Future Work}
+%\subsection{Gas Content}
+%\noindent * look into g/s ratios \\
+%* reference Dave and Katie's work here
+
+%\subsection{Metallicities}
+%\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-17 paperdraft.tex
updates to paper

@@
-\documentclass[iop,apj,twocolappendix]{emulateapj}
+\documentclass[iop,apj]{emulateapj}
 \pdfoutput=1 %for arxiv submission to use pdf
@@
 \usepackage{natbib}
+\usepackage{epstopdf}
 \usepackage{amsmath,amstext,textcomp}
@@
 These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details).
-For the one component fits, we set up our input file to have a section for measuring the value of the sky background, and another section for fitting a S\'ersic profile to galaxy.
-The two component fits with have three sections -- the sky and S\'ersic as in the one component fits, plus a second S\'ersic fit.
-}
+For the one component fits, we set up our input file to have a section for measuring the level of the sky background, and another section for fitting a S\'ersic profile to galaxy.
+The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.}
 
@@
 
-\item[The mask image]{The first step is to create a mask image that has the same dimensions as our input image with each pixel value as zero.
-We again use Source Extractor to compile a list of all the objects in the input image, and then use this list to replace the pixel values in our mask with one.
-We replace the areas of the mask that have detected sources with ones, thus creating a binary image.
-\textsc{Galfit} uses the mask image to }
+\item[The mask image]{The first step in making the mask is to create an image that has the same dimensions as our input image but with each pixel value equaling zero.
+We again use Source Extractor to compile a list of all the objects in the input image, and  use this list to replace the pixel values at the coordinates of the located objects with one.
+\textsc{Galfit} uses the mask image to ignore any objects neighboring our galaxy while it is completing the fit.}
 
-\item[The constant file]{The constraint file hosts the limits we are willing to accept for our fits.
-We fit on the following galaxy parameters: x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
-The constraints in place for these variables are listed in \autoref{constrtable}.}
+\item[The constant file]{The constraint file hosts the limits we are willing to accept for each of the fit parameters.
+The constraints for x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle for the one component fits are listed in \autoref{constrtable}.
+}
 
@@
 position angle & -360 -- 360 \\ \hline
-
 \end{tabular}
@@
 
-With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit.
-With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc.
-The core will be the smaller of the two components fit by \textsc{Galfit}.
+We use all of the above to obtain a one component, deconvolved fit for every galaxy in the RESOLVE survey.
+We then perform the two component fits as follows.
+We use the output of the one component fit as the basis of the input file for the two component fit.
+The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed).
+We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit.
+This gives \textsc{Galfit} an idea to fit on both a core and envelope.
+The PSF, image, and mask image will all be the same as before.
+We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section.
+In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit.
+The constraints for each parameter are the same for both sets.
+We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over constrain our fits.
+
+For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.
+Figure XX shows the output for three different galaxies in RESOLVE.
 
 \subsubsection{Selection of CCGs}
-\label{ccgsel}
 
-\noindent We use the AIMSS sample to select a maximum radius for our CCGs: 800 pc.
+Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies.
+We use the AIMSS sample to select a maximum cutoff core-only radius for CCGs at 800 pc.
 This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs.
-RESOLVE's lower stellar mass limit (quote, and include in RESOLVE section above) restricts us from reaching down to UCD masses.
+RESOLVE's lower stellar mass limit of  restricts us from reaching down to UCD masses.
 
-Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B).
-Figure 1 shows their distribution in stellar mass and \Reff\ compared to other RESOLVE galaxies and the AIMSS CSSs.
+We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc.
+Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
+We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored".
+After this selection, we are left with 124 galaxies in the CCG candidate sample.
 
-\section{Data and Methods}
+Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic fit is constrained to always be larger than that of the first S\'ersic fit, and (3) the S\'ersic n of the second component is held constant at 1 for an exponentially decreasing disk profile.
+We let the values of \Reff, the integrated magnitude, b/a ratio, and PA change for both fits.
+By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic fit) and disky envelope (the second S\'ersic fit) for each CCG candidate.
+
+We then examine the fits by eye and create our final CCG sample by selecting where the core \Reff\ $< 800$ pc and $\chi^2/\nu < 1.3$ to again exclude poor fits.
+Our sample is thus comprised of 96 CCGs in total (63 from RESOLVE-A and 33 from RESOLVE-B).
+This represents $\sim6$\% of the total RESOLVE galaxy sample.
+\autoref{fig:radius} shows their distribution in stellar mass and decomposed \Reff\ compared to other RESOLVE galaxies and the AIMSS cEs and dEs.
+For the RESOLVE sample, we are plotting the one component fits
+
+We quantify the amount of light in the core vs.
+the envelope by taking a ratio of the fluxes of the core and the envelope.
+The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
+There areWhen \textsc{Galfit} cannot find a core or an envelope, it will sometimes fit instead an extremely large and faint component instead.
+Where this happens (5 out of 124 cases), we classify this fit as either all core/envelope depending on which component was bad.
+We also see in 4 out of the 124 cases that the \Reff\ values for each component will be exactly the same value.
+When this occurs, we classify the galaxy as being all core.
+
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics{Reff_Mstars.eps}
+\caption{We plot here the deconvolved \Reff\ measurements for the}
+\label{fig:radius}
+\end{center}
+\end{figure*}
+
+\section{Methods}
 \label{methods}
 
-\subsection{Photometry: colors, stellar masses, and star formation rates}
+\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
 \label{phot}
-\noindent The RESOLVE survey overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo.
+\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
+We reprocess this photometric data in a custom way in order to improve upon the standard SDSS pipeline photometry with improved sky subtraction following Blanton et al.
+(2011) and use additional sky subtraction for 2MASS and UKIDSS.
+and use it to derive galaxy colors, stellar and baryonic masses, and star formation rates.
 \citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.
+
+Our reprocessed photometry improves over SDSS pipeline photometry in several key ways.
+First, we use images with improved sky subtraction coming from either Blanton et al.
+(2011) for SDSS or our own additional sky subtraction for 2MASS and UKIDSS.
+Second, we use the sum of the high S/N gri images to define the elliptical apertures, allowing us to determine the PA and axial ratio of the outer disk if present.
+Third, we apply these same elliptical apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by the original automated survey pipeline in certain bands, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
+Lastly, we use two to three non-parametric methods of total magnitude exrapolation, measuring the light from each band independently (see Figure 2 and 3.1.2).
+This last point allows for color gradients within galaxies, as opposed to the model magnitudes provided by SDSS (more details in 3.1.3), and allows us to measure systematic errors on magnitudes.
+We provide a comparison of the magnitudes, colors, and radii with photometry from the DR7 catalog of SDSS in Figure 3 and 3.1.3.
+Briefly summarizing, we find that the newly reprocessed photometry yields brighter magnitudes and larger effective radii.
+The colors tend to be bluer for large objects, which we believe to be a consequence of both the improved sky subtraction from Blanton et al.
+(2011) and the fact that we allow color gradients in magnitude estimation.
+The newly reprocessed photometry does not create a tight red sequence on the color-magnitude relation as seen in the DR7 photometry, however we argue that the tight red sequence may be a consequence of these two issues in ¤3.1.3.
+We also dis- cuss an independent validation of our methods with the NFGS survey (shown in Figure 2a of K13) in 3.1.3.
+
+Stellar masses and star formation rates are then derived from these colors using the stellar population synthesis code described in
+
+To calculate stellar masses and colors, we use the
+spectral energy distribution (SED) modeling code described in Kannappan \& Gawiser (2007), Kannappan et al.
+(2009), and K13, which fits our newly reprocessed total NUVugrizY JHK magnitudes to a grid of stellar population models.
+With up to 9 or 10 bands of photo- metric data in ECO and RESOLVE-B respectively, we can estimate robust stellar masses.
+In RESOLVE-B we exclude the UKIDSS data if they are flagged due to sky background or image artifact issues (E15).
+We do not use UKIDSS J and we exclude H and K band data if they are fainter than 18 and 17.5 mag respectively.
+We exclude 2MASS JHK data if they are fainter than 16, 15, and 14.5mag respectively.
+We exclude any NUV data fainter than 24 mag.
+In this work we consider two model sets to determine
+how robust the mass function shape is to changes in IMF and star formation history.
+Both model grids consist of an old and young population, yielding a composite stellar population (CSP), including an old population and
 
@@
 \noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
-\citet{Moffett2015}
+We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy.
+The group halo mass allows us to look for CCGs that are M32--Andromeda analogs where tidal stripping may be at play, or conversely look for CCGs in large groups where ram-pressure stripping could occur.
+The distance to neighboring galaxies lets us examine if interaction may occur or look for analogs of the isolated galaxies found by \citet{Huxor2013} and \citet{Paudel2014}.
+
+Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006}, and the masses of these group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}.
+More information on group identification can be found in \citet{Moffett2015}.
+The nearest neighbor distances are computed using the RA, Dec, and redshifts of each galaxy and along with spherical geometry principles.
 
@@
 We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup.
-From this absorption-line setup, we are able to derive velocity dispersions.
-We use the supremely-efficient 2100 l/mm VPH grating and cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335.
+With this absorption-line setup, we are able to derive velocity dispersions.
+We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335.
 To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.
 
-The
+The reduction process is as follows: we use standard IRAF tasks to perform bias and overscan subtraction, trimming of the science data to remove unnecessary spatial coverage, and flat fielding.
+We then use \texttt{LA\_COSMIC} \citep{vanDokkum2001} to clean cosmic rays from each science exposure.
+We next complete a wavelength calibration and transformation, and then perform object tracing and extraction into a 1D spectrum using the IRAF task apall.
+We lastly combine the individual exposures using the IRAF task scombine.
 
@@
 Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed.
-We then stack the individal fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
-More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix A.
+We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
+More information on the data reduction for the Gemini GMOS IFU can be found in  Appendix A.
 
@@
 
-\noindent We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
-This code fits many model spectra (cite Maraston) to the observed input spectrum.
+\noindent We then derive $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
+This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$.
+A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skews the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy.
+Future work will include implementing a stellar rotation subtraction routine for these fits, but preliminary testing by binning the spectra to $1''$ instead of to \Reff\ shows little change between the derived $\sigma$ values.
 
@@
 \subsection{Colors and Star formation rates}
-\noindent 
-* FIGURE: FSMGR vs Mbary/stars for RESOLVE, CCGs, and AIMSS \\
-* FIGURE: SFR vs. Mbary/stars for RESOLVE, CCGs, and AIMSS \\
 
-\noindent Figure \#A shows the u-r colors of our CCG sample plotted against M$_{\rm bary}$, compared to the RESOLVE sample as a whole.
-An unsual finding is that XX CCGs live on the blue sequence, a previsouly rare color for CSSs.
+\begin{figure*}[t!]
+\begin{center}
+\includegraphics[scale=0.65]{sfr_mbary.eps}
+\caption{default}
+\label{flg:fsmgr}
+\end{center}
+\end{figure*}
+
+\noindent The left side of \autoref{fig:envplot} shows the $u-r$ colors of our CCG sample plotted against M$_*$, compared to the RESOLVE sample as a whole.
+An unusual finding is that many CCGs live on the blue sequence, a previously rare color for CSSs.
 REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".
 
-Figure \#B shows FSMGR vs.
+The right side of \autoref{fig:envplot} shows FSMGR vs.
 M$_{\rm bary}$ for the same objects.
-As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr).
+As with the colors, we find that many CCGs are forming stars at a rapid rate (> 1 per Gyr).
 This again goes against the common thought that CSSs are ``red and dead".
-
-Here discuss more the envelope vs non-enveloped CCGs and how their popultions may differ.
 
@@
 * Tie in Huxor's cE, idea of ejection from groups, how environment would effect CCGs
+
+\begin{figure*}[t]
+\begin{center}
+\includegraphics{nn_groupmass.eps}
+\caption{default}
+\label{fig:envplot}
+\end{center}
+\end{figure*}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CCG formation and evolution} %kind of like a discussion section
+%\section{CCG formation and evolution} %kind of like a discussion section
 
@@
 
+\begin{table*}[b]
+\caption{default}
+\begin{center}
+\begin{tabular}{cccccccc}\hline \hline
+\# & name & RA & Dec & core \Reff\ [pc] & envelope \Reff\ [pc] & $\chi^2/\nu$ & log(flux$_{core}$/flux$_{envelope}$) \\ \hline
+1 & rs0003 & 133.68635 & 4.3019552 & 821.463 & 821.463 & 1.18600 & 1.00000  \\
+2 & rs0178 & 149.91796 & 3.2930701 & 397.295 & 1406.25 & 1.16500 & -0.184240  \\
+3 & rs0226 & 153.10508 & 1.2459080 & 632.824 & 3156.16 & 1.21900 & 0.297680  \\
+4 & rs0241 & 155.57380 & 0.010365953 & 445.272 & 884.769 & 1.07200 & -0.904000 \\
+5 & rs0246 & 155.77914 & 1.0061422 & 533.968 & 1056.30 & 1.08500 & 0.697800 \\
+6 & rs0264 & 156.83775 & 0.42236355 & 489.703 & 1015.89 & 1.17800 & -0.292520 \\
+7 & rs0284 & 158.11599 & 3.9140821 & 438.697 & 1239.27 & 1.16200 & -0.539200 \\
+8 & rs0297 & 159.47069 & 4.8132268 & 712.400 & 768.898 & 1.07100 & -0.568280 \\
+9 & rs0345 & 163.22317 & 4.5062644 & 414.999 & 966.451 & 1.06700 & -0.243041 \\
+10 & rs0350 & 163.69943 & 2.9479643 & 772.270 & 1584.13 & 0.952000 & 0.394559 \\
+11 & rs0364 & 165.21139 & 4.3915459 & 538.817 & 1612.12 & 1.16000 & -0.158081 \\
+12 & rs0419 & 169.33097 & 2.8817070 & 252.336 & 1002.62 & 1.03500 & -0.111560 \\
+13 & rs0422 & 169.39304 & 2.7726236 & 752.425 & 1189.52 & 1.09100 & 0.0501595 \\
+14 & rs0424 & 169.54402 & 2.6007993 & 463.767 & 1092.22 & 1.18400 & -0.672560 \\
+15 & rs0485 & 172.24999 & 3.8540120 & 584.173 & 803.029 & 1.17200 & -0.519680 \\
+16 & rs0493 & 172.55178 & 3.8010930 & 837.815 & 849.963 & 1.04200 & -0.351080 \\
+17 & rs0511 & 173.51621 & 2.9734660 & 650.023 & 1211.75 & 1.04000 & -0.101080 \\
+18 & rs0529 & 174.73052 & 3.6007886 & 444.960 & 1989.59 & 1.18600 & -0.142760 \\
+19 & rs0541 & 175.29068 & 4.6257403 & 560.561 & 1411.80 & 1.06800 & 0.846080 \\
+20 & rs0559 & 176.80368 & 2.5339341 & 460.211 & 1210.71 & 1.11800 & -0.160679 \\
+21 & rs0567 & 177.62803 & 1.9833304 & 203.049 & 2150.17 & 1.08800 & 0.165200 \\
+22 & rs0586 & 179.25994 & 0.49846395 & 519.351 & 807.097 & 1.12600 & -0.110800 \\
+23 & rs0596 & 180.30504 & 2.0499671 & 499.161 & 2119.90 & 1.08000 & 0.856960 \\
+24 & rs0623 & 180.73707 & 1.3937952 & 475.008 & 1019.83 & 1.13200 & -0.307200 \\
+25 & rs0640 & 180.90099 & 3.7565363 & 571.896 & 1138.14 & 1.14900 & -0.797760 \\
+26 & rs0662 & 181.05450 & 1.9002092 & 800.801 & 1212.27 & 1.07800 & 0.867321 \\
+27 & rs0663 & 181.06209 & 1.8667357 & 833.690 & 1576.26 & 1.09800 & 0.690200 \\
+28 & rs0666 & 181.07212 & 1.9175187 & 432.492 & 432.492 & 0.998000 & 1.00000 \\
+29 & rs0685 & 181.15300 & 1.8926987 & 270.945 & 471.503 & 1.02400 & -0.231679 \\
+30 & rs0692 & 181.19149 & 1.8039932 & 299.521 & 1419.81 & 1.14800 & -0.238760 \\
+31 & rs0693 & 181.19332 & 2.0052805 & 577.377 & 3597.03 & 1.10500 & 1.00000 \\
+32 & rs0706 & 181.32842 & 1.6376421 & 186.636 & 854.695 & 1.06100 & -1.00000 \\
+33 & rs0744 & 182.42105 & 0.65773495 & 361.692 & 915.910 & 1.00200 & 0.225360 \\
+34 & rs0749 & 182.62971 & 0.67284561 & 404.559 & 501.619 & 0.703000 & 0.753240 \\
+35 & rs0782 & 183.89462 & 1.2864481 & 450.290 & 848.580 & 1.11100 & -0.164360 \\
+36 & rs0812 & 185.76816 & 3.6659076 & 492.992 & 2409.71 & 1.12600 & 1.31604  \\
+37 & rs0814 & 185.81878 & 4.8360734 & 480.111 & 1499.67 & 1.15000 & 0.287200 \\
+38 & rs0840 & 187.42097 & 0.25347730 & 641.957 & 919.368 & 1.09300 & 0.0679602 \\
+39 & rs0862 & 187.93979 & 0.45263727 & 814.029 & 1199.91 & 1.17600 & 0.334680 \\
+40 & rs0869 & 188.68743 & 0.36667434 & 352.165 & 1889.67 & 1.21200 & 0.109560 \\
+41 & rs0906 & 191.31812 & 2.4491060 & 483.224 & 2456.56 & 1.11800 & 0.419680 \\
+42 & rs0972 & 197.87107 & 3.6874893 & 730.731 & 889.397 & 1.00900 & 0.793440 \\
+43 & rs0995 & 198.99419 & 2.9514062 & 836.917 & 2778.09 & 1.17400 & 0.653160 \\
+44 & rs1001 & 199.42659 & 3.6036901 & 692.197 & 855.021 & 1.13400 & 0.111879 \\
+45 & rs1053 & 201.81573 & 4.2087658 & 653.203 & 1401.12 & 1.10500 & 0.00380042 \\
+46 & rs1091 & 203.50670 & 1.0961109 & 278.757 & 833.818 & 1.08000 & 0.361680 \\
+47 & rs1094 & 203.52381 & 4.7805252 & 796.666 & 5662.08 & 1.09100 & 1.00000 \\
+48 & rs1100 & 203.64064 & 4.9188438 & 817.006 & 914.505 & 1.05000 & -0.856239 \\
+49 & rs1103 & 203.71245 & 4.2369242 & 358.480 & 1186.76 & 1.14700 & 0.175280 \\
+50 & rs1128 & 204.34076 & 4.6890855 & 604.906 & 1514.74 & 1.17300 & 0.135961 \\
+51 & rs1359 & 204.71440 & 4.4317127 & 513.871 & 1451.63 & 1.14900 & -0.0193595 \\
+52 & rs1172 & 205.14099 & 4.8202809 & 385.743 & 927.874 & 1.12800 & -0.170840 \\
+53 & rs1180 & 205.38541 & 4.1942047 & 603.266 & 1102.00 & 1.29500 & -0.188240 \\
+54 & rs1186 & 205.49539 & 4.7635971 & 605.924 & 1193.42 & 0.968000 & 0.512960 \\
+55 & rs1207 & 206.55280 & 3.5059126 & 432.668 & 1470.88 & 1.05300 & 0.281721 \\
+56 & rs1208 & 206.60028 & 1.5787812 & 679.536 & 1019.00 & 1.24500 & -0.584320 \\
+57 & rs1257 & 211.35992 & 3.0333434 & 657.017 & 928.701 & 1.09100 & -0.214119 \\
+58 & rs1259 & 212.19482 & 4.9098567 & 340.962 & 982.659 & 1.12200 & -0.370719 \\
+59 & rs1270 & 216.07293 & 4.6996761 & 587.943 & 1259.93 & 1.08200 & -0.164520 \\
+60 & rs1291 & 224.22974 & 4.2051356 & 739.350 & 1137.16 & 1.22400 & 0.0689202 \\
+61 & rs0287 & 158.77285 & 0.28142271 & 411.813 & 840.318 & 1.08800 & -0.803640 \\
+62 & rs1453 & 200.69881 & 3.7793812 & 324.608 & 792.803 & 1.20200 & -0.284640 \\
+63 & rs1456 & 205.20741 & 2.8178559 & 391.510 & 391.510 & 1.08600 & 1.00000 \\
+64 & rf0518 & 2.2105393 & -1.1702019 & 465.731 & 2196.11 & 1.13900 & 0.114200 \\
+65 & rf0003 & 2.3154592 & 0.81264576 & 686.760 & 686.760 & 0.971000 & 1.00000 \\
+66 & rf0078 & 15.724560 & -0.31966061 & 355.476 & 1137.93 & 0.821000 & 0.300120 \\
+67 & rf0563 & 16.109272 & -0.65961046 & 822.314 & 3972.25 & 1.17600 & 1.00000 \\
+68 & rf0568 & 16.747559 & -0.59600971 & 552.735 & 1257.87 & 1.21100 & -0.313640 \\
+69 & rf0143 & 18.353539 & 0.22052619 & 689.135 & 1033.19 & 1.08300 & -0.0775604 \\
+70 & rf0154 & 18.903888 & -0.95294103 & 789.710 & 20578.8 & 1.12200 & 1.00000 \\
+71 & rf0179 & 21.123601 & -0.36943684 & 549.049 & 2260.41 & 1.26300 & 0.585001 \\
+72 & rf0195 & 21.478055 & -0.98781101 & 718.558 & 2522.79 & 1.16500 & 0.523720 \\
+73 & rf0197 & 21.556976 & 0.35858673 & 245.635 & 686.455 & 1.08200 & -0.577440 \\
+74 & rf0217 & 21.968796 & -0.50420076 & 801.105 & 27583.3 & 1.19900 & 1.00000 \\
+75 & rf0229 & 22.801921 & -0.61075471 & 644.919 & 3473.07 & 1.10000 & 0.413480 \\
+76 & rf0241 & 23.436054 & 0.95319263 & 623.932 & 945.284 & 1.20000 & 1.00000 \\
+77 & rf0243 & 23.531574 & -1.0483175 & 681.056 & 1421.28 & 1.18200 & -0.148561 \\
+78 & rf0247 & 23.786680 & 0.71782400 & 569.185 & 1700.14 & 1.14600 & 1.00000 \\
+79 & rf0250 & 24.296472 & 0.88248657 & 486.472 & 10812.0 & 1.08600 & 1.00000 \\
+80 & rf0253 & 24.678808 & -0.34802671 & 183.131 & 739.562 & 1.15800 & 0.0172801 \\
+81 & rf0266 & 28.224302 & -0.90206277 & 181.014 & 693.328 & 1.18200 & -0.262840 \\
+82 & rf0280 & 28.693912 & -0.73893120 & 513.218 & 27731.2 & 1.20300 & 1.00000 \\
+83 & rf0663 & 34.464996 & 1.2245195 & 762.472 & 2440.96 & 1.19500 & 0.141921 \\
+84 & rf0328 & 37.152547 & -0.24656214 & 442.135 & 1714.92 & 1.18400 & 0.339000 \\
+85 & rf0332 & 37.413698 & 0.12338943 & 671.104 & 682.327 & 1.27800 & -0.486200 \\
+86 & rf0340 & 37.926994 & 1.1969289 & 810.561 & 810.561 & 1.10000 & 1.00000 \\
+87 & rf0352 & 38.090155 & 1.1750138 & 675.498 & 1220.81 & 1.13000 & 1.06556 \\
+88 & rf0365 & 38.209305 & 0.66106589 & 384.276 & 682.691 & 1.12700 & -0.306679 \\
+89 & rf0367 & 38.211703 & 1.1492129 & 471.387 & 1604.43 & 1.16400 & -0.0500407 \\
+90 & rf0707 & 40.340884 & 0.058162170 & 464.822 & 1112.55 & 1.14000 & 0.304760 \\
+91 & rf0392 & 41.594894 & -1.1714824 & 742.347 & 47400.9 & 1.21200 & 1.00000  \\
+92 & rf0419 & 330.45871 & -0.70729601 & 447.720 & 1181.10 & 1.20200 & -0.706640 \\
+93 & rf0479 & 353.17151 & -0.75714491 & 507.162 & 1799.10 & 1.18800 & -0.132120 \\
+94 & rf0492 & 356.07298 & 0.44182044 & 232.505 & 1118.50 & 1.09600 & 0.00903985 \\
+95 & rf0503 & 358.09449 & -0.62866731 & 356.736 & 2299.10 & 0.883000 & 0.314640 \\
+96 & rf0505 & 358.63499 & -0.046906637 & 785.406 & 785.406 & 1.17100 & 1.00000 \\
+
+\\ \hline\hline
+
+\end{tabular}
+\end{center}
+\label{default}
+\end{table*}%
+
+\section{Appendix}
+
 \bibliographystyle{apj}
@@
 
-\section{Appendix}
-
 \end{document}

### 2016-04-18 paperdraft.tex
more new pics
first draft!

--- 2016-04-12 paperdraft.tex
@@
 \usepackage{natbib}
+\usepackage{epstopdf}
+\usepackage{longtable}
 \usepackage{amsmath,amstext,textcomp}
@@
 
-\title{The Formation and Evolution of Compact Core Galaxies in the RESOLVE Survey}
+\title{Compact Core Galaxies in the RESOLVE Survey}
 \author{Elaine M. Snyder\altaffilmark{1}}
@@
 \author{Ashley S. Bittner\altaffilmark{1}}
-\author{Christine Ray\altaffilmark{1,4}}
 \author{Kathleen D. Eckert\altaffilmark{1}}
+\author{Amanda J. Moffett\altaffilmark{1,4}}
+\author{David V. Stark\altaffilmark{1}}
 \author{the RESOLVE Team}
-\affil{$^1$University of North Carolina at Chapel Hill}
-\affil{$^2$National Optical Astronomical Observatory}
-\affil{$^3$University of Central Lancashire}
-\affil{$^4$Rutgers, The State University of New Jersey}
+\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599,
+USA}
+\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
+\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
+\affil{$^4$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
+way, Crawley, WA 6009, Australia}
 \begin{abstract}
-We analyze the complete set of compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments.
-CCGs include both compact ellipticals (cEs) and compact cores surrounded by an envelope of gas and stars, which may represent earlier or later evolutionary stages of cEs.
-We select CCGs to have core-only radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
-CCGs naturally occur in a range of environments from isolated to cluster.
-With GALEX NUV data, we derive star formation histories and find that a significant number of CCGs have recently formed stars.
-We compare velocity dispersions of CCGs derived from Gemini IFU data to velocity dispersions of other RESOLVE galaxies derived from SOAR spectroscopy.
+We analyze the complete set of 96 compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments.
+We perform one and two component S\'ersic fits on the galaxies in the RESOLVE sample using \textsc{Galfit} to produce seeing-deconvolved effective radius (\Reff) measurements.
+These one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we subsequently perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
+We finalize the CCG sample for those galaxies with core-only (first component) radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
+We quantify the amount of light in the core and envelope of each CCG by performing fixed two S\'ersic fits on UKIDSS $Y$-band imaging, and taking the ratio of the fluxes in each component.
+The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated.
+With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive the colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars.
+We find that CCGs naturally occur in a range of environments from isolated to cluster.
+We compare velocity dispersions of CCGs derived from Gemini IFU data and SOAR spectroscopy to velocity dispersions of other RESOLVE galaxies.
 We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
@@
 
-\keywords{galaxies: formation; galaxies: evolution}
+\keywords{galaxies: formation, evolution --- surveys}
 \maketitle
@@
 
-\noindent The term compact stellar system (CSS) composes a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es).
+\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es).
 Different types of CSSs include ultra compact dwarf galaxies (UCDs; \citet{Phillipps2001}), compact elliptical galaxies (cEs; \citet{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).
-There are many unanswered questions about these types of galaxies, typically involving how they form and evolve.
-One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are in an intermediate and short-lived evolutionary phase, or simply hard to find due to their size.
+There are many unanswered questions about CSSs, typically involving how they form and evolve through time.
+One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size.
 Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.
 
-\subsection{Introduction to UCDs}
 UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \citet{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\citet{Drinkwater2000}, \citet{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\citet{Bekki2001}, \citet{Bekki2003}, \citet{Jennings2015}, \citet{Zhang2015}).
-Meanwhile, \citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546.
-\citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy.
+\citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546.
+\citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy, lending more evidence toward tidal stripping being a common for UCDs.
 
- \subsection{Introduction to cEs}
-cEs, the intermediate-sized CSSs of the three previously mentioned have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}).
-They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (Choi, Guhathakurta \& Johnson 2002, Graham 2002), or as a part of the low mass extension to the elliptical galaxy population.
-The evidence for tidal stripping includes finding tidal streams near cEs (Smith Castelli 2008, Chilingarian 2009) and one cE, studied in Kormendy 1997 that is believed to host a central massive black hole.
-(Threshed spiral scenario: Davidge, Beck \& McGregor 2008).
-On the other hand, Kormendy \& Bender 2012 argue that cEs can be the extension of normal elliptical galaxies, based on
+Meanwhile, cEs have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}).
+They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (\citet{Choi2002}, \citet{Graham2002}), or as a part of the low mass extension to the elliptical galaxy population.
+The evidence for tidal stripping includes finding tidal streams near cEs (\citet{SmithCastelli2008a}, \citet{Chilingarian2009}) and one cE, studied in \citet{Kormendy1997} that is believed to host a central massive black hole.
+On the other hand, \citet{Kormendy2012a} argue that cEs are the extension of normal elliptical galaxies.
 
-\subsection{Introduction to dEs and dE,Ns}
 dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \citet{Norris2014}).
-Similarly to cEs, dEs and dE,Ns are though to be tidally stripped remnants (Crnojevic 2014 - dEs in M31 show signs of tidal stripping) or the low mass extension to elliptical galaxies (Steve Crawfords work on high-z LCBDs).
+Similarly to cEs, dEs and dE,Ns are thought to be either tidally stripped remnants (\citet{Crnojevi2014} find dEs in M31 that show signs of tidal stripping) or the low mass extension to elliptical galaxies \citep{Crawford2016}.
 They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched.
@@
 
-\subsection{Environments of UCDs}
-UCDs have been primarily found in clusters, such as Coma (\citet{Price2009}, \citet{Madrid2010}), Fornax (\citet{Hilker1999}, \citet{Drinkwater2000}), Virgo (\citet{Hasegan2005}, \citet{Jones2006}), Centaurus (\citet{Mieske2009}), and Hydra I (\citet{Wehner2007}, \citet{Misgeld2008}).
-Fewer UCDs have been found in groups: \citet{Evstigneeva2007} find one definite and two candidate UCDs in the Dorado group as well as two candidates in the NGC1400 group.
-Addititonally, \citet{Hau2009} find a UCD near the Sombrero galaxy.
+Clues to how a CSS is formed may be given by their environments.
+UCDs, cEs, dEs have all been found in clusters (for UCDs:\citet{Price2009}, \citet{Madrid2010}, \citet{Hasegan2005}, \citet{Jones2006}, \citet{Mieske2009}, \citet{Wehner2007}, \citet{Misgeld2008}; for cEs: \citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}; and dEs: \citep{SmithCastelli2012}, \citet{Koo1994}, \citet{Guzman1996}, \citet{Crawford2016}).
+Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups.
+Lastly, only cEs have been found in isolated environments: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$ Mpc.
 
-\subsection{Environments of cEs}
-cEs suffer the same issue: they are mainly found in clusters (\citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}) and groups (Chilingarian \& Bergond 2010, \citet{Huxor2011}), but recently more have been found in an isolated environment.
-\citet{Huxor2013}, \citet{Paudel2014}.
-There is also recent work by Chilingarian 2015 that finds more isolated
+Given the similarities in formation scenarios and environments for these CSSs, we propose to study these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff\ sizes.
+Critical to this study is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments.
+Previous studies have mainly focused on selecting targets in the group/cluster environments, since this route is often more convenient.
+Our goal is thus to create a complete and volume-limited sample of compact galaxies across all environments so that we may examine their formation and evolution.
 
-\subsection{Environments of dEs}
-dEs have also primarily been found in groups -- Crnojevic et al.
-2014 - dEs in M31, Penny 2014) and clusters (\citep{SmithCastelli2012}, Koo 1994, Guzman 1996, Michielson 2008, Steve Crawford's papers).
-
-\subsection{How environments impact formation scenarios}
-Thus, there's been no ubiquitous sample of CSSs that allow us to analyze the formation as a function of all environments.
-These studies mostly focus on selecting targets in the group/cluster environments, since this route is more convenient.
-Only recently have CSSs been found in the field environment (\citet{Huxor2013}, \citet{Chilingarian2015}), which highlights the need for a statistical census of CSSs that spans the group to cluster to field environments.
-
-\noindent Our goal is to create a complete and volume-limited sample of compact galaxies across all environments so that we may study their evolutionary sequences.
-For this, we derive our sample from the RESOLVE survey, as described in (\autoref{resolve}).
-We also use the objects in the Archive of Intermediate Mass Stellar Systems (AIMSS) for comparisons to our sample (\autoref{aimss}).
-We describe our sample selection process in \autoref{samples} and lastly, describe our spectroscopic data collection and analysis in \autoref{methods}.
+This paper presents the preliminary results of this work, characterizing the colors, star formation histories, environments, and preliminary kinematics of the first complete, volume-limited sample of CCGs.
+The paper is organized as follows.
+We explain our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} in \autoref{deconv}.
+We then explain the selection of the CCG sample from the RESOLVE survey in \autoref{CCGs}.
+We then describe our photometric and spectroscopic data and analysis in \autoref{methods}.
+We gives our results in \autoref{results}.
+Lastly, our results are summarized in \autoref{conclusions}.
 
@@
 With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively.
-We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}).
+We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2016}).
 In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
@@
 position angle & -360 -- 360 \\ \hline
-
 \end{tabular}
 \end{center}
-\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
+\caption{Summary of the constraints imposed on our \textsc{Galfit} models for our initial one component fits for the entire RESOLVE sample.}
 \label{constrtable}
@@
 
-With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit.
-With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc.
-The core will be the smaller of the two components fit by \textsc{Galfit}.
+\noindent We use all of the above to obtain a one component, deconvolved fit for every galaxy in the RESOLVE survey.
+We then perform the two component fits as follows.
+We use the output of the one component fit as the basis of the input file for the two component fit.
+The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed).
+We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit.
+This gives \textsc{Galfit} an idea to fit on both a core and envelope.
+The PSF, image, and mask image will all be the same as before.
+We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section.
+In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit.
+The constraints for each parameter are the same for both sets.
+We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over constrain our fits.
+
+For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.
 
 \subsubsection{Selection of CCGs}
-\label{ccgsel}
+\label{CCGs}
 
-\noindent We use the AIMSS sample to select a maximum radius for our CCGs: 800 pc.
+\begin{figure*}[t]
+\begin{center}
+\includegraphics{CCGpics.eps}
+\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to envelope+core to core-only.
+Images are taken from the SDSS-DR8 image list tool.
+The central image is rf0492, a CCG with possible ram pressure stripping origins (see \autoref{kin}).}
+\label{fig:pics}
+\end{center}
+\end{figure*}
+
+\noindent Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies.
+We use the AIMSS sample to select a maximum cutoff core-only radius for CCGs at 800 pc.
 This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs.
-RESOLVE's lower stellar mass limit (quote, and include in RESOLVE section above) restricts us from reaching down to UCD masses.
+RESOLVE's lower stellar mass limit of  restricts us from reaching down to UCD masses.
 
-Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B).
-Figure 1 shows their distribution in stellar mass and \Reff\ compared to other RESOLVE galaxies and the AIMSS CSSs.
+We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc.
+Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
+We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored".
+After this selection, we are left with 124 galaxies in the CCG candidate sample.
 
-\section{Data and Methods}
+Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic fit is constrained to always be larger than that of the first S\'ersic fit, and (3) the S\'ersic n of the second component is held constant at 1 for an exponentially decreasing disk profile.
+We let the values of \Reff, the integrated magnitude, b/a ratio, and PA change for both fits.
+By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic fit) and disky envelope (the second S\'ersic fit) for each CCG candidate.
+
+We then examine the fits by eye and create our final CCG sample by selecting where the core \Reff\ $< 800$ pc and $\chi^2/\nu < 1.3$ to again exclude poor fits.
+Our sample is thus comprised of 96 CCGs in total (63 from RESOLVE-A and 33 from RESOLVE-B).
+This represents $\sim6$\% of the total RESOLVE galaxy sample.
+\autoref{fig:radius} shows their distribution in stellar mass and decomposed \Reff\ compared to other RESOLVE galaxies and the AIMSS cEs and dEs.
+For the RESOLVE sample, we are plotting the one component fits, while for the CCGs, we are plotting the core \Reff\ from the fixed two component fits.
+
+We quantify the amount of light in the core vs.
+the envelope by taking a ratio of the fluxes of the core and the envelope.
+The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
+For each plot in this paper, we color code the CCGs by the logarithm of the flux ratio.
+CCGs with more light in the envelope will have log(flux ratio) $<$ 0, and will hereafter be called ``envelope-dominated' CCGs.
+CCGs with more light in the core will have log(flux ratio) $>$ 0, and will hereafter be called ``core-dominated'' CCGs.
+CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs.
+See \autoref{fig:pics} for examples of CCGs on this scale.
+There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead.
+Where this happens (5 out of 96 cases), we classify this fit as either all core/envelope depending on which component was bad (log(flux ratio) = -1 or 1).
+We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component.
+When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).
+
+We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
+There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
+
+\begin{figure*}[b]
+\begin{center}
+\includegraphics{Reff_Mstars.eps}
+\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CCSs of the AIMSS catalog.
+In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff.
+The CCG sample is using the core \Reff\ of the two component fits, which is why they may appear separated from the full RESOLVE sample.
+The colors of the CCGs represent the logarithm of the flux ratio between the core and envelope.
+Galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $\sim \pm 1$ will have more light in the core (+1) or envelope (-1).}
+\label{fig:radius}
+\end{center}
+\end{figure*}
+
+\section{Methods}
 \label{methods}
 
-\subsection{Photometry: colors, stellar masses, and star formation rates}
+\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
 \label{phot}
-\noindent The RESOLVE survey overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo.
-\citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.
+\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
+We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in \citet{Eckert2015}.
+The main differences in this processing are (1) improved sky subtraction following Blanton et al.
+(2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
+Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).
+
+Colors, stellar masses and fractional stellar mass growth rates (FSMGR) are then derived from these $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in \citet{Kannappan2007}, \citet{Kannappan2009}, and \citet{Kannappan2013}.
+FSMGR is similar to a star formation rate, but it instead gives the ratio of stellar mass created in the last Gyr to the stellar mass previously existing.
+Therefore, an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr.
+
+The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al.
+in prep.).
+We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.
 
@@
 
-\noindent As noted in the Introduction, the velocity dispersion of a galaxy is an extremely helpful tool when testing formation scenarios.
-We describe the data reduction and analysis to derive $\sigma$ for our CCG sample in this section.
-
 \subsubsection{SOAR spectroscopy}
@@
 
-\noindent We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
-This code fits many model spectra (cite Maraston) to the observed input spectrum.
+\noindent We then derive $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
+This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$.
+A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skews the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy.
+Future work will include implementing a stellar rotation subtraction routine for these fits, but preliminary testing by binning the spectra to $1''$ instead of to \Reff\ shows little change between the derived $\sigma$ values.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[scale=0.4]{rf0078ppxffit.eps}
+\caption{Plotted here in black is a summed Gemini-South IFU spectrum for the CCG rf0078.
+Overplotted in red is the pPXF best fit model spectrum.
+The spectrum is zoomed-in to show the MgB triplet fit at $\sim 5275$ \AA.}
+\label{fig:ppxffit}
+\end{center}
+\end{figure}
 
@@
 \section{Results}
+\label{results}
+\subsection{Colors and Star formation rates}
 
-\subsection{Colors and Star formation rates}
-\noindent 
-* FIGURE: FSMGR vs Mbary/stars for RESOLVE, CCGs, and AIMSS \\
-* FIGURE: SFR vs. Mbary/stars for RESOLVE, CCGs, and AIMSS \\
+\begin{figure*}[t!]
+\begin{center}
+\includegraphics[scale=0.65]{sfr_mbary.eps}
+\caption{\textbf{(a.)} On the left we plot the $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample.
+\textbf{(b.)} On the right we have plotted the FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample.
+}
+\label{fig:fsmgr}
+\end{center}
+\end{figure*}
 
-\noindent Figure \#A shows the u-r colors of our CCG sample plotted against M$_{\rm bary}$, compared to the RESOLVE sample as a whole.
-An unsual finding is that XX CCGs live on the blue sequence, a previsouly rare color for CSSs.
-REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".
+\noindent We begin by examining the colors of the CCG sample.
+The left side of \autoref{fig:envplot} shows the $u-r$ colors of our CCG sample plotted against M$_{\star}$, compared to the RESOLVE sample as a whole.
+An unusual finding is that many CCGs live on the blue sequence, since most CSSs are typically thought of as being ``red and dead''.
+The right side of \autoref{fig:envplot} shows FSMGR vs.
+M$_{\rm bary}$ for the same objects.
+As with the colors, we find that many CCGs are forming stars at a rapid rate (FSMGR $\sim1$ means that the galaxy has doubled its mass in the last Gyr), again an unexpected finding which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if a tidally-stripped remnant).
 
-Figure \#B shows FSMGR vs.
-M$_{\rm bary}$ for the same objects.
-As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr).
-This again goes against the common thought that CSSs are ``red and dead".
-
-Here discuss more the envelope vs non-enveloped CCGs and how their popultions may differ.
+Looking now at the log(flux ratio values), we see that red sequence CCGs tend to be more core-dominated, while blue sequence CCGs tend to me more envelope-dominated.
+There also tends to be more core-dominated CCGs at lower FSMGR, while envelope-dominated CCGs reside at higher FSMGR.
+There is considerable scatter though, making these trends harder to qualify.
 
 \subsection{Environments}
-\noindent 
- *FIGURE: nearest neighbor and group halo mass\\
-* FIGURE: group n vs group halo mass  \\
-* Tie in Huxor's cE, idea of ejection from groups, how environment would effect CCGs
+\noindent We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
+We see many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could be at play.
+On the opposite end, we see several CCGs in massive group halos, and that these tend to be either core- or envelope dominated CCGs.
+This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies.
+There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.
+
+\begin{figure*}[t]
+\begin{center}
+\includegraphics{nn_groupmass.eps}
+\caption{We plot here the group halo mass against the nearest 3D neighbor for the RESOLVE survey and CCG sample.
+We see that CCGs live in a variety of environments, from extremely isolated (nearest neighbor $>$ 1 Mpc) to massive (M$_{\rm halo} \sim 10^{13}$ M$_{\odot}$) groups.
+There is no obvious trend into whether cores+envelopes and cores/envelopes preferentially live in different environments.}
+\label{fig:envplot}
+\end{center}
+\end{figure*}
 
 \subsection{Kinematics}
-\noindent * why kinematics are important for formation scenario discernment\\
-* FIGURE: ppxf fits for spectroscopic data to derive velocity dispersions \\
-* FIGURE: velocity dispersion vs. stellar mass
+\label{kin}
+\noindent We lastly investigate the kinematics of the CCG sample using the $\sigma$s derived from SOAR and Gemini telescope data.
+\autoref{fig:sigma} plots the $\sigma$-M$_{\star}$ relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with measured $\sigma$s.
+Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since  they will have more  Conversely, $\sigma$s that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
+
+We find that most of the CCGs tend to follow the dissipative formation track.
+However, there is one CCG with a core+envelope that lies close to M32, a tidally stripped cE, in the relation.
+We now take a closer look at this CCG, rf0492.
+This CCG lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}.
+Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$.
+This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.
+
+\begin{figure*}[t!]
+\begin{center}
+\includegraphics{faber-jackson_resolvesigmas.eps}
+\caption{Here we plot the stellar mass vs.
+velocity dispersion ($\sigma$) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
+Most CCGs appear to be following the dissipative formation track.}
+\label{fig:sigma}
+\end{center}
+\end{figure*}
 
@@
 \section{Summary}
+\label{conclusions}
+
+\noindent In this paper we have examined the colors, FSMGR, environments, and kinematics of the 96 compact core galaxies (CCGs) in the RESOLVE survey.
+We have selected CCGs to have a seeing-deconvolved, core-only \Reff\ $<$ 800 pc, based on the sizes of the compact and dwarf ellipticals in the AIMSS catalog.
+We have quantified the amount of light in the cores and envelopes of each CCG by performing two component fits with \textsc{Galfit} and taking the logarithm of the ratio of the fluxes of the two different components.
+CCGs with more light in the envelope have log(flux ratio) $<$ 0 and are called ``envelope-dominated' CCGs.
+CCGs with more light in the core have log(flux ratio) $>$ 0 and are called ``core-dominated'' CCGs.
+CCGs with log(flux ratio) $\sim 0$ have both a bright core plus an extended envelope and are called ``core+envelope'' CCGs.
+Our main results can be summarized as follows:
+
+\begin{enumerate}
+\item \autoref{fig:radius} shows that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
+There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
+
+\item We find that many CCGs live on the blue sequence and are forming stars at a rapid rate (see \autoref{fig:fsmgr}), which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if a tidally-stripped remnant).
+
+\item We find that CCGs span a range of different environments (see \autoref{fig:envplot}).
+Many CCGs live in low mass groups, similar to the M32--Andromeda relationship, perhaps hinting at tidal stripping formation scenarios.
+Others live in massive group halos and tend to be either core- or envelope dominated CCGs, conversely hinting towards ram pressure stripping being at play.
+There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to a dissipative formation scenario.
+
+\item Using velocity dispersions ($\sigma$) derived from the SOAR and Gemini telescopes, we look for offsets in $\sigma$-M$_{\star}$ relation that could point to tidal stripping or dissipative formation scenarios (see \autoref{fig:sigma}).
+We find that CCGs tend to follow the dissipative formation track, however one CCG with a core+envelope lies close to M32, a tidally stripped cE, in the relation.
+\end{enumerate}
 
 \section{Future Work}
-%\subsection{Gas Content}
-%\noindent * look into g/s ratios \\
-%* reference Dave and Katie's work here
+\subsection{Gas Content}
+\noindent The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
+For example, a CCG in a galaxy cluster with little HI gas may point towards ram pressure stripping being important.
+Combined with CCG colors and FSMGR, the gas content may be an important tool in determining the evolution of a CCG.
 
-%\subsection{Metallicities}
-%\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{
-  Acknowledgments. 
+\subsection{Metallicities}
+\noindent \citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
+With the SOAR data we have in hand, we may be able to test this hypothesis for the CCG sample and use this method as another way to discern formation scenarios.
+
+\acknowledgments{ \textit{Acknowledgements.}
+  This work has been supported by funding from NSF grants AST-0955368 and OCI-1156614 and NASA grant HST-AR-12147.01-A. 
 }
@@
 
-\section{Appendix}
+\appendix
 

### 2016-04-18 paperdraft.tex
adding more plots

@@
 \author{the RESOLVE Team}
-\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599,
-USA}
+\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599, USA; emsnyder@live.unc.edu}
 \affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
@@
 \begin{abstract}
-We analyze the complete set of 96 compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies across a broad statistical distribution of environments.
-We perform one and two component S\'ersic fits on the galaxies in the RESOLVE sample using \textsc{Galfit} to produce seeing-deconvolved effective radius (\Reff) measurements.
-These one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we subsequently perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
-We finalize the CCG sample for those galaxies with core-only (first component) radius $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (ultra compact dwarfs, cEs, nucleated dwarf ellipticals) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
-We quantify the amount of light in the core and envelope of each CCG by performing fixed two S\'ersic fits on UKIDSS $Y$-band imaging, and taking the ratio of the fluxes in each component.
+We analyze the complete set of 96 compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments.
+We perform one and two component S\'ersic fits KIDSS for all galaxies in the RESOLVE sample with UKIDSS $Y$-band imaging using \textsc{Galfit}, which produces seeing-deconvolved effective radius (\Reff) measurements.
+The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
+We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs, dEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
+We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the fluxes in each component.
 The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated.
-With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive the colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars.
+With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars.
 We find that CCGs naturally occur in a range of environments from isolated to cluster.
-We compare velocity dispersions of CCGs derived from Gemini IFU data and SOAR spectroscopy to velocity dispersions of other RESOLVE galaxies.
+We compare velocity dispersions of CCGs derived from Gemini IFU data and SOAR spectroscopy to velocity dispersions of other RESOLVE galaxies and the cEs and and dEs of AIMSS.
 We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
@@
 Meanwhile, cEs have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}).
-They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (\citet{Choi2002}, \citet{Graham2002}), or as a part of the low mass extension to the elliptical galaxy population.
-The evidence for tidal stripping includes finding tidal streams near cEs (\citet{SmithCastelli2008a}, \citet{Chilingarian2009}) and one cE, studied in \citet{Kormendy1997} that is believed to host a central massive black hole.
-On the other hand, \citet{Kormendy2012a} argue that cEs are the extension of normal elliptical galaxies.
+They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (\citet{Choi2002}, \citet{Graham2002}), or as a part of the low mass extension to the E population.
+The evidence for tidal stripping includes finding tidal streams near cEs (\citet{SmithCastelli2008a}, \citet{Chilingarian2009}) and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
+On the other hand, \citet{Kormendy2012a} argue that cEs are the extension of normal E galaxies.
 
@@
 Clues to how a CSS is formed may be given by their environments.
-UCDs, cEs, dEs have all been found in clusters (for UCDs:\citet{Price2009}, \citet{Madrid2010}, \citet{Hasegan2005}, \citet{Jones2006}, \citet{Mieske2009}, \citet{Wehner2007}, \citet{Misgeld2008}; for cEs: \citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}; and dEs: \citep{SmithCastelli2012}, \citet{Koo1994}, \citet{Guzman1996}, \citet{Crawford2016}).
+UCDs, cEs, dEs have all been found in clusters (for UCDs: \citet{Price2009}, \citet{Madrid2010}, \citet{Hasegan2005}, \citet{Jones2006}, \citet{Mieske2009}, \citet{Wehner2007}, \citet{Misgeld2008}; for cEs: \citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}; and dEs: \citep{SmithCastelli2012}, \citet{Koo1994}, \citet{Guzman1996}, \citet{Crawford2016}).
 Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups.
@@
 
-Given the similarities in formation scenarios and environments for these CSSs, we propose to study these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff\ sizes.
+Given the similarities in formation scenarios and environments for these CSSs, we propose to study these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff.
 Critical to this study is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments.
@@
 Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted.
-AIMSS also includes literature data for (nucleated) dwarf ellipticals, dwarf spheroidals, dwarf S0s, young massive clusters, and massive elliptical galaxies.
+AIMSS also includes literature data for other UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es.
 AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects.
@@
 
-\noindent We begin our analysis by deriving seeing-corrected \Reff\ measurements for all galaxies in the RESOLVE sample.
+\noindent We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample.
 For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits on each galaxy.
@@
 
-\item[The initial input file]{The initial input file tells \textsc{Galfit} where to find the image, PSF, mask, and constraint, and also holds the initial guesses for our fit parameters.
-These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details).
+\item[The initial input file]{The initial input file gives \textsc{Galfit} the files paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters.
 For the one component fits, we set up our input file to have a section for measuring the level of the sky background, and another section for fitting a S\'ersic profile to galaxy.
-The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.}
+The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
+These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's photometric data (see \autoref{phot} for more details)}
 
@@
 While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful for constructing a PSF.
-There are  only XX galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis.
-Visual inspection of these galaxies indicate that they would most likely not be classified as CCGs anyways.
+There are only 24 galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis.
 
-\item[The PSF image]{We build our PSF image via the following steps.
+\item[The PSF image]{\textsc{Galfit} uses the PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken.
+We build our PSF image via the following steps.
 \begin{enumerate}
@@
 \item We begin by running Source Extractor on the image to identify every object in the frame, including stars, galaxies, and even sometimes hot pixels.
-Source Extractor outputs a .txt file that has estimates of each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.
+Source Extractor outputs a text file that has estimates of each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.
 
@@
 We also make sure the stars are not near the image edges, since there can sometimes be image artifacts there.
-Lastly, we make sure to not include the galaxy we are going to fit, since the cE-like galaxies can appear to be stars.
+Lastly, we make sure to not include the galaxy we are going to fit, since the cE-like galaxies can sometimes appear to be stars.
 
@@
 
-\item We also use the background median to reject any of the cutouts that have a background median greater than $2\sigma$ from the mean of all the background median values.
+\item We then reject any of the cutouts that have a background median value greater than $2\sigma$ from the mean of the background median values for every cutout.
 This ensures we are not including any cutouts that have stars with large or bright neighboring objects.
-We are now left with background-subtracted cutouts of stars with no neighbors that could effect our stacking.
+We are now left with background-subtracted cutouts of stars with no neighbors that could affect our stacking.
 
 \item Before we can combine all the cutouts, we must normalize the flux of each central star to the same amplitude.
-To do this, we run each cutout through Source Extractor once more to obtain the fluxes of each central star, and use these to weight the cutouts accordingly.
+To do this, we run each cutout through Source Extractor once more to obtain the fluxes of each central star and use these to weight the cutouts accordingly.
 We calculate the weight for each cutout as follows: (1) we find the central star with the highest flux of all the cutouts and then (2) divide every flux by this maximum flux.
@@
 \noindent Our last step is to fit a 2D Gaussian to the PSF to determine a rough estimate seeing full width half max (FWHM), as a sanity check.
-We find that the average FWHM for all PSFs is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.
-\textsc{Galfit} uses this PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken.}
+We find that the average FWHM for all PSFs is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.}
 
-\item[The mask image]{The first step in making the mask is to create an image that has the same dimensions as our input image but with each pixel value equaling zero.
-We again use Source Extractor to compile a list of all the objects in the input image, and  use this list to replace the pixel values at the coordinates of the located objects with one.
-\textsc{Galfit} uses the mask image to ignore any objects neighboring our galaxy while it is completing the fit.}
+\item[The mask image]{\textsc{Galfit} uses the mask image to ignore any objects neighboring our galaxy while it is completing the fit.The first step in making the mask is to create an image that has the same dimensions as our input image but with each pixel value equaling zero.
+We again use Source Extractor to compile a list of all the objects in the input image, and  use this list to replace the pixel values at the coordinates of the located objects with one.}
 
@@
 The constraints for x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle for the one component fits are listed in \autoref{constrtable}.
-}
+We change the constraint file for the two component fits later in the analysis.}
 
@@
 
-\noindent We use all of the above to obtain a one component, deconvolved fit for every galaxy in the RESOLVE survey.
+\noindent We use all of the above to obtain a one component, seeing-deconvolved fit for every galaxy in the RESOLVE survey.
 We then perform the two component fits as follows.
@@
 \subsection{Kinematics}
-\label{kin}
+\label{kindata}
 

### 2016-04-18 paperdraft.tex
more changes

@@
 For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.
+See \autoref{fig:galfit} for example one and two component fits for a RESOLVE galaxy.
+
+\begin{figure*}[b]
+\begin{center}
+\includegraphics{galfitexample.eps}
+\caption{}
+\label{fig:galfit}
+\end{center}
+\end{figure*}
 
@@
 Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
-We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored".
+We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spirals or irregulars that we would not consider a CCG.
 After this selection, we are left with 124 galaxies in the CCG candidate sample.
@@
 CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs.
-See \autoref{fig:pics} for examples of CCGs on this scale.
+See \autoref{fig:pics} for examples of CCGs on this continuous scale.
 There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead.
@@
 \noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
-We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in \citet{Eckert2015}.
+We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
 The main differences in this processing are (1) improved sky subtraction following Blanton et al.
@@
 
-\noindent A subset of the smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR.
-For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of 3"$\times$5" and the spectral range 4200-5600\AA.
+\noindent A subset of the faintest or smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR.
+For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of $3''\times5''$ and the spectral range 4200-5600\AA.
 The B1200 grating offers 0.9\AA\ resolution when binned spectrally by 2.
@@
 We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
-More information on the data reduction for the Gemini GMOS IFU can be found in  Appendix A.
+More information on the data reduction for the Gemini GMOS IFU can be found in \autoref{app}.
 
@@
 \appendix
+\label{app}
 

### 2016-04-25 paperdraft.tex
new pdf
revising text

@@
 \usepackage{epstopdf}
+\usepackage{gensymb}
 \usepackage{longtable}
@@
 \author{Dara J. Norman\altaffilmark{2}}
-\author{Mark N. Norris\altaffilmark{3}}
+\author{Mark A. Norris\altaffilmark{3}}
 \author{Callie Hood\altaffilmark{1}}
@@
 \author{Kathleen D. Eckert\altaffilmark{1}}
-\author{Amanda J. Moffett\altaffilmark{1,4}}
+\author{Ian Dell'Antonio\altaffilmark{4}}
+\author{Samantha Dallas\altaffilmark{4}}
+\author{Amanda J. Moffett\altaffilmark{1,5}}
 \author{David V. Stark\altaffilmark{1}}
@@
 \affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
-\affil{$^4$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
+\affil{$^4$Department of Physics, Brown Univsersity, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
+\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
 way, Crawley, WA 6009, Australia}
 \begin{abstract}
-We analyze the complete set of 96 compact core galaxies (CCGs) in the volume-limited RESOLVE survey to investigate the formation and evolution of compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments.
-We perform one and two component S\'ersic fits KIDSS for all galaxies in the RESOLVE sample with UKIDSS $Y$-band imaging using \textsc{Galfit}, which produces seeing-deconvolved effective radius (\Reff) measurements.
-The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
+We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments.
+To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (XX\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements.
+The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
 We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs, dEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
-We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the fluxes in each component.
+We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component.
 The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated.
@@
 We find that CCGs naturally occur in a range of environments from isolated to cluster.
-We compare velocity dispersions of CCGs derived from Gemini IFU data and SOAR spectroscopy to velocity dispersions of other RESOLVE galaxies and the cEs and and dEs of AIMSS.
-We search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
-Initial results show several CCGs following the dissipative formation track.
+We also derive velocity dispersions for 8 CCGs from Gemini IFU data and SOAR spectroscopy.
+Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
+Initial results show 7 CCGs clearly following the dissipative formation track.
 \end{abstract}
@@
 \noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es).
-Different types of CSSs include ultra compact dwarf galaxies (UCDs; \citet{Phillipps2001}), compact elliptical galaxies (cEs; \citet{Faber1973}), dwarf elliptical galaxies (dEs), and nucleated dwarf elliptical galaxies (dE,Ns).
-There are many unanswered questions about CSSs, typically involving how they form and evolve through time.
-One fact that makes the study of these compact galaxies so intriguing is their relative scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size.
+Different types of CSSs include ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001} and compact elliptical galaxies \citep[cEs;][]{Faber1973}.
+There are many unanswered questions about how CSSs form and evolve through time.
+One fact that makes the study of these compact galaxies so intriguing is their apparent scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size.
 Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.
 
-UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc (see Figure 11 in \citet{Norris2014}), are largely believed to be either the high mass extension of the globular cluster population (\citet{Drinkwater2000}, \citet{Mieske2002}) or tidally-stripped remnants of nucleated dwarf galaxies (\citet{Bekki2001}, \citet{Bekki2003}, \citet{Jennings2015}, \citet{Zhang2015}).
-\citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and S0 galaxy NGC4546.
-\citet{Seth2014} find a supermassive black hole at the center of a UCD near M60, a massive elliptical galaxy, lending more evidence toward tidal stripping being a common for UCDs.
+In contrast, dwarf elliptical galaxies (dEs) and their nucleated dwarf elliptical galaxies (dE,Ns) are ...
 
-Meanwhile, cEs have radii ranging typically from $\sim$100--600 pc (again see Figure 11 in \citet{Norris2014}).
-They are typically thought to be either the result of a tidal stripping event, as is the case for the prototypical cE, M32 (\citet{Choi2002}, \citet{Graham2002}), or as a part of the low mass extension to the E population.
-The evidence for tidal stripping includes finding tidal streams near cEs (\citet{SmithCastelli2008a}, \citet{Chilingarian2009}) and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
-On the other hand, \citet{Kormendy2012a} argue that cEs are the extension of normal E galaxies.
+UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc \citep[e.g.,][]{Norris2014}, are largely believed to be either the high mass extension of the globular cluster population \citep{Drinkwater2000, Mieske2002} or tidally-stripped remnants of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}.
+\citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and the S0 galaxy NGC4546.
+\citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
 
-dEs and their nucleated counterparts, dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc (again see Figure 11 in \citet{Norris2014}).
-Similarly to cEs, dEs and dE,Ns are thought to be either tidally stripped remnants (\citet{Crnojevi2014} find dEs in M31 that show signs of tidal stripping) or the low mass extension to elliptical galaxies \citep{Crawford2016}.
+Moving up in size, cEs have radii ranging typically from $\sim$100--600 pc \citep[e.g.,][]{Norris2014}.
+Similarly to UCDs, they are typically thought to be the result of a tidal stripping event, as is the case for the prototypical cE, M32 \citep{Choi2002, Graham2002}.
+The evidence for tidal stripping includes finding tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
+On the other hand, \citet{Kormendy2012a} argue that cEs could be the low mass extension to the normal E population created via dissipative formation in gas rich environments.
+\citet{Norris2014} argue that both scenarios are likely at play.
+%explain more
+
+In contrast to CSSs, dEs and dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc \citep[e.g.,][]{Norris2014}.
+Similar again to UCDs and cEs, dEs are often thought to be either tidally stripped remnants (\citet{Crnojevi2014} find dEs in M31 that show signs of tidal stripping) or the low mass extension to elliptical galaxies \citep{Crawford2016}.
 They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched.
@@
 
-Clues to how a CSS is formed may be given by their environments.
-UCDs, cEs, dEs have all been found in clusters (for UCDs: \citet{Price2009}, \citet{Madrid2010}, \citet{Hasegan2005}, \citet{Jones2006}, \citet{Mieske2009}, \citet{Wehner2007}, \citet{Misgeld2008}; for cEs: \citet{Chilingarian2007}, \citet{SmithCastelli2012}, \citet{Price2009}; and dEs: \citep{SmithCastelli2012}, \citet{Koo1994}, \citet{Guzman1996}, \citet{Crawford2016}).
+Clues to how CCGs form may be given by their morphology i.e., one- or two-component structure, environments, star formation histories, and kinematics.
+\citet{Pfeffer2013} predict that tidally stripped remnants will display multi-component surface brightness profiles due to lingering outer galaxy structures.
+Dissipative processes could also cause cores to form as gas rushes to the center and star formation begins.
+These effects could vary, however, based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
+
+CSSs have been found in a range of environments thus far.
+In the cluster environment we find UCDs \citep{Price2009,Madrid2010,Hasegan2005,Jones2006,Mieske2009,Wehner2007,Misgeld2008}, cEs \citep{Chilingarian2007,SmithCastelli2012,Price2009}, and dEs \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}.
 Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups.
 Lastly, only cEs have been found in isolated environments: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$ Mpc.
+CSSs found in group or cluster environments may be tidally stripped remnants, whereas isolated CCSs may rather be disippatively formed like normal Es.
 
-Given the similarities in formation scenarios and environments for these CSSs, we propose to study these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff.
-Critical to this study is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments.
-Previous studies have mainly focused on selecting targets in the group/cluster environments, since this route is often more convenient.
-Our goal is thus to create a complete and volume-limited sample of compact galaxies across all environments so that we may examine their formation and evolution.
+Another useful tool we have in discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$).
+\citet{Bender1992} and \citet{Bekki2003} show that $\sigma$ will remain largely unchanged when tidal stripping occurs, even though the \Reff\ and stellar mass will be greatly reduced.
+Thus, galaxies that are offset to higher $\sigma$ in a Faber-Jackson (stellar mass -- $\sigma$) relation \citep{faber1976} are most likely tidally stripped, while galaxies falling along the relation are most likely the low-mass extension of normal Es.
 
-This paper presents the preliminary results of this work, characterizing the colors, star formation histories, environments, and preliminary kinematics of the first complete, volume-limited sample of CCGs.
-The paper is organized as follows.
-We explain our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} in \autoref{deconv}.
-We then explain the selection of the CCG sample from the RESOLVE survey in \autoref{CCGs}.
-We then describe our photometric and spectroscopic data and analysis in \autoref{methods}.
-We gives our results in \autoref{results}.
-Lastly, our results are summarized in \autoref{conclusions}.
+Given the similarities in formation scenarios and environments for CSSs, we propose a study of these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff.
+Critical to this work is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments.
+Our goal is therefore to create a complete and volume-limited sample of compact galaxies with key data quantifying their demographics, environments, and kinematics.
+In this work we present the first complete, volume-limited sample of 96 compact galaxies that we term ``compact core galaxies'' or CCGs.
+We supplement this analysis with data on the colors and star formation histories of CCGs, which could point to recent star formation as a sign of stripping or disippative formation.
+
+This paper is organized as follows.
+We describe our parent sample, the RESOLVE survey, in \autoref{resolve} and our comparison sample, the AIMSS catalog, in \autoref{aimss}.
+Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}.
+We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}.
+We next describe our photometric and spectroscopic data and analysis in \autoref{methods}.
+We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}.
+In \autoref{discussion}, we present a discussion of our results in the context of CCG formation and evolution.
+Lastly, the summary and future work are given in \autoref{conclusions}.
 
@@
 
-\noindent We use the RESOLVE survey (Kannpann \& Wei 2008, Kannappan et al., in prep) as the parent sample for our census of CCGs.
+\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs.
 RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages.
-RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \citet{York2000}), and is designed to span two individual semesters: A for the spring sky and B for the fall, which overlaps much of Stripe-82.
-RESOLVE-A spans $\sim38,400$ Mpc$^3$ and occupies the region 131.25\textdegree $<$ RA $<$ 236.25\textdegree, 0\textdegree $<$ Dec $<$ 5\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$, while RESOLVE-B spans $\sim13,7000 $ Mpc$^3$ and occupies the region 330\textdegree $<$ RA $<$ 45\textdegree, -1.25\textdegree $<$ Dec $<$ 1.255\textdegree, and 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.
+RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \citet{York2000}), and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82.
+With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$.
+Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.
 
-RESOLVE's exceptional completeness is due to our use of multiple redshift surveys to recover galaxies that were missed in SDSS due to fiber collisions and several issues with their photometry pipeline.
-These issues include the oversubtraction of sky around galaxies that causes their flux to be underestimated and thereby not meet the magnitude cut for spectroscopic follow-up; the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, making no one piece meet the magnitude cut; and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut.
-We have used SDSS along with additional redshifts from archival sources (the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}) to counteract these issues and build up the survey's membership.
+RESOLVE's exceptional completeness is obtained by making use of multiple redshift surveys to recover galaxies that were missed in SDSS due to fiber collisions, the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, so no one piece meets the magnitude cut and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut.
+We supplement the SDSS main redshift survey with additional redshifts from archival sources (the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}) to achieve $\sim12\%$ higher completeness in RESOLVE-A and $\sim25\%$ higher completeness in RESOLVE-B.
 
@@
 In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
-We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.
 
 An important caveat to RESOLVE's completeness is that the survey is most likely to be missing the objects this study is focused on, cEs.
-This is because these objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}, which uses the flux and ellipticity of an object to determine the probability of it being a star or a galaxy.
-There are current ongoing efforts to use photo-z estimates to recover these objects.
+This is because these objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}.
+We are engaged in ongoing efforts to use photo-z estimates to recover some of these objects.
 
@@
 Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.
+
+\begin{figure*}[b]
+\begin{center}
+\includegraphics[scale=0.5]{galfitexample.eps}
+\caption{Shown here are the model outputs from \textsc{Galfit}.
+The left column shows the UKIDSS $Y$-band image cut out around the galaxy.
+The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model).
+The top row shows the one component fit for one of the RESOLVE galaxies, rf0055.
+As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope.
+The bottow row shows the two component fit for the same galaxy.
+We now are able to well fit both the inner bulge and the outer envelope.
+The residual is much cleaner, although there may be some spiral structure remaining that could require a third component to fit.}
+\label{fig:galfit}
+\end{center}
+\end{figure*}
 
@@
 
-\begin{figure*}[b]
-\begin{center}
-\includegraphics{galfitexample.eps}
-\caption{}
-\label{fig:galfit}
-\end{center}
-\end{figure*}
-
 \subsubsection{Selection of CCGs}
@@
 
-\begin{figure*}[t]
+\begin{figure*}[hbpt!]
 \begin{center}
@@
 
-\begin{figure*}[b]
+\begin{figure*}[hbpt!]
 \begin{center}
@@
 
-\begin{figure}[t]
+\begin{figure}[hbpt!]
 \begin{center}
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[hbpt!]
 \begin{center}
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[b]
 \begin{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{CCG formation and evolution} %kind of like a discussion section
+\section{CCG formation and evolution} %kind of like a discussion section
+\label{discussion}
+
+We now take an in depth look at the 8 CCGs with kinematics.
 
@@
 
-\section{Future Work}
-\subsection{Gas Content}
-\noindent The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
+\noindent Future work will include investigating the gas content and metallicities of CCGs.
+The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
 For example, a CCG in a galaxy cluster with little HI gas may point towards ram pressure stripping being important.
 Combined with CCG colors and FSMGR, the gas content may be an important tool in determining the evolution of a CCG.
-
-\subsection{Metallicities}
-\noindent \citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
+\citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
 With the SOAR data we have in hand, we may be able to test this hypothesis for the CCG sample and use this method as another way to discern formation scenarios.

### 2016-04-28 paperdraft.tex
adding new figure
lots of new text in intro

@@
 
-\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range ($\sim10 - 800$ pc), lying between globular clusters (GCs) and normal elliptical galaxies (Es).
-Different types of CSSs include ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001} and compact elliptical galaxies \citep[cEs;][]{Faber1973}.
+\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range between globular clusters (GCs) and normal elliptical galaxies (Es).
+Different types of CSSs include compact elliptical galaxies \citep[cEs;][]{Faber1973} and ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001}.
 There are many unanswered questions about how CSSs form and evolve through time.
@@
 
-In contrast, dwarf elliptical galaxies (dEs) and their nucleated dwarf elliptical galaxies (dE,Ns) are ...
+CSSs have radii ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form.
+The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}.
+The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}.
+\citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
+Similarly, cEs are also thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}.
+More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
+On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}.
+One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with a wealth of newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.
 
-UCDs, the smallest of the CSSs mentioned above with radii ranging from 10--100 pc \citep[e.g.,][]{Norris2014}, are largely believed to be either the high mass extension of the globular cluster population \citep{Drinkwater2000, Mieske2002} or tidally-stripped remnants of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}.
-\citet{Norris2011} find evidence that UCDs are a ``mixed bag'' of both giant GCs and stripped nuclei based on their analysis of UCDs discovered near the elliptical galaxy NGC3923 and the S0 galaxy NGC4546.
-\citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
+In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated dwarf elliptical galaxies (dE,Ns) are quite common, especially in clusters.
+\citet{Binggeli1991} find that of 225 dwarf galaxies present in the Virgo cluster, 174 are classfied as dEs or dE,Ns based on their sufrace brightness profiles.
+dEs and dE,Ns are also larger than CSSs with radii ranging from $\sim$600-800~pc \citep[e.g.,][]{Norris2014}, which may perhaps help their numbers.
+Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Crawford2016}.
+They could also be the remnants of luminous compact blue dwarfs (LCBDs) that have been ram-pressure stripped and often quenched as they enter the cluster environment.
+There is also some evidence that dE,Ns are the progenitors of UCDs \citep{Pfeffer2013,Zhang2015,Liu2015}.
 
-Moving up in size, cEs have radii ranging typically from $\sim$100--600 pc \citep[e.g.,][]{Norris2014}.
-Similarly to UCDs, they are typically thought to be the result of a tidal stripping event, as is the case for the prototypical cE, M32 \citep{Choi2002, Graham2002}.
-The evidence for tidal stripping includes finding tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
-On the other hand, \citet{Kormendy2012a} argue that cEs could be the low mass extension to the normal E population created via dissipative formation in gas rich environments.
-\citet{Norris2014} argue that both scenarios are likely at play.
-%explain more
+Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with radii up to 800~pc.
+The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios.
+Clues to how CCGs form may be given by their morphology i.e., one- or two-component structure, environments, star formation histories, and kinematics.
+We highlight these differences below.
 
-In contrast to CSSs, dEs and dE,Ns, are the largest of the CSSs mentioned with radii ranging from $\sim$600-800 pc \citep[e.g.,][]{Norris2014}.
-Similar again to UCDs and cEs, dEs are often thought to be either tidally stripped remnants (\citet{Crnojevi2014} find dEs in M31 that show signs of tidal stripping) or the low mass extension to elliptical galaxies \citep{Crawford2016}.
-They could also be the remnants of LCBDs that have been ram-pressure stripped as they entered the cluster environment and subsequently quenched.
-There is some evidence that dE,Ns are the progenitors of UCDs (\citet{Pfeffer2013}, \citet{Zhang2015}, \citet{Liu2015}).
+%structure
+The morphologies of \citet{Pfeffer2013} predict that tidally stripped remnants will display multi-component surface brightness profiles due to lingering outer galaxy structures.
+*** M32 has a bulge plus disk profile (Graham 2002)*** Dissipative processes could also cause cores to form as gas rushes to the center and star formation begins.
+*** Huxor cE has no underlying disk *** These effects could vary, however, based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
 
-Clues to how CCGs form may be given by their morphology i.e., one- or two-component structure, environments, star formation histories, and kinematics.
-\citet{Pfeffer2013} predict that tidally stripped remnants will display multi-component surface brightness profiles due to lingering outer galaxy structures.
-Dissipative processes could also cause cores to form as gas rushes to the center and star formation begins.
-These effects could vary, however, based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
-
+%environments
 CSSs have been found in a range of environments thus far.
@@
 
+*** include kicked out scenarios here ***
+
+%colors
+
+%kinematics
 Another useful tool we have in discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$).
@@
 
-Given the similarities in formation scenarios and environments for CSSs, we propose a study of these galaxies as a part of a continuum of compact galaxies instead of being broken up into (perhaps somewhat arbitrary) classes based on \Reff.
-Critical to this work is a ubiquitous sample of CSSs that will allow us to analyze their formation as a function of all environments.
-Our goal is therefore to create a complete and volume-limited sample of compact galaxies with key data quantifying their demographics, environments, and kinematics.
-In this work we present the first complete, volume-limited sample of 96 compact galaxies that we term ``compact core galaxies'' or CCGs.
-We supplement this analysis with data on the colors and star formation histories of CCGs, which could point to recent star formation as a sign of stripping or disippative formation.
-
+In this paper, we present a volume-limited sample of CCGs with key data quantifying their morphologies, environments, star formation histories, and kinematics.
 This paper is organized as follows.
@@
 We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}.
-We next describe our photometric and spectroscopic data and analysis in \autoref{methods}.
+We next describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}.
 We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}.

### 2016-04-29 paperdraft.tex
new intro sections

@@
 \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
-Similarly, cEs are also thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}.
+Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}.
 More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
 On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}.
-One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with a wealth of newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.
+One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.
 
-In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated dwarf elliptical galaxies (dE,Ns) are quite common, especially in clusters.
-\citet{Binggeli1991} find that of 225 dwarf galaxies present in the Virgo cluster, 174 are classfied as dEs or dE,Ns based on their sufrace brightness profiles.
-dEs and dE,Ns are also larger than CSSs with radii ranging from $\sim$600-800~pc \citep[e.g.,][]{Norris2014}, which may perhaps help their numbers.
-Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Crawford2016}.
-They could also be the remnants of luminous compact blue dwarfs (LCBDs) that have been ram-pressure stripped and often quenched as they enter the cluster environment.
-There is also some evidence that dE,Ns are the progenitors of UCDs \citep{Pfeffer2013,Zhang2015,Liu2015}.
+In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated counterparts (dE,Ns) are quite common, especially in clusters where they were first discovered.
+In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles.
+dEs are typically larger than CSSs with radii ranging up to $\sim800$~pc, whereas dE,Ns may have larger envelopes with a core radius <$800$~pc \citep[e.g.,][]{Norris2014}.
+Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
+They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and often quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016}.
+There is also some evidence that dE,Ns are the progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
 
@@
 The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios.
-Clues to how CCGs form may be given by their morphology i.e., one- or two-component structure, environments, star formation histories, and kinematics.
-We highlight these differences below.
+Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics.
+We highlight these data below.
+
+%environments
+\textit{Environments.} CSSs have been found in a large range of environments thus far.
+UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}.
+M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}.
+As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}, but have also been found near groups \citep{Crnojevi2014,Penny2014}.
+Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$~Mpc.
+
+Environment bears on formation scenarios in different ways.
+One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CCSs may rather be dissipatively formed like Es.
+However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process.
+The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.
 
 %structure
-The morphologies of \citet{Pfeffer2013} predict that tidally stripped remnants will display multi-component surface brightness profiles due to lingering outer galaxy structures.
-*** M32 has a bulge plus disk profile (Graham 2002)*** Dissipative processes could also cause cores to form as gas rushes to the center and star formation begins.
-*** Huxor cE has no underlying disk *** These effects could vary, however, based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
+\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology.
+\citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin.
+\citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures.
+Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center and star formation begins.
+This core is then ``puffed up'' through time as it interacts with other galaxies.
+The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation.
+It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
 
-%environments
-CSSs have been found in a range of environments thus far.
-In the cluster environment we find UCDs \citep{Price2009,Madrid2010,Hasegan2005,Jones2006,Mieske2009,Wehner2007,Misgeld2008}, cEs \citep{Chilingarian2007,SmithCastelli2012,Price2009}, and dEs \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}.
-Fewer CSSs have been found in groups: \citet{Evstigneeva2007} find one definite UCD and two candidates in the Dorado group as well as two candidates in the NGC1400 group and \citet{Hau2009} find a UCD near the Sombrero galaxy; \citet{Huxor2011} and \citet{Chilingarian2010} find cEs in groups; and \citet{Crnojevi2014}  \citet{Penny2014} find dEs in groups.
-Lastly, only cEs have been found in isolated environments: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$ Mpc.
-CSSs found in group or cluster environments may be tidally stripped remnants, whereas isolated CCSs may rather be disippatively formed like normal Es.
-
-*** include kicked out scenarios here ***
+Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found.
+\citet{Mastropietro2005a} use the N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not completely destroyed by ram pressure or tidal stripping.
+The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.
 
 %colors
+\textit{Star formation histories.} 
+Colors and star formation rates are useful since they may point to recent star formation as a part of tidal stripping or dissipative formation.
+\citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations.
+\citet{Norris2011} find a similar result with one UCD best fit using older stellar populations.
+\citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.
 
 %kinematics
-Another useful tool we have in discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$).
+\textit{Kinematics.}  The last useful tool we have for discerning between formation scenarios is the galaxy's stellar velocity dispersion ($\sigma$).
 \citet{Bender1992} and \citet{Bekki2003} show that $\sigma$ will remain largely unchanged when tidal stripping occurs, even though the \Reff\ and stellar mass will be greatly reduced.
@@
 
-In this paper, we present a volume-limited sample of CCGs with key data quantifying their morphologies, environments, star formation histories, and kinematics.
+In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey that have key data quantifying their morphologies, environments, star formation histories, and kinematics.
+We use this sample to examine the formation scenarios and evolution of CSSs and dEs/dE,Ns simultaneously as a spectrum of compact galaxies that span the gap from GCs to Es.
+Because we have derived a complete sample from RESOLVE, our sample contains CCGs at every evolutionary stage.
 This paper is organized as follows.
@@
 RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages.
-RESOLVE falls within the footprint of the Sloan Digital Sky Survey (SDSS, \citet{York2000}), and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82.
+RESOLVE falls within the footprint of the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}, and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82.
 With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$.
@@
 With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively.
-We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2016}).
-In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs.
+We can convert these absolute magnitude limits into stellar mass limits: M$_{\star}~\sim~10^{8.9}$~\Msun for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun in the B semester (see Figure 7 in \citet{Eckert2016}).
+In Figure 1, we plot the stellar masses against the deconvolved, one-component, half-light radius \Reff\ (see \autoref{deconv}) for all of RESOLVE along with the core-only \Reff\ for the CCG sample and see that these limits allow us to reach down to CSSs with sizes and masses similar to cEs.
 
-An important caveat to RESOLVE's completeness is that the survey is most likely to be missing the objects this study is focused on, cEs.
-This is because these objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}.
+An important caveat to RESOLVE's completeness is that the survey is preferentially incomplete for the very objects this study is focused on, cEs.
+Such round objects can often be mistaken for stars in redshift surveys using tools such as the \texttt{class\_star} parameter in Source Extractor \citep{Bertin1996}.
 We are engaged in ongoing efforts to use photo-z estimates to recover some of these objects.
@@
 
-\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog (\citet{Norris2014}, \citet{Forbes2014}, \citet{Janz2015}) as a reference sample for our CCGs.
-AIMSS is a catalog of spectroscopically confirmed CSSs found in groups and clusters and includes both literature and newly discovered objects.
+\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.
+AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both literature and newly discovered objects.
 Their process to find new CSSs is as follows.
@@
 We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
-The main differences in this processing are (1) improved sky subtraction following Blanton et al.
-(2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
-Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).
+The main differences in this processing are (1) improved sky subtraction following \citet{Blanton2011} for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
+Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method \citep[e.g., Figure 2 in][]{Eckert2015}.
 
@@
 
-The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al.
-in prep.).
+The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al., submitted).
 We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.
@@
 We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
-More information on the data reduction for the Gemini GMOS IFU can be found in \autoref{app}.
+More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix.
 
@@
 This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies.
-There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.
+There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.
 
@@
 \begin{center}
-\includegraphics{nn_groupmass.eps}
+\includegraphics{nn_groupmass_2d.eps}
 \caption{We plot here the group halo mass against the nearest 3D neighbor for the RESOLVE survey and CCG sample.
@@
 Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since  they will have more  Conversely, $\sigma$s that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
-
-We find that most of the CCGs tend to follow the dissipative formation track.
-However, there is one CCG with a core+envelope that lies close to M32, a tidally stripped cE, in the relation.
-We now take a closer look at this CCG, rf0492.
-This CCG lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}.
-Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$.
-This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.
+Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.
 
@@
 
-We now take an in depth look at the 8 CCGs with kinematics.
+We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
+
+\subsection{rs0345}
+
+\subsection{rs0567, rs1186, rf0078}
+
+\subsection{rs1100}
+
+\subsection{rf0003}
+
+\subsection{rf0328}
+
+\subsection{rf0492}
+This galaxy has a core+envelope morphology and lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}.
+Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$.
+This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.
+
+\begin{figure*}[b]
+\begin{center}
+\includegraphics[scale=0.7]{miniplots.eps}
+\caption{Here we plot the stellar mass vs.
+velocity dispersion ($\sigma$) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
+Most CCGs appear to be following the dissipative formation track.}
+\label{fig:miniplots}
+\end{center}
+\end{figure*}
 

### 2016-05-10 paperdraft.tex
revisions

@@
 \author{Dara J. Norman\altaffilmark{2}}
+\author{Ashley S. Bittner\altaffilmark{1}}
 \author{Mark A. Norris\altaffilmark{3}}
-\author{Callie Hood\altaffilmark{1}}
-\author{Ashley S. Bittner\altaffilmark{1}}
 \author{Kathleen D. Eckert\altaffilmark{1}}
 \author{Ian Dell'Antonio\altaffilmark{4}}
+\author{Callie Hood\altaffilmark{1}}
 \author{Samantha Dallas\altaffilmark{4}}
+\author{David V. Stark\altaffilmark{1}}
 \author{Amanda J. Moffett\altaffilmark{1,5}}
-\author{David V. Stark\altaffilmark{1}}
 \author{the RESOLVE Team}
@@
 \affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
-\affil{$^4$Department of Physics, Brown Univsersity, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
-\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University ofWestern Australia, 35 Stirling High-
+\affil{$^4$Department of Physics, Brown University, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
+\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University of Western Australia, 35 Stirling High-
 way, Crawley, WA 6009, Australia}
@@
 We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments.
-To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (XX\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements.
+To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements.
 The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
@@
 We find that CCGs naturally occur in a range of environments from isolated to cluster.
-We also derive velocity dispersions for 8 CCGs from Gemini IFU data and SOAR spectroscopy.
+We also derive velocity dispersions ($\sigma$) for 8 CCGs from Gemini IFU data and SOAR spectroscopy.
 Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
-Initial results show 7 CCGs clearly following the dissipative formation track.
+Initial results show 6 CCGs likely following the dissipative formation track and 2 CCGs that are slightly offset to higher $\sigma$.
+
 \end{abstract}
@@
 One fact that makes the study of these compact galaxies so intriguing is their apparent scarcity, which raises the question as to whether they are an intermediate and short-lived evolutionary phase in the life of a galaxy, or simply hard to find due to their size.
-Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios and evolution over cosmic time.
+Only in the last 15 years have we discovered enough ($\sim 40$) of these objects to enable studies of their formation scenarios.
 
-CSSs have radii ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form.
+CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form.
 The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}.
@@
 More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
-On the other hand, \citet{Wirth1984,Kormendy2009,Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}.
-One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that both the high-mass GCs and tidal stripping scenarios are likely for UCD formation and both tidal stripping and low-mass E scenarios are likely for cE formation.
+On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}.
+One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.
 
@@
 Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
-They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and often quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016}.
-There is also some evidence that dE,Ns are the progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
+They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}.
+There is also some evidence that dE,Ns are progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
 
-Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with radii up to 800~pc.
-The goal of this paper is to study these galaxies as a part of a continuum of compact galaxies in order to discern between formation scenarios.
+Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core radii up to 800~pc.
+The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios.
 Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics.
@@
 M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}.
-As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016}, but have also been found near groups \citep{Crnojevi2014,Penny2014}.
-Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015} find cEs separated from other galaxies by $>1$~Mpc.
+As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevi2014,Penny2014}.
+Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} find cEs separated from other galaxies by $>1$~Mpc.
 
 Environment bears on formation scenarios in different ways.
-One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CCSs may rather be dissipatively formed like Es.
+One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CSSs may rather be dissipatively formed like Es.
 However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process.
@@
 Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found.
-\citet{Mastropietro2005a} use the N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not completely destroyed by ram pressure or tidal stripping.
+\citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping.
 The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.
@@
 Colors and star formation rates are useful since they may point to recent star formation as a part of tidal stripping or dissipative formation.
+The typical thought is that CSSs are ``red and dead'', and some studies even cut on color when selecting CSS samples \citep{Chilingarian2015}.
 \citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations.
@@
 
-In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey that have key data quantifying their morphologies, environments, star formation histories, and kinematics.
+In this paper, we present a complete sample of CCGs derived from the volume-limited RESOLVE survey, along with key data quantifying their morphologies, environments, star formation histories, and kinematics.
 We use this sample to examine the formation scenarios and evolution of CSSs and dEs/dE,Ns simultaneously as a spectrum of compact galaxies that span the gap from GCs to Es.
@@
 Our methods for performing seeing-deconvolved one and two component fits for the entire RESOLVE sample using \textsc{Galfit} are presented in \autoref{deconv}.
-We then detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}.
-We next describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}.
+We detail the selection of the CCG sample from the RESOLVE survey and quantify our CCG demographics in \autoref{CCGs}.
+We describe our photometric, environmental, and spectroscopic data and analysis in \autoref{methods}.
 We present a statistical distribution of environments, star formation histories, and velocity dispersions for the complete sample in \autoref{results}.
@@
 RESOLVE falls within the footprint of the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}, and covers equatorial strips in both semesters: A for the northern spring sky and B for the northern fall sky, which overlaps much of Stripe-82.
-With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.255\degree$.
+With $\text{H}_{\circ} = 70~\text{km~s}^{-1}$, RESOLVE-A spans $\sim38,400~\text{Mpc}^3$ and occupies the region $131.25\degree~<~\text{RA}~<~236.25\degree$ and $0\degree~<~\text{Dec}~<~5\degree$, while RESOLVE-B spans $\sim13,700~\text{Mpc}^3$ and occupies the region $330\degree~<~\text{RA}~<~45\degree$ and $-1.25\degree~<~\text{Dec}~<~1.25\degree$.
 Both semesters cover the redshift range 4500 km s$^{-1} <$ cz $< 7000$ km s$^{-1}$.
 
-RESOLVE's exceptional completeness is obtained by making use of multiple redshift surveys to recover galaxies that were missed in SDSS due to fiber collisions, the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces, so no one piece meets the magnitude cut and the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut.
-We supplement the SDSS main redshift survey with additional redshifts from archival sources (the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}) to achieve $\sim12\%$ higher completeness in RESOLVE-A and $\sim25\%$ higher completeness in RESOLVE-B.
+RESOLVE's exceptional completeness is obtained by making use of multiple redshift surveys to recover galaxies that were missed in SDSS due to (i) fiber collisions, (ii) the ``shredding'' of galaxies in which the pipeline breaks up a single galaxy into individual pieces so no one piece meets the magnitude cut, and (iii) the intentional exclusion of low surface brightness galaxies ($\mu_{50} < 24.5$ mag arcsec$^{-2}$), even if they meet the magnitude cut.
+We supplement the SDSS main redshift survey with additional redshifts from archival sources, including the Updated Zwicky Catalog \citep{Falco1999}, HyperLeda \citep{Paturel2003}, 6dF \citep{Jones2009}, 2dF \citep{Colless2001}, GAMA \citep{Driver2011}, and ALFALFA \citep{Haynes2011}, to achieve $\sim12\%$ higher completeness in RESOLVE-A and $\sim25\%$ higher completeness in RESOLVE-B \citep{Eckert2015}.
 
 With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively.
-We can convert these absolute magnitude limits into stellar mass limits: M$_{\star}~\sim~10^{8.9}$~\Msun for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun in the B semester (see Figure 7 in \citet{Eckert2016}).
-In Figure 1, we plot the stellar masses against the deconvolved, one-component, half-light radius \Reff\ (see \autoref{deconv}) for all of RESOLVE along with the core-only \Reff\ for the CCG sample and see that these limits allow us to reach down to CSSs with sizes and masses similar to cEs.
+To derive the stellar mass completeness limits of RESOLVE, \citet{Eckert2016} use the known stellar masses and magnitudes of all RESOLVE galaxies to determine the stellar mass limit above which no more than 2\% of objects have an $r$-band magnitude fainter than the stated magnitude completeness limit.
+These values are M$_{\star}~\sim~10^{8.9}$~\Msun~for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun~in the B semester \citep[Figure 8 in ][]{Eckert2016}.
+These stellar mass completeness limits allow us to reach down to CSSs with sizes and masses similar to cEs (see \autoref{morph} for more details).
 
@@
 \noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.
-AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both literature and newly discovered objects.
-Their process to find new CSSs is as follows.
-First, a search is conducted in the Hyperleda redshift catalog \citep{Paturel2003} for all galaxies at distances between $\sim 7$ and 200 Mpc (to ensure CSSs with \Reff\ $> 50$ pc will be resolved in any available HST imaging) and with M$_{\rm B} < -15$.
-Once complete, the team then searches the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150kpc in projection of the selected galaxies.
-Next, Source Extractor is run on the HST images, and candidates are identified using a training set of previously known CSSs from the literature.
-Once cross-matched to ensure none are previously known and vetted by eye, spectra are obtained, redshift confirmation is performed, and velocity dispersions are extracted.
-AIMSS also includes literature data for other UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es.
-AIMSS compiles M$_{\rm V}$, stellar mass, effective radius, and velocity dispersions for each of its objects.
-Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can calibrate and compare our CCGs.
+AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects.
+The AIMSS CSS discovery process was as follows.
+First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging).
+The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies.
+Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature.
+After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions.
+AIMSS also includes literature data for previously known UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es.
+The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects.
+Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs.
 
@@
 \includegraphics[scale=0.5]{galfitexample.eps}
-\caption{Shown here are the model outputs from \textsc{Galfit}.
-The left column shows the UKIDSS $Y$-band image cut out around the galaxy.
+\caption{Model inputs and outputs from \textsc{Galfit}.
+The left column shows the UKIDSS $Y$-band image cutout around the galaxy.
 The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model).
@@
 As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope.
-The bottow row shows the two component fit for the same galaxy.
-We now are able to well fit both the inner bulge and the outer envelope.
-The residual is much cleaner, although there may be some spiral structure remaining that could require a third component to fit.}
+The bottom row shows the two component fit for the same galaxy.
+We are now  able to fit both the inner bulge and the outer envelope.
+The residual is much cleaner, although there may be some spiral structure remaining.}
 \label{fig:galfit}
@@
 \noindent We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample.
-For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits on each galaxy.
-Deconvolution is especially important since the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for the study of these objects.
+For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits to each galaxy.
+Deconvolution is especially important since the smallest galaxies in RESOLVE are most affected by seeing, and accurate radius measurements are crucial for the study of these objects.
 
 \textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file.
-We obtain/construct these items as follows:
+We obtain or construct these items as follows:
 
@@
 
-\item[The initial input file]{The initial input file gives \textsc{Galfit} the files paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters.
-For the one component fits, we set up our input file to have a section for measuring the level of the sky background, and another section for fitting a S\'ersic profile to galaxy.
+\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters.
+For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile to the galaxy.
 The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
-These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's photometric data (see \autoref{phot} for more details)}
+These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}
 
@@
 We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}.
-While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful for constructing a PSF.
-There are only 24 galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis.
+While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful when constructing the PSF image.
+There are only 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.
 
@@
 \item With this information, we select stars to use for building our PSF.
-The limiting parameters are (1) that the flux must be between $5,000-100,000$ counts to ensure no extremely faint or saturated stars are included, (2) that the ellipticity be lt 0.2 to ensure we are selecting round objects, (3) that the effective radius of the star be greater than 1 pixel to avoid selecting hot pixels, and (4) that \texttt{class\_star} is greater than 0.6 to ensure the objects we're picking are most likely stars.
+The limiting parameters are (1) that the flux must be between $5,000-100,000$ counts to ensure no extremely faint or saturated stars are included, (2) that the ellipticity be less than 0.2 to ensure we are selecting round objects, (3) that the effective radius of the star be greater than 1 pixel to avoid selecting hot pixels, and (4) that \texttt{class\_star} is greater than 0.6 to ensure the objects we're picking are most likely stars.
 We also make sure the stars are not near the image edges, since there can sometimes be image artifacts there.
@@
 \begin{tabular}{cc} \hline
-parameter & constaint  \\ \hline
+parameter & constraint  \\ \hline
 x \& y position & $\pm5$ pixels from input value \\
@@
 S\'ersic n & 0.1 -- 8 \\ 
-axial ratio & 0 -- 1 \\
-position angle & -360 -- 360 \\ \hline
+axial ratio (b/a) & 0 -- 1 \\
+position angle (PA)) & -360 -- 360 \\ \hline
 \end{tabular}
@@
 Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
-We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spirals or irregulars that we would not consider a CCG.
+We note that this limit is arbitrary, and will be relaxed in the future (see \autoref{conclusions}).
+We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spiral or irregular galaxies.
 After this selection, we are left with 124 galaxies in the CCG candidate sample.
 
-Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic fit is constrained to always be larger than that of the first S\'ersic fit, and (3) the S\'ersic n of the second component is held constant at 1 for an exponentially decreasing disk profile.
-We let the values of \Reff, the integrated magnitude, b/a ratio, and PA change for both fits.
-By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic fit) and disky envelope (the second S\'ersic fit) for each CCG candidate.
+Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic component fit is constrained to always be larger than that of the first S\'ersic component fit, and (3) the S\'ersic n of the second component is held constant at 1 representing an exponentially decreasing disk profile.
+We let the values of \Reff, integrated magnitude, b/a ratio, and PA change for both fits.
+By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic component fit) and disky envelope (the second S\'ersic component fit) for each CCG candidate.
 
@@
 
-We quantify the amount of light in the core vs.
-the envelope by taking a ratio of the fluxes of the core and the envelope.
+We quantify the amount of light in the core vs.~the envelope by taking a ratio of the fluxes of the core and the envelope.
 The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
@@
 There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead.
-Where this happens (5 out of 96 cases), we classify this fit as either all core/envelope depending on which component was bad (log(flux ratio) = -1 or 1).
+Where this happens (5 out of 96 cases), we classify this fit as either all core/all envelope depending on which component was bad (log(flux ratio) = -1 or 1).
 We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component.
 When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).
-
-We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
-There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
 
@@
 \includegraphics{Reff_Mstars.eps}
-\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CCSs of the AIMSS catalog.
+\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs of the AIMSS catalog.
 In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff.
@@
 \noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
-We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
-The main differences in this processing are (1) improved sky subtraction following \citet{Blanton2011} for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
-Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method \citep[e.g., Figure 2 in][]{Eckert2015}.
+These photometry data has been reprocessed to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
+The main improvements in this processing are (1) improved sky subtraction following \citet{Blanton2011} for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) definition of elliptical apertures using the sum of the high S/N $gri$ images to determine the PA and b/a ratio yielding improved sensitivity to the outer disk (if present), and (3) application of the same apertures to all bands, which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
+Then, total magnitudes are derived for each band using three methods to enable robust estimation of errors: an exponential outer disk fit, a curve of growth, and a color correction  \citep[Figure 2 in][]{Eckert2015}.
 
-Colors, stellar masses and fractional stellar mass growth rates (FSMGR) are then derived from these $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in \citet{Kannappan2007}, \citet{Kannappan2009}, and \citet{Kannappan2013}.
-FSMGR is similar to a star formation rate, but it instead gives the ratio of stellar mass created in the last Gyr to the stellar mass previously existing.
-Therefore, an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr.
+Stellar masses, a long-term fractional stellar mass growth rate (FSMGR), and model colors are then derived from these reprocessed $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in  \citet{Kannappan2013}.
+We adopt the model grid from \citet{Kannappan2013} that combines old simple stellar populations with 2-12 Gyr age ranges and young stellar populations with either continuous star formation from 1015 Myr ago to 0-195 Myr ago, or with a simple stellar population with age either 360, 509, 641, 806, or 1015 Myr.
+A stellar mass is calculated for each model, along with a likelihood.
+\citet{Kannappan2013} design their model to also estimate FSMGR, which is the ratio of stellar mass created in the last Gyr to the stellar mass previously existing (i.e., an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr).
+Likelihood weighted model colors are also output with k-corrections to $z=0$.
 
-The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al., submitted).
-We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses.
+Baryonic masses are estimated
 
-\subsection{Environmental Metrics}
+%The HI masses for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and from new pointed observations with the GBT and Arecibo telescopes (Stark et al., submitted).
+We use these masses along with the stellar masses computed in the SED models to estimate baryonic masses, defined as $\text{M}_{bary} = \text{M}_{\star} + 1.4\text{M}_{HI}$.
+
+\subsection{Environment metrics}
 \label{env}
-\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
+\noindent The volume-limited design of RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
 We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy.
-The group halo mass allows us to look for CCGs that are M32--Andromeda analogs where tidal stripping may be at play, or conversely look for CCGs in large groups where ram-pressure stripping could occur.
+The group halo mass allows us to look for CCG-host pairs that are M32--Andromeda analogues where tidal stripping is likely or conversely to look for CCGs in large groups where either ram-pressure or tidal stripping could be important.
 The distance to neighboring galaxies lets us examine if interaction may occur or look for analogs of the isolated galaxies found by \citet{Huxor2013} and \citet{Paudel2014}.
 
-Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006}, and the masses of these group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}.
-More information on group identification can be found in \citet{Moffett2015}.
-The nearest neighbor distances are computed using the RA, Dec, and redshifts of each galaxy and along with spherical geometry principles.
+Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006} with linking lengths modified as described in \citet{Eckert2016}, and the masses of the group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}.
+More information on group identification can be found in \citet{Eckert2016}.
+The nearest 2-dimensional neighbor distances are computed using the RA and Dec coordinates for each galaxy along with a requirement that the neighbor be within $\pm~500$~km~$^{-1}$ of the primary.
+Three-dimensional distances are also available based on Hubble's Law distances, however the added errors that come with peculiar velocities make these values less reliable.
 
@@
 \noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile.
-We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup.
-With this absorption-line setup, we are able to derive velocity dispersions.
+We employ the Goodman Spectrograph \citep{Clemens2004} along with RESOLVE's custom-built image slicer with three parallel $1''$ slits to observe galaxies in either an emission- or absorption-line kinematic setup depending on whether the stellar continuum or gas emission lines are more prominent.
+With the absorption-line setup we are able to derive velocity dispersions, which are typically the best kinematic metric for CCGs.
 We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335.
@@
 The spectral reduction proceeds as follows.
-Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed.
+Using the standard IRAF Gemini-GMOS data packages, we perform bias and overscan subtraction, spatial trimming, flat fielding and fiber identification.
 We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure.
@@
 
-\noindent We then derive $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
+\noindent We measure $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
 This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$.
-A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skews the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy.
+In \autoref{fig:ppxffit}, we show an example of a pPXF fit for one of the CCGs observed with the Gemini-South IFU.
+In black is the observed spectrum that has been summed out to \Reff\ and in red is the pPXF best fit model spectrum.
+A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skew the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy.
 Future work will include implementing a stellar rotation subtraction routine for these fits, but preliminary testing by binning the spectra to $1''$ instead of to \Reff\ shows little change between the derived $\sigma$ values.
@@
 \includegraphics[scale=0.4]{rf0078ppxffit.eps}
-\caption{Plotted here in black is a summed Gemini-South IFU spectrum for the CCG rf0078.
-Overplotted in red is the pPXF best fit model spectrum.
-The spectrum is zoomed-in to show the MgB triplet fit at $\sim 5275$ \AA.}
+\caption{Summed Gemini-South IFU spectrum for the CCG rf0078. Overplotted in red is the pPXF best fit model spectrum. The spectrum is zoomed-in to show the MgB triplet fit at $\sim 5275$ \AA.}
 \label{fig:ppxffit}
@@
 \label{results}
+
+\subsection{Morphologies}
+\label{morph}
+
+We plot in \autoref{fig:radius} the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs and dEs of the AIMSS catalog.
+In grey are all RESOLVE galaxies, plotted using their one component fit \Reff.
+The CCG sample is plotted again with the core \Reff\ of the two component fits, causing them to shift down from the full RESOLVE sample.
+The symbol color for the CCGs represents the logarithm of the light ratio between the core and envelope, meaning that galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $\sim \pm 1$ will have more light in the core (+1) or envelope (-1).
+We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
+There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
+
 \subsection{Colors and Star formation rates}
@@
 \noindent We begin by examining the colors of the CCG sample.
-The left side of \autoref{fig:envplot} shows the $u-r$ colors of our CCG sample plotted against M$_{\star}$, compared to the RESOLVE sample as a whole.
-An unusual finding is that many CCGs live on the blue sequence, since most CSSs are typically thought of as being ``red and dead''.
-The right side of \autoref{fig:envplot} shows FSMGR vs.
+The left side of \autoref{fig:fsmgr} shows the k-corrected and extinction-corrected $u-r$ colors (as described in \autoref{phot}) of our CCG sample plotted against M$_{\star}$, compared to the RESOLVE sample as a whole.
+An unusual finding is that many CCGs live on the blue sequence, since most CSSs are typically thought of as being ``red and dead'', except for dE,Ns with blue cores.
+The right side of \autoref{fig:fsmgr} shows FSMGR vs.
 M$_{\rm bary}$ for the same objects.
-As with the colors, we find that many CCGs are forming stars at a rapid rate (FSMGR $\sim1$ means that the galaxy has doubled its mass in the last Gyr), again an unexpected finding which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if a tidally-stripped remnant).
+As with the colors, we find that many CCGs are forming stars at a rapid rate (FSMGR $\sim1$ means that the galaxy has doubled its mass in the last Gyr), again an unexpected finding which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if tidally-stripped remnants).
 
@@
 \noindent We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
-We see many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could be at play.
-On the opposite end, we see several CCGs in massive group halos, and that these tend to be either core- or envelope dominated CCGs.
+There are many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could have occurred for those CCGs.
+On the opposite end, we see several CCGs in massive group halos, and these CCGs tend to be either core- or envelope dominated.
 This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies.
-There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013}, \citet{Paudel2014}, and \citet{Chilingarian2015}, which may point to a dissipative formation scenario since there is no nearby object to have performed the stripping.
+There are also nine CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, and four of those are core dominated, resembling the isolated cE found by \citet{Huxor2013}.
+These free floating CCGs may be the result of dissipative formation since there is no nearby object to have performed the stripping or may have been ejected from groups or clusters during the stripping process.
 
@@
 \noindent We lastly investigate the kinematics of the CCG sample using the $\sigma$s derived from SOAR and Gemini telescope data.
-\autoref{fig:sigma} plots the $\sigma$-M$_{\star}$ relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with measured $\sigma$s.
-Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since  they will have more  Conversely, $\sigma$s that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
+\autoref{fig:sigma} plots the Faber-Jackson ($\sigma$-M$_{\star}$) relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with $\sigma$ measured.
+Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since they will have less stellar mass than the motions of the stars suggest should be there.
+Conversely, galaxies with $\sigma$ that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
 Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.
@@
 \includegraphics{faber-jackson_resolvesigmas.eps}
-\caption{Here we plot the stellar mass vs.
-velocity dispersion ($\sigma$) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
-Most CCGs appear to be following the dissipative formation track.}
+\caption{The Faber-Jackson relation (stellar mass vs.
+velocity dispersion) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
+We look for CCGs offset to higher $\sigma$ for its stellar mass, which may indicate tidal stripping as a possible formation scenario.
+The green point is M32, the prototypical cE, that is believed to be tidally stripped \citep{Faber1973}.
+In orange is the free floating cE discovered in \citet{Huxor2013} that is thought to be dissipatively formed.}
 \label{fig:sigma}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CCG formation and evolution} %kind of like a discussion section
+\section{CCG formation processes} %kind of like a discussion section
 \label{discussion}
 
-We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
+\noindent We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
+For this discussion, we classify CCGs using the terms ``CSS-like'', ``dE-like'', or ``crossover''.
+A CSS-like CCG will have a small core radius and a $\sigma$ value offset higher off the main Faber-Jackson relation, like is expected for UCDs and cEs that have been tidally stripped.
+A dE-like CCG will have a large core radius and low $\sigma$ like is expected for dEs that are dissipatively formed.
+Crossover CCGs will have either large core radius and high $\sigma$ or small core radius and low $\sigma$.
 
-\subsection{rs0345}
+We have replotted Figures 3, 5, and 6 in \autoref{fig:miniplots}, this time highlighting the eight CCGs with velocity dispersions only.
+An important caveat for the CSSs and dEs in the AIMSS catalog is that the radius measurements are not decomposed into one and two components.
+To correct for this, we plot in the top left panel of \autoref{fig:miniplots} the one component \Reff\ instead of the two component core \Reff\ so that we may accurately compare the radius measurements of CCGs to those of the AIMSS objects.
 
-\subsection{rs0567, rs1186, rf0078}
+\subsection{dE-like CCGs}
+We classify rs0345, rs1100, rf0003, and rf0328 as dE-like CCGs, based on high one-component effective radius and low $\sigma$.
+The CCGs rs0345 and rs1100 are both envelope-dominated, live firmly on the blue sequence, and are forming stars quite rapidly with FSMGR~$>1$.
+Despite having a low stellar mass ($\sim10^{ 8.3}$~\Msun), it's baryonic (gas+stars) mass is higher than many RESOLVE galaxies, suggesting a large gas reservoir fueling star formation.
+The galaxy is in a moderately-sized group (halo mass $\sim10^{11.7}$~\Msun) and is within $\sim$0.15~Mpc from a companion galaxy.
+Taken together rs0345 may be an example of tidal stripping or dissipative formation actively occurring, which is fueling the star formation and funneling gas from the disk to build a core.
 
 \subsection{rs1100}
+Galaxy rs1100 is envelope-dominated and has one of the highest core \Reff values in the same at $\sim 800$~pc.
+It is on the blue sequence and has a large FSMGR, suggesting much past star formation.
+It also lives in a large group with halo mass $\sim10^{12.6}$~\Msun, and has a close neighbor.
+Its $\sigma$ value places it on the dissipative formation track.
+We propose that rs1100 may be a galaxy in the process of being ram pressure stripped in the large group environment, or may be dissipatively forming actively.
 
-\subsection{rf0003}
+The CCGs rf0003 and rf0328 are both core-dominated, live intermediate between the blue and red sequences and has a low FSMGR, near $\sim0.10$.
+It is also in a small group and is $>2$~Mpc from another galaxy, making it perhaps a ``free floating'' CCG, similar to the object found in \citet{Huxor2013}.
+Its $\sigma$ places it firmly along the main Faber-Jackson relation.
+All together, these clues point to a dissipatively-formed CCG.
+However, being near the green valley may indicate that this formation occurred relatively recently.
 
-\subsection{rf0328}
+\ has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr.
+The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor.
+Its $\sigma$ places it among the dissipatively formed CCGs, and like rf0003, its color and FSMGR may indicate this formation happened recently.
 
-\subsection{rf0492}
-This galaxy has a core+envelope morphology and lives on the red sequence, has an FSMGR$\sim 0.08$, and has a prominent core, and can be seen in the center image of \autoref{fig:pics}.
-Its nearest 3D neighbor is 2.63 Mpc away, making it fairly isolated, even though it lives in a group with halo mass = $10^{12.09}$ M$_{\odot}$.
-This could be an example of a CCG that was perturbed, perhaps even ram pressure stripped, as it fell into this larger group, causing gas to funnel to the center to create the core we see.
+\subsection{CSS-like CCGs}
+
+\subsection{Crossover CCGs}
+We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small radius measurements and low $\sigma$ values.
+The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies.
+They live on the red sequence and display little star formation with FSMGR $> 0.1$ for all.
+They reside in smaller groups and have moderately close neighbors.
+
+We note that there are CSSs in AIMSS that follow this track with extremely low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$).
+We postulate that these may be low-$z$ analogues to ``red nuggets'' found at high-$z$.
 
@@
 \includegraphics[scale=0.7]{miniplots.eps}
-\caption{Here we plot the stellar mass vs.
-velocity dispersion ($\sigma$) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
-Most CCGs appear to be following the dissipative formation track.}
+\caption{We show here \textbf{(a.)} deconvolved \Reff\ vs.
+stellar mass, \textbf{(b.)} the nearest two-dimensional neighbor vs.
+group halo mass, \textbf{(c.)} $u-r$ color vs.
+stellar mass, and \textbf{(d.)} FSMGR vs.
+baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information.
+This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.}
 \label{fig:miniplots}
@@
 
+%\subsection{CCGs without velocity dispersions}
+
+%For the other 88 CCGs without velocity dispersions, we attempt to classify their formation scenarios using the above cases as a primer.
+We divide the above 8 CCGs into four categories: ``forming with uncertain origins'' (rs0345, rs1100), ``recently formed with dissipative origins likely'' (rf0003, rf0328), ``uncertain stripping and dissipative formation'' (rf0492), and ``likely dissipatively formed'' (rs0567, rs1186, rf0078).
+
+%``Forming with uncertain origins'' CCGs are easily characterized as having envelopes (log(flux ratio) $<$ -0.1), high FSMGR ($>0.5$), and living in high mass groups ($>10^{11.5}$~\Msun).
+There are 6 CCGs with these parameters ($\sim1\%$ of the sample), including the two already identified.
+CCGs in the ``likely dissipatively formed'' are also easy characterized by having cores (log(flux ratio) $>$ 0.1), low FSMGR ($>0.5$), and living in low mass groups ($>10^{11.5}$~\Msun).
+There are 21 CCGs with these parameters ($\sim21\%$ of the sample), again including the three already identified.
+This leaves 66 CCGs left to classify, but the remaining groups, ``uncertain stripping and dissipative formation'' and ``recently formed'' are more difficult to classify definitely due to their ranges of colors, morphologies, and environments.
+This leaves $\sim69\%$ of the CCG unclassified until more velocity information is available.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}
+\section{Conclusions}
 \label{conclusions}
@@
 
-\item Using velocity dispersions ($\sigma$) derived from the SOAR and Gemini telescopes, we look for offsets in $\sigma$-M$_{\star}$ relation that could point to tidal stripping or dissipative formation scenarios (see \autoref{fig:sigma}).
-We find that CCGs tend to follow the dissipative formation track, however one CCG with a core+envelope lies close to M32, a tidally stripped cE, in the relation.
+\item Using velocity dispersions ($\sigma$) derived from the SOAR and Gemini telescopes, we classify the eight CCGs with $\sigma$ measurements as ``CCS-like'', ``dE-like'', or ``crossover'', based on their one-component radius measurements (the top left panel of \autoref{fig:miniplots}) and position on the Faber-Jackson ($\sigma$-M$_{\star}$) relation (\autoref{fig:sigma}).
+We find four CCGs that are dE-like and four that are crossovers.
+
+%In \autoref{fig:sigma}, we find that 6 CCGs tend to follow the main Faber-Jackson trend, which is expected for galaxies formed via dissipative formation, and two CCGs that may be slightly offset to higher $\sigma$.
+
+%\item Using the 8 CCGs with velocity dispersions as a primer, we attempt to quantify the number of CCGs that are tidally stripped or dissipatively formed based on morphologies, colors, FSMGR, and environment.
+We estimate $\sim$6\% of CCGs are actively forming (though the driver is uncertain) and $\sim$21\% are likely dissipatively formed.
+The remaining $\sim69$\% need more information to be classified.
 \end{enumerate}
 
-\noindent Future work will include investigating the gas content and metallicities of CCGs.
-The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
+\noindent Future work will include the following:
+
+\begin{enumerate}
+
+\item \textit{Redefine CCG sample using $\chi^2$ analysis.}
+
+\item \textit{Investigate gas content.} The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
 For example, a CCG in a galaxy cluster with little HI gas may point towards ram pressure stripping being important.
 Combined with CCG colors and FSMGR, the gas content may be an important tool in determining the evolution of a CCG.
-\citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
+
+\item \textit{Investigate metallicities.} \citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
 With the SOAR data we have in hand, we may be able to test this hypothesis for the CCG sample and use this method as another way to discern formation scenarios.
 
-\acknowledgments{ \textit{Acknowledgements.}
+\end{enumerate}
+
+\noindent \acknowledgments{ \textit{Acknowledgments.}
 This work has been supported by funding from NSF grants AST-0955368 and OCI-1156614 and NASA grant HST-AR-12147.01-A. 
-}
+Based on observations obtained at the Gemini Observatory under program numbers GS-2013B-Q52, GS-2014B-Q-13, GS-2014B-Q-51, and GS-2015B-C-1, which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).}
 

### 2016-05-11 paperdraft.tex
text updates

@@
 The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
-We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs, dEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
+We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
 We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component.
@@
 With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars.
-We find that CCGs naturally occur in a range of environments from isolated to cluster.
+We find that CCGs naturally occur in a range of environments from free floating to cluster.
 We also derive velocity dispersions ($\sigma$) for 8 CCGs from Gemini IFU data and SOAR spectroscopy.
-Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping or dissipative formation, respectively.
-Initial results show 6 CCGs likely following the dissipative formation track and 2 CCGs that are slightly offset to higher $\sigma$.
+Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping (as expected for cEs) or dissipative formation (as expected for dEs), respectively.
+Initial results show 4 CCGs likely following the dissipative formation track and 4 CCGs that are intermediate.
 
@@
 
-\noindent The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range between globular clusters (GCs) and normal elliptical galaxies (Es).
+  The term compact stellar system (CSS) encompasses a class of galaxies that spans the radius range between globular clusters (GCs) and normal elliptical galaxies (Es).
 Different types of CSSs include compact elliptical galaxies \citep[cEs;][]{Faber1973} and ultra compact dwarf galaxies \citep[UCDs;][]{Phillipps2001}.
@@
 
-In contrast to CSSs, dwarf elliptical galaxies (dEs) and their nucleated counterparts (dE,Ns) are quite common, especially in clusters where they were first discovered.
+In contrast to CSSs, dwarf elliptical galaxies \citep[dEs;][]{Sandage1985} and their nucleated counterparts \citep[dE,Ns;][]{Binggeli1984} are quite common, especially in clusters where they were first discovered.
 In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles.
-dEs are typically larger than CSSs with radii ranging up to $\sim800$~pc, whereas dE,Ns may have larger envelopes with a core radius <$800$~pc \citep[e.g.,][]{Norris2014}.
+While dEs are typically larger than CSSs with half light radii ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized.
 Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
@@
 
-Since dEs and dE,Ns are already divided into one and two component categories, it's easier to see the two morphologies are commonly found.
-\citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping.
-The authors go on to  argue that this excludes dEs as being the progenitors of UCDs, however, \citet{Pfeffer2013} seems to dispel this notion.
+By their nomenclature, dEs and dE,Ns have already been divided into one and two component morphologies.
+Studies have found that dE,Ns are usually more common than dEs: \citet{Grant2005} find that the majority of Virgo cluster dwarfs are indeed nucleated and speculate that at least some of the nuclei were formed out of an existing non-nucleated galaxy from infalling gas.
+Another possibility is that the morphology is already in place as dEs/dE,Ns form: \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs/dE,Ns enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping, leaving the dEs/dE,Ns we observe today.
 
@@
 \citet{Drinkwater2000} have examined the stellar populations of CSSs and find that CSSs are usually best fit as having older stellar populations.
-\citet{Norris2011} find a similar result with one UCD best fit using older stellar populations.
+However, \citet{Norris2011} find a UCD with young stellar populations and smoking gun signs of tidal stripping origins, including counter-rotating gas and a short dynamical friction timescale.
+\citet{Maraston2004} also find a young tidally formed UCD near the merger remnant galaxy NGC~7252.
+This evidence makes it clear that CCSs can have young and old stellar populations.
+
+For dEs and dE,Ns, there is similar diversity in colors.
 \citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.
+\cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.
 
@@
 Thus, galaxies that are offset to higher $\sigma$ in a Faber-Jackson (stellar mass -- $\sigma$) relation \citep{faber1976} are most likely tidally stripped, while galaxies falling along the relation are most likely the low-mass extension of normal Es.
+Lending evidence to this idea are the tidally-stripped UCD found in \citet{Maraston2004} and the prototypical cE, M32, both of which have much larger velocity dispersions than expected for their mass.
 
@@
 
-\noindent We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs.
+  We use the RESOLVE survey \citep[][Kannappan et al., in prep]{Kannappan2008} as the parent sample for our census of CCGs.
 RESOLVE is ideal because it is an unusually complete and volume-limited survey, which allows us to find CCGs at all evolutionary stages.
@@
 These values are M$_{\star}~\sim~10^{8.9}$~\Msun~for the A semester and M$_{\star}~\sim~10^{8.7}$~\Msun~in the B semester \citep[Figure 8 in ][]{Eckert2016}.
-These stellar mass completeness limits allow us to reach down to CSSs with sizes and masses similar to cEs (see \autoref{morph} for more details).
+These stellar mass completeness limits allow us to reach down to CSSs with sizes and masses similar to cEs (see \autoref{morph} for more details), but restricts us from reaching down to UCD masses.
 
@@
 
-\noindent We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.
+  We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.
 AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects.
@@
 Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs.
+We also note that the objects in AIMSS are not decomposed, meaning their \Reff\ are all single component fits.
+We discuss this more in \autoref{discussion}.
 
@@
 
-\noindent We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample.
+  We begin our analysis by deriving seeing-deconvolved \Reff\ measurements for all galaxies in the RESOLVE sample.
 For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits to each galaxy.
@@
 
-\noindent Our last step is to fit a 2D Gaussian to the PSF to determine a rough estimate seeing full width half max (FWHM), as a sanity check.
+Our last step is to fit a 2D Gaussian to the PSF to determine a rough estimate seeing full width half max (FWHM), as a sanity check.
 We find that the average FWHM for all PSFs is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.}
@@
 axial ratio (b/a) & 0 -- 1 \\
-position angle (PA)) & -360 -- 360 \\ \hline
+position angle (PA) & -360 -- 360 \\ \hline
 \end{tabular}
@@
 
-\noindent We use all of the above to obtain a one component, seeing-deconvolved fit for every galaxy in the RESOLVE survey.
+  We use all of the above to obtain a one component, seeing-deconvolved fit for every galaxy in the RESOLVE survey.
 We then perform the two component fits as follows.
@@
 The constraints for each parameter are the same for both sets.
-We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over constrain our fits.
+We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over-constrain the fits.
 
-For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.
-See \autoref{fig:galfit} for example one and two component fits for a RESOLVE galaxy.
+For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle as well as the $\chi^2$, $\chi^2/\nu$ and number of degrees of freedom for the fit.
+Also output is a fits file that contains the data, best fit model, and residual images.
+See \autoref{fig:galfit} for example one and two component fits for the RESOLVE galaxy rf0055.
 
@@
 \begin{center}
-\includegraphics{CCGpics.eps}
-\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to envelope+core to core-only.
+\includegraphics[scale=0.65]{coretoenvelopeims.eps}
+\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to core+envelope to core-only.
 Images are taken from the SDSS-DR8 image list tool.
-The central image is rf0492, a CCG with possible ram pressure stripping origins (see \autoref{kin}).}
+The galaxy rf0250 is an example of one of eleven CCGs that was fit with a large diffuse envelope and has hence been reclassified as ``core-dominated''.}
 \label{fig:pics}
@@
 
-\noindent Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies.
-We use the AIMSS sample to select a maximum cutoff core-only radius for CCGs at 800 pc.
-This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs.
-RESOLVE's lower stellar mass limit of  restricts us from reaching down to UCD masses.
+Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies.
+We select a maximum cutoff core-only radius for CCGs at 800~pc.
+Comparing to the CSSs and dEs/dE,Ns in the AIMSS catalog, this upper limit ensures that we are selecting CSSs in RESOLVE with \Reff\ up to 600~pc and lets us include the smallest dEs and dE,Ns as well.
 
-We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc.
-Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
-We note that this limit is arbitrary, and will be relaxed in the future (see \autoref{conclusions}).
+We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$~pc.
+Since we are looking for galaxies with compact cores, extending to \Reff\ $\sim 1000$~pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
+We do note that this limit is arbitrary, and will be relaxed in the future to allow CCGs with larger envelopes be included in the sample (see \autoref{conclusions}).
 We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spiral or irregular galaxies.
@@
 
-We quantify the amount of light in the core vs.~the envelope by taking a ratio of the fluxes of the core and the envelope.
-The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
+We quantify the amount of light in the core vs.~the envelope by taking a ratio of the flux in each component.
+We compute the fluxes using $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
+We note that \textsc{Galfit} calculates the integrated magnitude for S\'ersic profiles using the equations:
+
+\begin{eqnarray}
+\text{flux}~&=&~2~\text{R}_{eff}^2~\Sigma_e~\text{e}^{\kappa}~n~(\kappa)^{-2n}~\Gamma(2n)~(b/a)~/~R(C_0; m) \\
+\kappa~&\approx&~1.999~n~-~0.327\\
+m~&=&~-2.5~\log_{10}(\text{flux}/t_{exp})~+~\text{mag zpt},
+\end{eqnarray}
+
+where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag zpt is the zero point magnitude of the image.
+Since \textsc{Galfit} also outputs the S\'ersic n values, we can also plot the one dimensional light profiles for each component.
+In \autoref{fig:pics} we plot five CCGs spanning the range of log(flux ratio) values along with their one dimensional S\'ersic light profiles.
+Since the fluxes are calculated using the two dimensional ellipsoidal shape of the galaxy, the one dimensional profile may not always match what we expect the log(flux ratio) value to be.
+
 For each plot in this paper, we color code the CCGs by the logarithm of the flux ratio.
-CCGs with more light in the envelope will have log(flux ratio) $<$ 0, and will hereafter be called ``envelope-dominated' CCGs.
-CCGs with more light in the core will have log(flux ratio) $>$ 0, and will hereafter be called ``core-dominated'' CCGs.
-CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs.
-See \autoref{fig:pics} for examples of CCGs on this continuous scale.
-There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead.
-Where this happens (5 out of 96 cases), we classify this fit as either all core/all envelope depending on which component was bad (log(flux ratio) = -1 or 1).
-We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component.
-When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).
+CCGs with more light in the envelope will have log(flux ratio)~$<$~0, and will hereafter be called ``envelope-dominated' CCGs.
+CCGs with more light in the core will have log(flux ratio)~$>$~0, and will hereafter be called ``core-dominated'' CCGs.
+CCGs with log(flux ratio) $\sim~0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs.
 
-\begin{figure*}[hbpt!]
-\begin{center}
-\includegraphics{Reff_Mstars.eps}
-\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs of the AIMSS catalog.
-In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff.
-The CCG sample is using the core \Reff\ of the two component fits, which is why they may appear separated from the full RESOLVE sample.
-The colors of the CCGs represent the logarithm of the flux ratio between the core and envelope.
-Galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $\sim \pm 1$ will have more light in the core (+1) or envelope (-1).}
-\label{fig:radius}
-\end{center}
-\end{figure*}
+We also note that there are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead.
+When this happens (11 out of 96 cases), we classify this fit as either all core/all envelope depending on which component was bad, i.e., assigning log(flux ratio) = minimum of all flux ratios ($-0.93$) or maximum of all flux ratios ($+1.31$)\footnote{An example of this case is CCG rf0250, which is plotted on the far right of \autoref{fig:pics}.}.
+In six of 96 cases, \textsc{Galfit} fits identical \Reff\ values for both the first and second S\'ersic components.
+We inspect their S\'ersic plots by eye and see that these should be core-dominated CCGs.
+We assign these cases to have log(flux ratio) = maximum of all flux ratios ($+1.31$) as well.\footnote{An example of this case is CCG rf0003, which is plotted in the top right of \autoref{fig:imageplots}.}
 
@@
 \label{phot}
-\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
+  The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
 These photometry data has been reprocessed to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
@@
 \citet{Kannappan2013} design their model to also estimate FSMGR, which is the ratio of stellar mass created in the last Gyr to the stellar mass previously existing (i.e., an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr).
-Likelihood weighted model colors are also output with k-corrections to $z=0$.
+Likelihood weighted model colors are also output with extinction corrections and k-corrections to $z=0$.
 
-Baryonic masses are estimated
+Baryonic masses are from \citet{Eckert2016}, and are calculated as follows.
 
@@
 \label{env}
-\noindent The volume-limited design of RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
+The volume-limited design of RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
 We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy.
@@
 \subsubsection{SOAR spectroscopy}
-\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile.
+  The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile.
 We employ the Goodman Spectrograph \citep{Clemens2004} along with RESOLVE's custom-built image slicer with three parallel $1''$ slits to observe galaxies in either an emission- or absorption-line kinematic setup depending on whether the stellar continuum or gas emission lines are more prominent.
 With the absorption-line setup we are able to derive velocity dispersions, which are typically the best kinematic metric for CCGs.
-We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335.
+We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858 -- 5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335.
 To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.
@@
 We then use \texttt{LA\_COSMIC} \citep{vanDokkum2001} to clean cosmic rays from each science exposure.
-We next complete a wavelength calibration and transformation, and then perform object tracing and extraction into a 1D spectrum using the IRAF task apall.
-We lastly combine the individual exposures using the IRAF task scombine.
+We next complete a wavelength calibration and transformation.
+We lastly combine the individual exposures using the IRAF task scombine, leaving us with high signal-to-noise two-dimensional (y position vs.~wavelength) spectra for each galaxy.
 
@@
 
-\noindent A subset of the faintest or smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR.
-For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of $3''\times5''$ and the spectral range 4200-5600\AA.
-The B1200 grating offers 0.9\AA\ resolution when binned spectrally by 2.
-We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by 2 in the spectral direction and summing the fibers out to \Reff.
+  A subset of the faintest or smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR.
+For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of $3''\times5''$ and the spectral range 4200 -- 5600\AA.
+The B1200 grating offers 0.9\AA\ resolution when binned spectrally by two.
+We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by two in the spectral direction and summing the fibers out to \Reff.
 
@@
 We then correct the science frames for quantum efficiency differences between CCDs.
-Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed.
-We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$.
-More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix.
+Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made with $0.2''$ resolution (the width of each fiber).
+We stack the individual data cubes for each galaxy, leaving us with high signal to noise three-dimensional (x and y position vs.~wavelength) spectra.
+We lastly create a World Coordinate System \citep[WCS,][]{Greisen2002} solution for the data cube using the coordinates of the acquisition images and the position angle of the observation.
+More information on this process and the data reduction for the Gemini GMOS IFU in general can be found in the Appendix.
 
@@
 
-\noindent We measure $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}.
-This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$.
+  We use {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004} to measure the velocity dispersion ($\sigma$) for each galaxy.
+This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input one dimensional spectrum, and determines a best fit solution for $\sigma$.
+To create a one dimensional spectrum from the SOAR spectra, we first do a gaussian fit in the y-direction of the image to find the central row, which represents the center of the galaxy.
+We then sum the spectra in each row above and below the central row out to the effective radius of the galaxy to create the one dimensional spectrum.
+For the Gemini data cubes, we find the central position of the galaxy using its WCS solution, and then sum in all directions from the central spectrum out to the effective radius of the galaxy to create the one dimensional spectrum.
+Next, we must calculate the FWHM resolution of each spectrum so that {\sc pPXF} can convolve the model spectra with the input spectrum before performing the fits.
+To do this, we measure the FWHM of three unblended emission lines in the comparison arc spectrum taken with our galaxy spectra during observations (for both SOAR and Gemini).
+The average of these three measurements is the resolution we feed {\sc pPXF}.
 In \autoref{fig:ppxffit}, we show an example of a pPXF fit for one of the CCGs observed with the Gemini-South IFU.
-In black is the observed spectrum that has been summed out to \Reff\ and in red is the pPXF best fit model spectrum.
+In black is the observed spectrum that has been summed out to \Reff\ and in red is the pPXF best fit model spectrum, centered on the MgB triplet at $\sim 5275$ \AA.
+
 A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skew the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy.
@@
 
+\begin{figure*}[hbpt!]
+\begin{center}
+\includegraphics{Reff_Mstars.eps}
+\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs of the AIMSS catalog.
+In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff.
+The CCG sample is plotted using the core \Reff\ of the two component fits, which is why they may appear separated from the full RESOLVE sample.
+The colors of the CCGs represent the logarithm of the flux ratio between the core and envelope.
+Galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $>~1$ will have more light in the core and log(flux ratio) $>~1$ will have more light in the envelope.}
+\label{fig:radius}
+\end{center}
+\end{figure*}
+
 We plot in \autoref{fig:radius} the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs and dEs of the AIMSS catalog.
@@
 The CCG sample is plotted again with the core \Reff\ of the two component fits, causing them to shift down from the full RESOLVE sample.
-The symbol color for the CCGs represents the logarithm of the light ratio between the core and envelope, meaning that galaxies with log(flux ratio) near 0 will have both a core and envelope, while galaxies with log(flux ratio) $\sim \pm 1$ will have more light in the core (+1) or envelope (-1).
+The symbol color for the CCGs represents the logarithm of the light ratio between the core and envelope, meaning that galaxies with log(flux ratio) near zero will have both a core and envelope, while galaxies with log(flux ratio) greater or less than zero will have more light in the core or envelope, respectively.
 We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
@@
 \includegraphics[scale=0.65]{sfr_mbary.eps}
-\caption{\textbf{(a.)} On the left we plot the $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample.
-\textbf{(b.)} On the right we have plotted the FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample.
+\caption{\textbf{(Left.)} On the left we plot the $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample.
+\textbf{(Right.)} On the right we have plotted the FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample.
 }
@@
 
-\noindent We begin by examining the colors of the CCG sample.
+ We first examine the colors of the CCG sample.
 The left side of \autoref{fig:fsmgr} shows the k-corrected and extinction-corrected $u-r$ colors (as described in \autoref{phot}) of our CCG sample plotted against M$_{\star}$, compared to the RESOLVE sample as a whole.
-An unusual finding is that many CCGs live on the blue sequence, since most CSSs are typically thought of as being ``red and dead'', except for dE,Ns with blue cores.
+An unusual finding is that many CCGs live on the blue sequence, since most CSSs are most often thought of as being ``red and dead''.
 The right side of \autoref{fig:fsmgr} shows FSMGR vs.
 M$_{\rm bary}$ for the same objects.
-As with the colors, we find that many CCGs are forming stars at a rapid rate (FSMGR $\sim1$ means that the galaxy has doubled its mass in the last Gyr), again an unexpected finding which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if tidally-stripped remnants).
+As with the colors, we find that many CCGs are forming stars at a rapid rate (FSMGR $\sim~1$ means that the galaxy has doubled its mass in the last Gyr), again an unexpected finding which could indicate that some CCGs are still in the process of forming (if dissipatively formed) or relaxing (if tidally-stripped remnants).
 
-Looking now at the log(flux ratio values), we see that red sequence CCGs tend to be more core-dominated, while blue sequence CCGs tend to me more envelope-dominated.
-There also tends to be more core-dominated CCGs at lower FSMGR, while envelope-dominated CCGs reside at higher FSMGR.
-There is considerable scatter though, making these trends harder to qualify.
-
-\subsection{Environments}
-\noindent We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
-There are many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could have occurred for those CCGs.
-On the opposite end, we see several CCGs in massive group halos, and these CCGs tend to be either core- or envelope dominated.
-This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies.
-There are also nine CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, and four of those are core dominated, resembling the isolated cE found by \citet{Huxor2013}.
-These free floating CCGs may be the result of dissipative formation since there is no nearby object to have performed the stripping or may have been ejected from groups or clusters during the stripping process.
+%add statistical test at some point
 
@@
 
-\subsection{Kinematics}
-\label{kin}
-\noindent We lastly investigate the kinematics of the CCG sample using the $\sigma$s derived from SOAR and Gemini telescope data.
-\autoref{fig:sigma} plots the Faber-Jackson ($\sigma$-M$_{\star}$) relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with $\sigma$ measured.
-Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since they will have less stellar mass than the motions of the stars suggest should be there.
-Conversely, galaxies with $\sigma$ that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
-Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.
+\subsection{Environments}
+We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
+There are many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could have occurred for those CCGs.
+On the opposite end, we see several CCGs in massive group halos, and these CCGs tend to be either core- or envelope dominated.
+This hints towards ram pressure stripping being at play in these environments, especially for those CCGs at larger distances from other galaxies.
+There are also nine CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, and four of those are core dominated, resembling the isolated cE found by \citet{Huxor2013}.
+These free floating CCGs may be the result of dissipative formation since there is no nearby object to have performed the stripping or may have been ejected from groups or clusters during the stripping process.
 
@@
 
+\subsection{Kinematics}
+\label{kin}
+ We lastly investigate the kinematics of the CCG sample using $\sigma$ values derived from SOAR and Gemini telescope data.
+\autoref{fig:sigma} plots the Faber-Jackson ($\sigma$-M$_{\star}$) relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with $\sigma$ measured.
+Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since they will have less stellar mass than the motions of the stars suggest should be there.
+Conversely, galaxies with $\sigma$ that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
+Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\noindent We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
+We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
 For this discussion, we classify CCGs using the terms ``CSS-like'', ``dE-like'', or ``crossover''.
-A CSS-like CCG will have a small core radius and a $\sigma$ value offset higher off the main Faber-Jackson relation, like is expected for UCDs and cEs that have been tidally stripped.
-A dE-like CCG will have a large core radius and low $\sigma$ like is expected for dEs that are dissipatively formed.
+A CSS-like CCG will have a small core radius and a $\sigma$ value offset from the main Faber-Jackson relation, as expected for UCDs and cEs that have been tidally stripped.
+A dE-like CCG will have a large core radius and low $\sigma$ as is expected for dEs that are dissipatively formed.
 Crossover CCGs will have either large core radius and high $\sigma$ or small core radius and low $\sigma$.
+Following this logic, we classify M32 as CCS-like since it has \Reff~$\sim~100$~pc and $\sigma$ offset to higher dispersion.
+The cE discovered in \citet{Huxor2013} is a crossover, since it has \Reff~$\sim~500$~pc and a $\sigma$ value falling along the main Faber-Jackson relation.
 
-We have replotted Figures 3, 5, and 6 in \autoref{fig:miniplots}, this time highlighting the eight CCGs with velocity dispersions only.
+We have replotted Figures 4, 5, and 6 in \autoref{fig:miniplots}, this time highlighting the eight CCGs with velocity dispersions only.
 An important caveat for the CSSs and dEs in the AIMSS catalog is that the radius measurements are not decomposed into one and two components.
@@
 \subsection{dE-like CCGs}
-We classify rs0345, rs1100, rf0003, and rf0328 as dE-like CCGs, based on high one-component effective radius and low $\sigma$.
+We classify rs0345, rs1100, rf0003, and rf0328 as dE-like CCGs, based on their high one-component effective radius and low $\sigma$.
 The CCGs rs0345 and rs1100 are both envelope-dominated, live firmly on the blue sequence, and are forming stars quite rapidly with FSMGR~$>1$.
-Despite having a low stellar mass ($\sim10^{ 8.3}$~\Msun), it's baryonic (gas+stars) mass is higher than many RESOLVE galaxies, suggesting a large gas reservoir fueling star formation.
-The galaxy is in a moderately-sized group (halo mass $\sim10^{11.7}$~\Msun) and is within $\sim$0.15~Mpc from a companion galaxy.
-Taken together rs0345 may be an example of tidal stripping or dissipative formation actively occurring, which is fueling the star formation and funneling gas from the disk to build a core.
+The galaxies reside in intermediate-sized groups (halo masses $\sim10^{11.7-12.5}$~\Msun) and are both within $<~0.15$~Mpc from a companion galaxy.
+Taken together these data suggest that rs0345 and rs1100 may be an example of tidal stripping or dissipative processes actively occurring, which is fueling the star formation and funneling gas from the disk to build a core.
+Judging from the regular morphologies seen in the images of these CCGs in \autoref{fig:imageplots}, tidal stripping and dissipative formation via merging are unlikely, which leaves ram pressure stripping as a probable formation scenario.
 
-\subsection{rs1100}
-Galaxy rs1100 is envelope-dominated and has one of the highest core \Reff values in the same at $\sim 800$~pc.
-It is on the blue sequence and has a large FSMGR, suggesting much past star formation.
-It also lives in a large group with halo mass $\sim10^{12.6}$~\Msun, and has a close neighbor.
-Its $\sigma$ value places it on the dissipative formation track.
-We propose that rs1100 may be a galaxy in the process of being ram pressure stripped in the large group environment, or may be dissipatively forming actively.
-
-The CCGs rf0003 and rf0328 are both core-dominated, live intermediate between the blue and red sequences and has a low FSMGR, near $\sim0.10$.
-It is also in a small group and is $>2$~Mpc from another galaxy, making it perhaps a ``free floating'' CCG, similar to the object found in \citet{Huxor2013}.
+CCG rf0003 is core-dominated, lives intermediate between the blue and red sequences and has a low FSMGR ($\sim~0.10$).
+It resides in a low mass group (halo mass $\sim10^{10.9}$~\Msun) and is $>2$~Mpc from another galaxy, which we classify as free floating.
 Its $\sigma$ places it firmly along the main Faber-Jackson relation.
@@
 
-\ has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr.
+Lastly, rf0328 is also core-dominated and lives intermediate between the blue and red sequences, but has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr.
 The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor.
@@
 \subsection{CSS-like CCGs}
+We do not find any CSS-like CCGs in our subset of CCGs with kinematic data, however we expect that with additional velocity dispersion data, we will find CCGs following this track in the future.
 
 \subsection{Crossover CCGs}
-We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small radius measurements and low $\sigma$ values.
+We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500--700$~pc) and $\sigma$ values following the dissipative formation track.
 The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies.
-They live on the red sequence and display little star formation with FSMGR $> 0.1$ for all.
-They reside in smaller groups and have moderately close neighbors.
+They live on the red sequence and display little star formation (FSMGR $> 0.1$) for all.
+CCGs rs1186 and rf0078 both have close neighbors ($\sim~0.2$~Mpc distance), but rs0567 has a nearest neighbor $\sim~0.7$~Mpc, which makes it quite similar to the free floating cE discovered by \citet{Huxor2013} (which also has a core-dominated light profile).
 
-We note that there are CSSs in AIMSS that follow this track with extremely low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$).
-We postulate that these may be low-$z$ analogues to ``red nuggets'' found at high-$z$.
+CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:image plots}, but they don't share many other similarities.
+This CCG has a core+envelope profile and lives in an intermediate-sized group with halo mass~$\sim~10^{12}$~\Msun and neighbor within $\sim~0.11$~Mpc.
+
+There are some CSSs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$), making them dE-like as well.
+We postulate that galaxies like these and the other crossover CCGs discussed above may also be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$\sim~1$~kpc.
+\citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes (such as gas inflows to the central region of the disk) and then later quench to become red nuggets that are so common in the early Universe.
+
+There are also two AIMSS objects with the opposite conditions: large \Reff\ and high $\sigma$ (the two dark triangles in \autoref{fig:sigma} with M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~40-50~\text{km~s}^{-2}$).
+These dEs may be in the process of tidal stripping currently, and will move to the CSS-like track when the stripping is complete.
 
@@
 \includegraphics[scale=0.7]{miniplots.eps}
+\caption{\textbf{(Top left.)} deconvolved \Reff\ vs.
+stellar mass, \textbf{(Top right.)} the nearest two-dimensional neighbor vs.
+group halo mass, \textbf{(Bottom left.)} $u-r$ color vs.
+stellar mass, and \textbf{(Bottom right.)} FSMGR vs.
+baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information.
+This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.}
+\label{fig:miniplots}
+\end{center}
+\end{figure*}
+
+\begin{figure*}[b]
+\begin{center}
+\includegraphics[scale=0.7]{imageplots.eps}
 \caption{We show here \textbf{(a.)} deconvolved \Reff\ vs.
@@
 baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information.
-This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.}
-\label{fig:miniplots}
+This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.
+We also note that rf0003 is one of the six cases where \textsc{Galfit} finds identical \Reff\ values for both the first and second S\'ersic components, and have hence set log(flux ratio) = maximum of all flux ratios ($+1.31$).}
+\label{fig:imageplots}
 \end{center}
@@
 
-\noindent In this paper we have examined the colors, FSMGR, environments, and kinematics of the 96 compact core galaxies (CCGs) in the RESOLVE survey.
+  In this paper we have examined the colors, FSMGR, environments, and kinematics of the 96 compact core galaxies (CCGs) in the RESOLVE survey.
 We have selected CCGs to have a seeing-deconvolved, core-only \Reff\ $<$ 800 pc, based on the sizes of the compact and dwarf ellipticals in the AIMSS catalog.
@@
 
-\noindent Future work will include the following:
+  Future work will include the following:
 
@@
 
-\item \textit{Redefine CCG sample using $\chi^2$ analysis.}
+\item \textit{Redefine CCG sample using $\chi^2$ analysis.} As mentioned in \autoref{CCGs}, we want to redefine the CCG sample using the $\chi^2$ and number of degrees of freedom (NoDF) output by \textsc{Galfit} for each fit.
+This will entail using the $\chi^2$ and NoDF to decide whether the one or two component fits are best for all RESOLVE galaxies.
+Those best fit with one component would then be selected as a CCG if its one component \Reff\ is less than 800~pc, while those best fit with two components would be selected as a CCG if its core \Reff\ is less than 800~pc.
+This method replace the arbitrary cutoff for CCG candidates at \Reff~$<~1$~kpc, which should let us include more CCGs that have large diffuse envelopes and small cores that may be getting left out of our sample now.
 
-\item \textit{Investigate gas content.} The amount of neutral Hydrogen gas a CCG has may be able to give us insights into its evolution over time.
+\item \textit{Investigate gas content.} The amount of neutral Hydrogen gas CCGs have may give us insights into their evolution over time.
 For example, a CCG in a galaxy cluster with little HI gas may point towards ram pressure stripping being important.
@@
 \item \textit{Investigate metallicities.} \citet{Janz2015} have shown that tidally-stripped CSSs are systematically offset to higher metal abundances.
-With the SOAR data we have in hand, we may be able to test this hypothesis for the CCG sample and use this method as another way to discern formation scenarios.
+With the SOAR and Gemini spectroscopy currently in hand, we will be able to test this hypothesis for the CCG sample and use this method as another way to discern formation scenarios.
 
@@
 
-\noindent \acknowledgments{ \textit{Acknowledgments.}
+  \acknowledgments{ \textit{Acknowledgments.}
 This work has been supported by funding from NSF grants AST-0955368 and OCI-1156614 and NASA grant HST-AR-12147.01-A. 
-Based on observations obtained at the Gemini Observatory under program numbers GS-2013B-Q52, GS-2014B-Q-13, GS-2014B-Q-51, and GS-2015B-C-1, which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).}
+This work is based on data obtained as part of the UKIRT Infrared Deep Sky Survey.
+This work is based on observations obtained at the Gemini Observatory under program numbers GS-2013B-Q52, GS-2014B-Q-13, GS-2014B-Q-51, and GS-2015B-C-1, which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).}
 

### 2016-05-11 paperdraft.tex
paper draft 3

@@
 The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}.
-The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Jennings2015, Zhang2015}.
+The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}.
 \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
@@
 More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
-On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as mergers or in the two-phase formation process detailed in \citet{Oser2010}.
+On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or in the two-phase formation process detailed in \citet{Oser2010}.
 One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.
@@
 In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles.
-While dEs are typically larger than CSSs with half light radii ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized.
-Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevi2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
+While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized.
+Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevic2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
 They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}.
-There is also some evidence that dE,Ns are progenitors of UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
+There is also evidence that dE,Ns become UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
 
-Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core radii up to 800~pc.
+Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core \Reff\ up to 800~pc.
 The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios.
@@
 M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}.
-As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevi2014,Penny2014}.
-Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} find cEs separated from other galaxies by $>1$~Mpc.
+As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevic2014,Penny2014}.
+Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} both find one cE separated from other galaxies by $\sim~840$ and $\sim~600$~kpc, respectively.
 
@@
 \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures.
-Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center and star formation begins.
+Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas and star formation begins.
 This core is then ``puffed up'' through time as it interacts with other galaxies.
@@
 For dEs and dE,Ns, there is similar diversity in colors.
-\citet{Drinkwater2000} and \citet{Ferrarese2006} find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.
+\citet{SmithCastelli2012} find dEs in the Antlia cluster with both red and blue colors.
+\citet{Drinkwater2000} and \citet{Ferrarese2006} study the colors of dE,Ns and find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies.
 \cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.
@@
 After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions.
-AIMSS also includes literature data for previously known UCDs, cEs, (nucleated) dEs, dwarf spheroidals, dwarf S0s, young massive clusters, and Es.
+AIMSS also includes literature data for previously known UCDs, cEs, dEs, dE,Ns, dwarf spheroidals, dwarf S0s, young massive clusters, and Es.
 The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects.
@@
 
-\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file.
+\textsc{Galfit} needs the following input files to function properly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file.
 We obtain or construct these items as follows:
@@
 \item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters.
-For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile to the galaxy.
+For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile \citep{Sersic1963, Sersic1968} to the galaxy.
 The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
@@
 where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag zpt is the zero point magnitude of the image.
+Therefore the integrated magnitudes calculated take into account the two dimensional shape of the galaxy being fit.
 Since \textsc{Galfit} also outputs the S\'ersic n values, we can also plot the one dimensional light profiles for each component.
@@
 We inspect their S\'ersic plots by eye and see that these should be core-dominated CCGs.
-We assign these cases to have log(flux ratio) = maximum of all flux ratios ($+1.31$) as well.\footnote{An example of this case is CCG rf0003, which is plotted in the top right of \autoref{fig:imageplots}.}
+We assign these cases to have log(flux ratio) = maximum of all flux ratios ($+1.31$) as well\footnote{An example of this case is CCG rf0003, which is plotted in the top right of \autoref{fig:imageplots}.}.
 
@@
 More information on group identification can be found in \citet{Eckert2016}.
-The nearest 2-dimensional neighbor distances are computed using the RA and Dec coordinates for each galaxy along with a requirement that the neighbor be within $\pm~500$~km~$^{-1}$ of the primary.
+The nearest two-dimensional neighbor distances are computed using the RA and Dec coordinates for each galaxy along with a requirement that the neighbor be within $\pm~500$~km~$^{-1}$ of the primary.
 Three-dimensional distances are also available based on Hubble's Law distances, however the added errors that come with peculiar velocities make these values less reliable.
@@
 \caption{The Faber-Jackson relation (stellar mass vs.
-velocity dispersion) for the RESOLVE sample, CCGs, and the CSSs of the AIMSS catalog.
+velocity dispersion) for the RESOLVE sample, CCGs, and the cEs and dEs of the AIMSS catalog.
 We look for CCGs offset to higher $\sigma$ for its stellar mass, which may indicate tidal stripping as a possible formation scenario.
@@
 Its $\sigma$ places it firmly along the main Faber-Jackson relation.
-All together, these clues point to a dissipatively-formed CCG.
-However, being near the green valley may indicate that this formation occurred relatively recently.
+All together, these clues point to a dissipatively-formed CCG, perhaps through the convergence of cold streams.
+Residing near the green valley indicate that this formation may have occurred relatively recently.
 
@@
 The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor.
-Its $\sigma$ places it among the dissipatively formed CCGs, and like rf0003, its color and FSMGR may indicate this formation happened recently.
+Its $\sigma$ places it among the dissipatively-formed CCGs, perhaps due to cold gas streams converging or even a merger, given its environment.
+Like rf0003, its color and FSMGR may indicate this formation happened recently.
 
@@
 \subsection{Crossover CCGs}
-We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500--700$~pc) and $\sigma$ values following the dissipative formation track.
+We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500-700$~pc) and $\sigma$ values following the dissipative formation track.
 The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies.
@@
 
-CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:image plots}, but they don't share many other similarities.
+CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:imageplots}, but they don't share many other similarities.
 This CCG has a core+envelope profile and lives in an intermediate-sized group with halo mass~$\sim~10^{12}$~\Msun and neighbor within $\sim~0.11$~Mpc.
+It lives on the red sequence and has low FSMGR ($<~0.1$), making it a good candidate of a CCG formed via ram pressure stripping as a dwarf (perhaps an LCBD) fell into the group halo.
 
-There are some CSSs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$), making them dE-like as well.
-We postulate that galaxies like these and the other crossover CCGs discussed above may also be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$\sim~1$~kpc.
+We note that there are two cEs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$ in \autoref{fig:sigma}), and we classify these as crossovers as well.
+We postulate that galaxies like these and the other crossover CCGs discussed above may be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$<~1$~kpc.
 \citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes (such as gas inflows to the central region of the disk) and then later quench to become red nuggets that are so common in the early Universe.
@@
 There are also two AIMSS objects with the opposite conditions: large \Reff\ and high $\sigma$ (the two dark triangles in \autoref{fig:sigma} with M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~40-50~\text{km~s}^{-2}$).
-These dEs may be in the process of tidal stripping currently, and will move to the CSS-like track when the stripping is complete.
+These dEs may be in the process of tidal stripping currently and may move to the CSS-like track when the stripping is complete.
 
@@
 \includegraphics[scale=0.7]{miniplots.eps}
-\caption{\textbf{(Top left.)} deconvolved \Reff\ vs.
+\caption{\textbf{(Top left.)} single-component deconvolved \Reff\ vs.
 stellar mass, \textbf{(Top right.)} the nearest two-dimensional neighbor vs.
@@
 baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information.
-This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.}
+We emphasize that the \Reff\ values plotted in the top left panel are not the two-component core \Reff\ values as in \autoref{fig:radius} in order to compare our radius measurements with the CSSs of AIMSS that have not been decomposed.}
 \label{fig:miniplots}
@@
 \includegraphics[scale=0.7]{imageplots.eps}
-\caption{We show here \textbf{(a.)} deconvolved \Reff\ vs.
-stellar mass, \textbf{(b.)} the nearest two-dimensional neighbor vs.
-group halo mass, \textbf{(c.)} $u-r$ color vs.
-stellar mass, and \textbf{(d.)} FSMGR vs.
-baryonic mass for all galaxies in RESOLVE, the cEs and dEs of AIMSS, and the eight CCGs that have velocity dispersion information.
-This information, combined with \autoref{fig:sigma}, help us distinguish between formation scenarios for the CCG sample.
+\caption{The light profiles for the eight CCGs with velocity dipersion measurements.
+The $rgb$ images are from the SDSS-DR8 image list tool.
+Above each plot is the value of the logarithm of the ratio of the core and envelope fluxes, which are given via the symbol colors in \autoref{fig:sigma} and \autoref{fig:miniplots}.
 We also note that rf0003 is one of the six cases where \textsc{Galfit} finds identical \Reff\ values for both the first and second S\'ersic components, and have hence set log(flux ratio) = maximum of all flux ratios ($+1.31$).}

### 2016-05-13 paperdraft.tex
almost done!

@@
 \usepackage{epstopdf}
+\usepackage[final]{pdfpages}
 \usepackage{gensymb}
@@
 We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments.
-To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements.
-The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk.
-We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
-We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component.
-The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated.
+To identify CCGs, we use \textsc{Galfit} to perform one-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements.
+Candidate CCGs are selected to have \Reff~$<~1000$~pc.
+Two component (core and envelope) S\'ersic fits are then performed on the candidates with S\'ersic n fixed at 1 for an exponential disk profile for the envelope.
+We finalize the CCG sample by selecting core \Reff~$<~800$~pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog.
+We quantify the morphologies of CCGs by taking the logarithm of the ratio of the light in each component.
+The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated, which may represent earlier or later evolutionary stages of CCGs.
 With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars.
 We find that CCGs naturally occur in a range of environments from free floating to cluster.
-We also derive velocity dispersions ($\sigma$) for 8 CCGs from Gemini IFU data and SOAR spectroscopy.
+We derive velocity dispersions ($\sigma$) for eight CCGs from Gemini IFU data and SOAR spectroscopy.
 Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping (as expected for cEs) or dissipative formation (as expected for dEs), respectively.
-Initial results show 4 CCGs likely following the dissipative formation track and 4 CCGs that are intermediate.
+We classify CCGs as CSS-like (small radius and high dispersion), dE-like (large radius and low dispersion), or crossover (small radius and low dispersion).
+Initial results show four CCGs are dE-like and four are crossovers.
 
@@
 
-CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form.
+CSSs have half-light radii (\Reff) typically ranging from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple theories for how they form.
 The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}.
-The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}.
+There is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}.
 \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs.
@@
 More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole.
-On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or in the two-phase formation process detailed in \citet{Oser2010}.
+On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or the two-phase formation process detailed in \citet{Oser2010}.
 One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.
@@
 In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles.
-While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized.
+While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns are comparable in size to to CSSs and reside within larger envelopes that are dE-sized.
 Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevic2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}.
-They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}.
+They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that were ram-pressure stripped and quenched as they entered the cluster environment \citep{Lisker2013, Crawford2016a}.
 There is also evidence that dE,Ns become UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.
@@
 The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios.
-Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics.
+Clues to how CCGs form may be given by their environments,  morphology (i.e.
+one- or two-component structure), star formation histories, and kinematics.
 We highlight these data below.
@@
 UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}.
-M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}.
+M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs were later  found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}.
 As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevic2014,Penny2014}.
@@
 
-Environment bears on formation scenarios in different ways.
+Environment affects formation scenarios in different ways.
 One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CSSs may rather be dissipatively formed like Es.
 However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process.
-The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.
+The recent discovery of a free-floating GC and UCD that have likely been tidally stripped supports this idea \citep{Sandoval2015}.
 
@@
 \textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology.
-\citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin.
+\citet{Graham2002} has shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which points toward a tidal-stripping origin.
 \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures.
-Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas and star formation begins.
+Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas.
 This core is then ``puffed up'' through time as it interacts with other galaxies.
 The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation.
-It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.
+It is important to note that these effects may vary based on the degree of stripping and the time passed since the stripping or dissipative formation occurred.
 
@@
 Studies have found that dE,Ns are usually more common than dEs: \citet{Grant2005} find that the majority of Virgo cluster dwarfs are indeed nucleated and speculate that at least some of the nuclei were formed out of an existing non-nucleated galaxy from infalling gas.
-Another possibility is that the morphology is already in place as dEs/dE,Ns form: \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs/dE,Ns enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping, leaving the dEs/dE,Ns we observe today.
+Another possibility is that the morphology is already in place as dEs/dE,Ns form.
+For example, \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs/dE,Ns enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping, leaving the dEs/dE,Ns we observe today.
 
@@
 
-For dEs and dE,Ns, there is similar diversity in colors.
+For dEs and dE,Ns, there is similar diversity in color.
 \citet{SmithCastelli2012} find dEs in the Antlia cluster with both red and blue colors.
@@
   We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.
-AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects.
+AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies, in groups, and in clusters, and includes both previously known and newly discovered objects.
 The AIMSS CSS discovery process was as follows.
@@
 The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model).
-The top row shows the one component fit for one of the RESOLVE galaxies, rf0055.
+The top row shows the one component fit for the RESOLVE galaxy, rf0055.
 As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope.
@@
 The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.
-These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}
+We use initial values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}
 
@@
 While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful when constructing the PSF image.
-There are only 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.
+There are 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.
 
 \item[The PSF image]{\textsc{Galfit} uses the PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken.
-We build our PSF image via the following steps.
+We build our PSF image via the following steps:
+
 \begin{enumerate}
@@
 We use the output of the one component fit as the basis of the input file for the two component fit.
-The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed).
+The first two sections in the two component fit initial input file will be identical to the output of the one component fit.
 We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit.
-This gives \textsc{Galfit} an idea to fit on both a core and envelope.
+This gives \textsc{Galfit} a preliminary guess for the radius of an envelope.
 The PSF, image, and mask image will all be the same as before.
@@
 
-For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle as well as the $\chi^2$, $\chi^2/\nu$ and number of degrees of freedom for the fit.
+For both the one and two component fits, \textsc{Galfit} outputs the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle as well as the $\chi^2$, $\chi^2/\nu$ and number of degrees of freedom for the fit.
 Also output is a fits file that contains the data, best fit model, and residual images.
@@
 \includegraphics[scale=0.65]{coretoenvelopeims.eps}
-\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to core+envelope to core-only.
+\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to core+envelope to core-only from left to right.
 Images are taken from the SDSS-DR8 image list tool.
@@
 
-We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$~pc.
+We start by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$~pc.
 Since we are looking for galaxies with compact cores, extending to \Reff\ $\sim 1000$~pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit.
-We do note that this limit is arbitrary, and will be relaxed in the future to allow CCGs with larger envelopes be included in the sample (see \autoref{conclusions}).
-We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spiral or irregular galaxies.
+We do note that this limit is arbitrary, and it  will be relaxed in the future to allow CCGs with larger envelopes be included in the sample (see \autoref{conclusions}).
+We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals, which are normally spiral or irregular galaxies.
 After this selection, we are left with 124 galaxies in the CCG candidate sample.
 
-Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic component fit is constrained to always be larger than that of the first S\'ersic component fit, and (3) the S\'ersic n of the second component is held constant at 1 representing an exponentially decreasing disk profile.
+Next, we perform new two component fits using different constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic component fit is constrained to always be larger than that of the first S\'ersic component fit, and (3) the S\'ersic n of the second component is held constant at 1 representing an exponentially decreasing disk profile.
 We let the values of \Reff, integrated magnitude, b/a ratio, and PA change for both fits.
@@
 We compute the fluxes using $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}.
-We note that \textsc{Galfit} calculates the integrated magnitude for S\'ersic profiles using the equations:
+\textsc{Galfit} calculates the integrated magnitude for S\'ersic profiles using the equations:
 
@@
 \kappa~&\approx&~1.999~n~-~0.327\\
-m~&=&~-2.5~\log_{10}(\text{flux}/t_{exp})~+~\text{mag zpt},
+m~&=&~-2.5~\log_{10}(\text{flux}/t_{exp})~+~\text{mag}_{\varnothing},
 \end{eqnarray}
 
-where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag zpt is the zero point magnitude of the image.
-Therefore the integrated magnitudes calculated take into account the two dimensional shape of the galaxy being fit.
+where $\Sigma_e$ is the surface brightness at \Reff, $R(C_0; m)$ is a geometric correction factor when the azimuthal shape of the galaxy deviates from a perfect ellipse, $t_{exp}$ is the exposure time of the image, and mag$_{\varnothing}$ is the zero point magnitude of the image.
 Since \textsc{Galfit} also outputs the S\'ersic n values, we can also plot the one dimensional light profiles for each component.
@@
   The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}.
-These photometry data has been reprocessed to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
+These photometry data have been reprocessed to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}.
 The main improvements in this processing are (1) improved sky subtraction following \citet{Blanton2011} for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) definition of elliptical apertures using the sum of the high S/N $gri$ images to determine the PA and b/a ratio yielding improved sensitivity to the outer disk (if present), and (3) application of the same apertures to all bands, which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX.
@@
 
-Stellar masses, a long-term fractional stellar mass growth rate (FSMGR), and model colors are then derived from these reprocessed $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in  \citet{Kannappan2013}.
+Stellar masses ($\text{M}_{\star}$), a long-term fractional stellar mass growth rate (FSMGR), and model colors are then derived from these reprocessed $NUVugrizYJHK$ magnitudes using the spectral energy distribution (SED) modeling code described in  \citet{Kannappan2013}.
 We adopt the model grid from \citet{Kannappan2013} that combines old simple stellar populations with 2-12 Gyr age ranges and young stellar populations with either continuous star formation from 1015 Myr ago to 0-195 Myr ago, or with a simple stellar population with age either 360, 509, 641, 806, or 1015 Myr.
-A stellar mass is calculated for each model, along with a likelihood.
+A $\text{M}_{\star}$ likelihood distribution is calculated for each model, and the single value $\text{M}_{\star}$ is the median of the distribution.
 \citet{Kannappan2013} design their model to also estimate FSMGR, which is the ratio of stellar mass created in the last Gyr to the stellar mass previously existing (i.e., an FSMGR of 1 means that the galaxy has doubled its stellar mass in the last Gyr).
@@
 
-Baryonic masses are from \citet{Eckert2016}, and are calculated as follows.
+Baryonic masses ($\text{M}_{bary}$) are defined as $\text{M}_{\star}~+~\text{M}_{HI}$.
+HI values for RESOLVE are from the blind 21cm ALFALFA survey \citep{Haynes2011} and new pointed observations with the Greenbank and Arecibo telescopes (Stark et al., submitted).
+\citet{Eckert2016} calculates $\text{M}_{bary}$ by performing pseudo-convolutions of the likelihood distribution for $\text{M}_{\star}$ as computed above with the likelihoods for $\text{M}_{HI}$ computed in two ways.
+Galaxies with HI detections that are clean or successfully deconfused have Gaussian likelihood distributions with $\mu =  \text{M}_{HI}$ and $\sigma = $ the systematic uncertainty of the measurement.
+For galaxies with weak upper limits, low S/N or severely confused detections, or no HI observations at all, the log(gas-to-stellar mass) distributions from the photometric gas fraction calibration in \citet{Eckert2015} are used instead.
+For galaxies with strong upper limits, the likelihood in log(gas-to-stellar mass) is set to 1 at the upper limit value of
+log(gas-to-stellar mass). The single value $\text{M}_{bary}$ is computed by taking the median of the resulting baryonic mass likelihood distribution for each galaxy.
 
@@
 The volume-limited design of RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments.
-We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy.
+We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to a neighboring galaxy.
 The group halo mass allows us to look for CCG-host pairs that are M32--Andromeda analogues where tidal stripping is likely or conversely to look for CCGs in large groups where either ram-pressure or tidal stripping could be important.
@@
   The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile.
-We employ the Goodman Spectrograph \citep{Clemens2004} along with RESOLVE's custom-built image slicer with three parallel $1''$ slits to observe galaxies in either an emission- or absorption-line kinematic setup depending on whether the stellar continuum or gas emission lines are more prominent.
+We use the Goodman Spectrograph \citep{Clemens2004} along with RESOLVE's custom-built image slicer with three parallel $1''$ slits to observe galaxies in either an emission- or absorption-line kinematic setup depending on whether the stellar continuum or gas emission lines are more prominent.
 With the absorption-line setup we are able to derive velocity dispersions, which are typically the best kinematic metric for CCGs.
@@
 We next complete a wavelength calibration and transformation.
-We lastly combine the individual exposures using the IRAF task scombine, leaving us with high signal-to-noise two-dimensional (y position vs.~wavelength) spectra for each galaxy.
+We lastly combine the individual exposures using the IRAF task \textit{scombine}, leaving us with high signal-to-noise two-dimensional (y position vs.~wavelength) spectra for each galaxy.
 
@@
 The B1200 grating offers 0.9\AA\ resolution when binned spectrally by two.
-We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by two in the spectral direction and summing the fibers out to \Reff.
+We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by two pixels in the spectral direction and summing the fibers out to \Reff.
 
@@
 Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made with $0.2''$ resolution (the width of each fiber).
-We stack the individual data cubes for each galaxy, leaving us with high signal to noise three-dimensional (x and y position vs.~wavelength) spectra.
+We stack the individual data cubes for each galaxy, leaving us with high S/N three-dimensional (x and y position vs.~wavelength) spectra.
 We lastly create a World Coordinate System \citep[WCS,][]{Greisen2002} solution for the data cube using the coordinates of the acquisition images and the position angle of the observation.
@@
 \includegraphics{Reff_Mstars.eps}
-\caption{We plot here the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs of the AIMSS catalog.
+\caption{The deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs of the AIMSS catalog.
 In grey are the RESOLVE (non-CCG) galaxies, which are plotted using their one component fit \Reff.
@@
 
-We plot in \autoref{fig:radius} the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs and dEs of the AIMSS catalog.
+\autoref{fig:radius} shows the deconvolved \Reff\ measurements for the entire RESOLVE sample, along with the CSSs and dEs of the AIMSS catalog.
 In grey are all RESOLVE galaxies, plotted using their one component fit \Reff.
@@
 We see in \autoref{fig:radius} that both core- and envelope-dominated CCGs tend to be at the higher end of the \Reff\ values, while core+envelope CCGs tend to be the lower \Reff\ values.
-There also are more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
+There are also more core-dominated CCGs at the higher M$_{\star}$ end while envelope-dominated CCGs tend to reside at low M$_{\star}$.
 
@@
 \includegraphics[scale=0.65]{sfr_mbary.eps}
-\caption{\textbf{(Left.)} On the left we plot the $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample.
-\textbf{(Right.)} On the right we have plotted the FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample.
-}
+\caption{\textbf{(Left.)} The $u-r$ colors against stellar mass of CCGs with the entire RESOLVE sample. \textbf{(Right.)} FSMGR against baryonic mass for both the CCGs and entire RESOLVE sample.}
 \label{fig:fsmgr}
@@
 
- We first examine the colors of the CCG sample.
+ We now examine the colors of the CCG sample.
 The left side of \autoref{fig:fsmgr} shows the k-corrected and extinction-corrected $u-r$ colors (as described in \autoref{phot}) of our CCG sample plotted against M$_{\star}$, compared to the RESOLVE sample as a whole.
@@
 \includegraphics{nn_groupmass_2d.eps}
-\caption{We plot here the group halo mass against the nearest 3D neighbor for the RESOLVE survey and CCG sample.
+\caption{Group halo mass vs.
+the nearest 2D neighbor for the RESOLVE survey and CCG sample.
 We see that CCGs live in a variety of environments, from extremely isolated (nearest neighbor $>$ 1 Mpc) to massive (M$_{\rm halo} \sim 10^{13}$ M$_{\odot}$) groups.
@@
 \subsection{Environments}
-We investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
+We next investigate the distribution of CCGs throughout the cosmic web, and find that CCGs span a range of different environments (see \autoref{fig:envplot}).
 There are many CCGs residing in low mass groups, similar to the M32--Andromeda relationship, which suggests that tidal stripping could have occurred for those CCGs.
@@
 There are also nine CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, and four of those are core dominated, resembling the isolated cE found by \citet{Huxor2013}.
-These free floating CCGs may be the result of dissipative formation since there is no nearby object to have performed the stripping or may have been ejected from groups or clusters during the stripping process.
+These free floating CCGs may be the result of dissipative formation since there is no nearby object to have performed the stripping.
+Alternatively, they may have been ejected from groups or clusters during the stripping process.
 
@@
  We lastly investigate the kinematics of the CCG sample using $\sigma$ values derived from SOAR and Gemini telescope data.
-\autoref{fig:sigma} plots the Faber-Jackson ($\sigma$-M$_{\star}$) relation for the 8 CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with $\sigma$ measured.
+\autoref{fig:sigma} plots the Faber-Jackson ($\sigma$-M$_{\star}$) relation for the eight CCGs with $\sigma$ measurements along with the other 80+ RESOLVE galaxies with $\sigma$ measured.
 Galaxies with $\sigma$ offset to higher values point to tidal stripping occurring, since they will have less stellar mass than the motions of the stars suggest should be there.
 Conversely, galaxies with $\sigma$ that lie on the trend may point dissipative formation occurring, since these will have formed similarly to normal elliptical galaxies.
-Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these 8 CCGs with velocity dispersion measurements.
+Most CCGs seem to be following the dissipative merger track, and in \autoref{discussion}, we examine in depth the formation scenarios for each of these eight CCGs with velocity dispersion measurements.
 
@@
 
-We now take an in depth look at the 8 CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
+We now take an in depth look at the eight CCGs with kinematics, and assign formation scenarios based on their core \Reff\, morphology, star formation histories, kinematics, and environments.
 For this discussion, we classify CCGs using the terms ``CSS-like'', ``dE-like'', or ``crossover''.
@@
 A dE-like CCG will have a large core radius and low $\sigma$ as is expected for dEs that are dissipatively formed.
-Crossover CCGs will have either large core radius and high $\sigma$ or small core radius and low $\sigma$.
+Crossover CCGs will have small core radius and low $\sigma$.
 Following this logic, we classify M32 as CCS-like since it has \Reff~$\sim~100$~pc and $\sigma$ offset to higher dispersion.
@@
 
-We have replotted Figures 4, 5, and 6 in \autoref{fig:miniplots}, this time highlighting the eight CCGs with velocity dispersions only.
+We have replotted Figures 4, 5, and 6 in \autoref{fig:miniplots}, this time highlighting the CCGs with velocity dispersions only.
 An important caveat for the CSSs and dEs in the AIMSS catalog is that the radius measurements are not decomposed into one and two components.
@@
 \subsection{dE-like CCGs}
-We classify rs0345, rs1100, rf0003, and rf0328 as dE-like CCGs, based on their high one-component effective radius and low $\sigma$.
+We classify rs0345, rs1100, rf0003, and rf0328 as dE-like CCGs, based on their large one-component \Reff\ and low $\sigma$.
 The CCGs rs0345 and rs1100 are both envelope-dominated, live firmly on the blue sequence, and are forming stars quite rapidly with FSMGR~$>1$.
 The galaxies reside in intermediate-sized groups (halo masses $\sim10^{11.7-12.5}$~\Msun) and are both within $<~0.15$~Mpc from a companion galaxy.
-Taken together these data suggest that rs0345 and rs1100 may be an example of tidal stripping or dissipative processes actively occurring, which is fueling the star formation and funneling gas from the disk to build a core.
-Judging from the regular morphologies seen in the images of these CCGs in \autoref{fig:imageplots}, tidal stripping and dissipative formation via merging are unlikely, which leaves ram pressure stripping as a probable formation scenario.
+Taken together these data suggest that rs0345 and rs1100 may be an example of a dissipative process actively occurring.
+Judging from the regular morphologies seen in the images of these CCGs in \autoref{fig:imageplots}, dissipative formation via merging is unlikely, which leaves ram pressure stripping that is perturbing the gas and fueling star formation as a probable formation scenario given their location in intermediate-sized groups.
 
-CCG rf0003 is core-dominated, lives intermediate between the blue and red sequences and has a low FSMGR ($\sim~0.10$).
+CCG rf0003 is core-dominated, lives between the blue and red sequences and has a low FSMGR ($\sim~0.10$).
 It resides in a low mass group (halo mass $\sim10^{10.9}$~\Msun) and is $>2$~Mpc from another galaxy, which we classify as free floating.
@@
 
-Lastly, rf0328 is also core-dominated and lives intermediate between the blue and red sequences, but has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr.
+Lastly, rf0328 is also semi core-dominated and lives intermediate between the blue and red sequences, but has a higher FSMGR at $\sim0.6$, indicating considerable star formation taking place in the last Gyr.
 The galaxy resides in a low mass group and is $\sim0.4$~Mpc from a neighbor.
-Its $\sigma$ places it among the dissipatively-formed CCGs, perhaps due to cold gas streams converging or even a merger, given its environment.
-Like rf0003, its color and FSMGR may indicate this formation happened recently.
+Its $\sigma$ places it among the dissipatively-formed CCGs, perhaps due to ram pressure stripping or even a minor merger.
+Like rf0003, its color and FSMGR may indicate recent formation.
+
+These dE-like CCGs with high FSMGR may be related to luminous compact blue dwarfs \citep[LCBDs;][]{Lisker2013, Crawford2016a} or ``green pea'' galaxies that were discovered by the Galaxy Zoo project \citep{Cardamone2009}.
+Green peas have similar sizes and masses as LCBDs but have extreme star formation that cause them to appear green in SDSS $gri$ image stacks due to huge [OIII] emission lines.
 
@@
 We classify rs0567, rs1186, rf0078, rf0492 as crossover CCGs, based on their small one component \Reff\ measurements ($\sim~500-700$~pc) and $\sigma$ values following the dissipative formation track.
-The CCGs rs0567, rs1186, and rf0078 are all three are mildly core-dominated galaxies.
-They live on the red sequence and display little star formation (FSMGR $> 0.1$) for all.
+There are two cEs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$ in \autoref{fig:sigma}), and we classify these as crossovers as well.
+
+The CCGs rs0567, rs1186, and rf0078 are all three mildly core-dominated galaxies.
+They live on the red sequence and display little star formation (FSMGR $> 0.1$).
 CCGs rs1186 and rf0078 both have close neighbors ($\sim~0.2$~Mpc distance), but rs0567 has a nearest neighbor $\sim~0.7$~Mpc, which makes it quite similar to the free floating cE discovered by \citet{Huxor2013} (which also has a core-dominated light profile).
 
-CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:imageplots}, but they don't share many other similarities.
+CCG rf0492 lies closest to the free floating cE from \citet{Huxor2013} in both \autoref{fig:sigma} and the top left of \autoref{fig:imageplots}, but they do not share many other similarities.
 This CCG has a core+envelope profile and lives in an intermediate-sized group with halo mass~$\sim~10^{12}$~\Msun and neighbor within $\sim~0.11$~Mpc.
-It lives on the red sequence and has low FSMGR ($<~0.1$), making it a good candidate of a CCG formed via ram pressure stripping as a dwarf (perhaps an LCBD) fell into the group halo.
+It lives on the red sequence and has low FSMGR ($<~0.1$), making it a good candidate of a CCG formed via ram pressure stripping as a dwarf fell into the group halo.
+The core may have been formed through this process as gas funnels to the center or may have been in place before infalling.
 
-We note that there are two cEs in AIMSS with extremely small \Reff\ and low $\sigma$ (the dark squares at M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~20~\text{km~s}^{-2}$ in \autoref{fig:sigma}), and we classify these as crossovers as well.
-We postulate that galaxies like these and the other crossover CCGs discussed above may be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$<~1$~kpc.
-\citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes (such as gas inflows to the central region of the disk) and then later quench to become red nuggets that are so common in the early Universe.
-
-There are also two AIMSS objects with the opposite conditions: large \Reff\ and high $\sigma$ (the two dark triangles in \autoref{fig:sigma} with M$_{\star}~\sim~10^{8.5}$~\Msun\ and $\sigma~\sim~40-50~\text{km~s}^{-2}$).
-These dEs may be in the process of tidal stripping currently and may move to the CSS-like track when the stripping is complete.
+We postulate that CCGs like these may be the low-$z$ analogues to the ``red/blue nugget'' galaxies that are common at high-redshift with \Reff~$<~1$~kpc.
+\citet{Dekel2013} propose that at high redshifts, blue nuggets form when gaseous disks contract during dissipative processes and then later quench to become red nuggets that are so common in the early universe.
 
@@
 
-  In this paper we have examined the colors, FSMGR, environments, and kinematics of the 96 compact core galaxies (CCGs) in the RESOLVE survey.
+  In this paper we have examined the morphologies, colors, FSMGR, environments, and kinematics of the 96 compact core galaxies (CCGs) in the RESOLVE survey.
 We have selected CCGs to have a seeing-deconvolved, core-only \Reff\ $<$ 800 pc, based on the sizes of the compact and dwarf ellipticals in the AIMSS catalog.
-We have quantified the amount of light in the cores and envelopes of each CCG by performing two component fits with \textsc{Galfit} and taking the logarithm of the ratio of the fluxes of the two different components.
+We quantified the morphology of CCGs by performing two component (core and envelope) S\'ersic fits with \textsc{Galfit} and taking the logarithm of the ratio of the fluxes of the core and the envelope.
 CCGs with more light in the envelope have log(flux ratio) $<$ 0 and are called ``envelope-dominated' CCGs.
@@
 Many CCGs live in low mass groups, similar to the M32--Andromeda relationship, perhaps hinting at tidal stripping formation scenarios.
-Others live in massive group halos and tend to be either core- or envelope dominated CCGs, conversely hinting towards ram pressure stripping being at play.
-There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the isolated cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to a dissipative formation scenario.
+Others live in massive group halos where tidal or ram pressure stripping may occur.
+There are also many CCGs that are $>1$ Mpc away from another object in RA--Dec--redshift space, resembling the free floating cEs found by \citet{Huxor2013} and \citet{Paudel2014}, which may point to dissipative formation scenarios or tidally stripped CCGs that have been ejected.
 
-\item Using velocity dispersions ($\sigma$) derived from the SOAR and Gemini telescopes, we classify the eight CCGs with $\sigma$ measurements as ``CCS-like'', ``dE-like'', or ``crossover'', based on their one-component radius measurements (the top left panel of \autoref{fig:miniplots}) and position on the Faber-Jackson ($\sigma$-M$_{\star}$) relation (\autoref{fig:sigma}).
+\item Using velocity dispersions ($\sigma$) derived from the SOAR and Gemini telescopes, we classify the eight CCGs with $\sigma$ measurements as ``CCS-like'', ``dE-like'', or ``crossover'', based on their position in the Faber-Jackson ($\sigma$-M$_{\star}$) relation (\autoref{fig:sigma}) and one-component radius measurements (the top left panel of \autoref{fig:miniplots}).
 We find four CCGs that are dE-like and four that are crossovers.
@@
 
-\item \textit{Investigate gas content.} The amount of neutral Hydrogen gas CCGs have may give us insights into their evolution over time.
+\item \textit{Investigate gas content.} The amount of neutral hydrogen gas CCGs have may give us insight into their evolution over time.
 For example, a CCG in a galaxy cluster with little HI gas may point towards ram pressure stripping being important.
-Combined with CCG colors and FSMGR, the gas content may be an important tool in determining the evolution of a CCG.
+Combined with CCG colors and FSMGR, gas content may be an important diagnostic in determining the evolution of a CCG.
 
@@
 \bibliographystyle{apj}
-\bibliography{library.bib}
+\bibliography{oldlibrary.bib}
 
-\appendix
-\label{app}
+%\appendix
+%\label{app}
+
+%\newpage
+%\pagebreak
+
+\setboolean{@twoside}{false}
+\includepdf[pages={{},-}, offset=20 -50]{gemini_dr_user_guide.pdf}
 
